```{r, include=F}
library(here)
source(file = here::here("functions/fun.R"))
f_load_libraries_colors()
col_Molecule <- rev(col_Molecule)
```

# Toxicokinetics of Imidacloprid and Epoxiconazole

**Research question:** What is the kinetic of uptake and depuration of EPX and IMD in earthworms ?

## Experiment

### Exposition of earthworms

We aimed to perform toxicokinetic experiements based on OECD TG 317 to be able to estimate the uptake and the depuration rate of each molecule.

```{r, warning=F, message=F}
#| fig-cap: Desing of the toxicokinetic experiements.
#| label: fig-TKdesign
#| fig-width: 6
#| fig-height: 3

t_elim <- 21
t <- seq(0,t_elim*2,0.01)
C0 <- 0
C_soil <- 10
C_soil <- 1000
ks <- 0.1
ke <- 1

fdata <- function(t, state, parameters) {
    with(as.list(c(state, parameters)), {
      if(t<21){dl <- ks*C_soil-ke*state[1]}else{dl <- -ke*state[1]}
      list(c(dl))
    })  }

# Initial condition
init_var <- c(C0)

# Parameters and time
params <- c(
  ks=ks, 
  ke=ke, 
  C_soil=C_soil
  )

# Resolution
sol_fdata <- ode(
  y=init_var, 
  times=t, 
  func=fdata, 
  parms=params
  )
  
sim_data_ex <- data.frame(
  t= sol_fdata[,1], 
  Cworm = sol_fdata[,2]
  )
sim_data_ex_up <- sim_data_ex[sim_data_ex$t<=t_elim,]
sim_data_ex_elim <- sim_data_ex[sim_data_ex$t>=t_elim,]

times_uptake <- c(1, 2, 3, 7, 10, 14, 17, 21)
times_elim <- c(22, 23, 24, 28, 31, 35, 38, 42)
times_points <- c(times_uptake, times_elim)

sim_data_points <- sim_data_ex[sim_data_ex$t %in% times_points,]


p <- ggplot()+
  geom_line(
    aes(
      x=sim_data_ex_up$t, 
      y=sim_data_ex_up$Cworm
      ), 
    color=col_uptake, 
    linewidth=2
    )+
  geom_line(
    aes(
      x=sim_data_ex_elim$t, 
      y=sim_data_ex_elim$Cworm
      ), 
    color=col_elim, 
    linewidth=2
    )+
  geom_point(
    aes(
      x=sim_data_points$t, 
      y=sim_data_points$Cworm
      ), 
    cex=3
    )+
  geom_label_repel(
    aes(x=sim_data_points$t, 
        y=sim_data_points$Cworm, 
        label = sim_data_points$t
        ),
    box.padding   = 0.35, 
    point.padding = 0.5,
    segment.color = Nord_polar[1]
    )+
  annotate(
    "text", 
    x=t_elim/2, 
    y=min(sim_data_ex$Cworm), 
    colour=col_uptake, 
    label="Uptake", 
    fontface="bold"
    )+
  annotate(
    "text", 
    x=t_elim*1.5, 
    y=max(sim_data_ex$Cworm), 
    colour=col_elim, 
    label="Elimination", 
    fontface="bold"
    )+
  
  labs(x="Time (d)", y=expression(paste("Concentration in earthworm")))+
  
  theme_bw()+
  theme(
    legend.position = "right", 
    legend.title=element_text(size=sizetitle-2,face="bold"), 
    title=element_text(size=sizetitle, face="bold"), 
    axis.title.x = element_text(size=sizetitle,face="plain"), 
    axis.title.y = element_text(size=sizetitle,face="plain")
    )

p
```

```{r, include=F}
ggsave(
  filename="TK_design.png", 
  plot=p, 
  width=8, 
  height = 4, 
  path=here::here("fig/TK")
  )
```

The @fig-TKdesign gives a general idea of the chosen experimental design with a first phase of uptake when earthworms are exposed to a given dose of a given substance and a second phase of elimination when earthworms are not exposed anymore. Timepoints are defined when the substance concentration in earthworms is measured to be able to describe the uptake and elimination curves (8 timepoints each, in 4 replicates).

One replicate consists of 1 individual exposed to the given concentration during the given time point if the time point is in the uptake phase or during 21 days with an elimination period (non exposed period) until the given time point. Individuals are kept individually in a medium cosm containing 200 g of soil (dry weight) at a WHC of 70% and fed with 3 g/ind/14 d (dry weight) of horse dung (WHC 70%). Cosms are kept in a thermoregulated enclosure at 18°C.

AJOUTER PHOTO COSME AVEC UN VER

The chosen tested concentration is 1 mg/kg for EPX for which no lethal effect is expected.

At the end of their exposure scenario, earthworms are weighted and then put on wet filter paper in Petri dishes for about 24 hours so their can void their gut content. At the end of these 24 hours, they are massaged to removed what is left in the gut and then weighted and frozen at -80°C.

### Chemical analysis of soils and earthworms (HPLC-HRMS)

AJOUTER PROTOCOLES

### Toxicokinetics modeling

The dynamic of the internal concentration is modeled with a one compartment model taking dilution with growth into account.

$$
\begin{aligned}
\frac{\mathrm{d}C_i}{\mathrm{d}t}&= \frac1L(k_u\times C_e-k_e\times C_i)-C_i\times \frac1V \frac{\mathrm{d}V}{\mathrm{d}t}\\
&=\frac1L\left(k_u\times C_e-k_e\times C_i-\frac{3a}{L} \ C_i \times \frac{\mathrm{d}L}{\mathrm{d}t} \right)
\end{aligned}
$$

-   $C_e$ : Soil concentration (ng/g)
-   $C_i$ : Internal concentration in earthworms (ng/g)
-   $L$ : Structural volumetric length (cm)
-   $V$ : Structural volume (cm$^3$) $= L^3$
-   $k_u$ : Uptake rate (cm.g(soil).day$^{-1}$.g(worm)$^{-1}$)
-   $k_e$ : Elimination rate (cm.day$^{-1}$)

!!!!! CHOICE OF PRIORS !!!!!

## Relationship between fresh weight and fresh weight without gut content {#sec-gutcontent}

!!!!!!! Expliquer pourquoi on en a besoin !!!!

```{r}
df_TK_full <- read_excel(here::here("data/Data_TK_long.xlsx")) |> 
  mutate(
    Time_point_f = as.factor(Time_point),
    ID = as.factor(ID),
    w = w/1000, # Conversion mg to g
    Dose = Dose*1000, # mg/kg to ng/g (mg/kg = microg/g = 1000 ng/g),
    CiIMD = C_worm_IMD,
    CiEPX = C_worm_EPX
  ) |> 
  mutate(
    C_soil_IMD = case_when(
      t == 0 & ID_recipient == "1" ~ 0.089, # ng/g
      t == 0 & ID_recipient == "2" ~ 0.072  # ng/g
    ),
    C_soil_EPX = case_when(
      t == 0 & ID_recipient == "1" ~ 0.780, # ng/g
      t == 0 & ID_recipient == "2" ~ 1.070  # ng/g
    )
  ) |> 
  mutate(expo = case_when(
    Phase == "Uptake" ~ 1,
    Phase == "Elimination" ~ 0,
    Phase == "Frozen" ~ 2
    )
  ) |> 
  filter(Keep == "Yes") |> 
  group_by(ID) |> 
  mutate(t = as.numeric(difftime(Date, first(Date), units = "days"))) |> 
  dplyr::ungroup()
```

```{r, warning=F, message=F}

# t1 = dernière masse avant expo == 2
t1_df <- df_TK_full %>%
  filter(Phase != "Frozen") %>%
  group_by(ID) %>%
  filter(t == max(t)) %>%
  dplyr::select(ID, w_popo = w, Molecule)

# t2 = première masse pendant expo == 2
t2_df <- df_TK_full %>%
  filter(Phase == "Frozen") %>%
  group_by(ID) %>%
  dplyr::select(ID, w_nopopo = w, Molecule)

# Joindre les deux et calculer le pourcentage de perte
df_TK_fasting <- t1_df %>%
  inner_join(t2_df, by = c("ID", "Molecule")) %>%
  mutate(
    Per_loss = 100 * (w_popo - w_nopopo) / w_popo,
    Loss = (w_popo - w_nopopo)
    )
```

```{r}
#| fig-cap: Relationship between fresh weight before and after fasting. 
#| fig-label: fig-Wfasting
#| fig-width: 5
#| fig-height: 4
#intercept <- 1.0
#fit <- lm(I(x - intercept) ~ 0 + y, lin)> summary(fit)
lm.fasting <- lm(w_nopopo ~ w_popo+0, data = df_TK_fasting)
summary(lm.fasting)
#plot(lm.fasting)

ggplot(
  data = df_TK_fasting
)+
  geom_point(
    aes(
      x=w_popo,
      y=w_nopopo,
      color = Molecule
      ),
    alpha = 0.3
  )+
  geom_abline(
    intercept = 0,
    slope = lm.fasting$coefficients[1],
    color = col_red
  )+
  annotate(
    geom="text", 
    x = 0.6, y = 1.1, 
    label = paste0("Wnopopo = Wpopo x ", signif(lm.fasting$coefficients[1],4), "\n adj-R2 = ", signif(summary(lm.fasting)$adj.r.squared, 4)), 
    color = col_red,
    size = 3
    )+
  scale_color_manual(values = col_Molecule)+
  lims(x=c(0.4, 1.2), y=c(0.4, 1.2))+
  labs(
    x="Weight with gut content (g)",
    y="Weight without gut content (g)"
  )+
  theme_minimal()


```

## Description of the gut depuration dynamic

When on Petri dishes, we need to account for the slow voiding process of the gut content during the 24 hours there are fasting.

A small experiment was done with 10 earthworms individually put in cosm with 200 g of Closeaux soil and 3 g of horse dung. After a week they were placed on filter paper in Petri dishes and weighted regularly. After 32 hours, earthworms were massaged to void the rest of their gut and weighted again.

```{r data gut, message=F, warning=F}
df_gut <- read_excel(here::here("data/Data_GUT.xlsx")) |> 
  mutate(
    ID = as.factor(ID)
  ) |> 
  group_by(ID) |> 
  mutate(
    Per_Weight = 100 * Weight / Weight[t == 0]
    ) |> 
  ungroup()
```

```{r, message=F, warning=F}
#| fig-cap: Evolution of earthworm weight and the corresponding percentage of initial weight throughout time in Petri dishes. Weight after being massaged are described with squared points.
#| label: fig-GUT
#| fig-height: 4
#| fig-width: 8

p_mg <- ggplot(
  data = df_gut, 
  aes(
    x = t,
    y = Weight,
    color = ID,
    shape = Handling
  )
)+
  geom_line(
    linewidth = 0.8,
    alpha = 0.8
  )+
  geom_point(
    alpha = 0.5,
    size = 2.5
  )+
  
  labs(
    x = "Time (hours)",
    y = "Weight (mg)"
  )+
  scale_color_manual(values = c(Nord_aurora, Nord_frost, Nord_polar))+
  scale_shape_manual(values = shape_Molecule)+
  theme_minimal()

p_per <- ggplot(
  data = df_gut, 
  aes(
    x = t,
    y = Per_Weight,
    color = ID,
    shape = Handling
  )
)+
  geom_line(
    linewidth = 0.8,
    alpha = 0.8
  )+
  geom_point(
    alpha = 0.5,
    size = 2.5
  )+
  
  labs(
    x = "Time (hours)",
    y = "Percentage of initial weight (%)"
  )+
  ylim(50, NA)+
  scale_color_manual(values = c(Nord_aurora, Nord_frost, Nord_polar))+
  scale_shape_manual(values = shape_Molecule)+
  theme_minimal()

p <- p_mg + p_per + plot_layout(ncol=2, guides="collect")
p

```

We modele the dynamic with a first order decay :

$$\frac{dP_{Weight}}{dt}=-\frac{\ln 2}{DT_{50,\text{gut}}}\ (P_{Weight}-P^{\infty}_{Weight})$$

$$P_{Weight}=P^{\infty}_{Weight}+(100-P^{\infty}_{Weight})\ \exp\left(- \frac{\ln 2}{DT_{50,\text{gut}}}\times t\right)$$

With :

-   $t$ : Time (h)
-   $P_{Weight}$ : Percentage of initial weight (%, 0-100)
-   $P^{\infty}_{Weight}$ : Percentage of initial weight when gut is fully emptied (%)
-   $DT_{50,\text{gut}}$ : Half-life of the gut content (h)

For the model, we consider that weights measured after massage are weights measured after a significant amount of time has passed. Therefore, the corresponding percentages of initial weight inform $P^{\infty}_{Weight}$.

```{r modgut, message=F, warning=F}

df_gut_mod <- df_gut |> 
  mutate(
    t = case_when(
      Handling == "None" ~ t,
      Handling == "Massaged" ~ 1000
    )
  )

mod.gut <- nlsLM(Per_Weight ~ Per_Weight_void + (100-Per_Weight_void)*exp(-lambda*t),
               data = df_gut_mod,
               start = list(
                 Per_Weight_void = 15,
                 lambda = 0.01
                 ),
               lower = c(0,0), 
               upper = c(Inf,Inf)
               )

summary(mod.gut)
cat("95% confidence intervals\n")
confint2(mod.gut, level = 0.95)

DT50_gut <- signif(as.numeric(log(2)/ coef(mod.gut)["lambda"]), 3)
Per_Weight_void <- signif(as.numeric(coef(mod.gut)["Per_Weight_void"]), 3)

df_gut_mod_plot <- df_gut_mod |> 
  filter(Handling == "None")

df_gut_mod_plot$Per_Weight_pred <- predict(mod.gut, newdata = df_gut_mod_plot)
```

The estimated value for $DT_{50,\text{gut}}$ and $P^{\infty}_{Weight}$ are `r DT50_gut` hours and `r Per_Weight_void`%, respectively.

$P^{\infty}_{Weight}$ estimated here is consistent with the one estimated in @sec-gutcontent.

```{r}
#| fig-cap: Modeling of the evolution of earthworm percentage of initial weight throughout time in Petri dishes. The grey line correspond to the prediction of the model.  
#| label: fig-GUTmod
#| fig-height: 4
#| fig-width: 6

p_mod <- ggplot(
  data = df_gut_mod_plot, 
  aes(
    x = t,
    y = Per_Weight,
    group = ID
  )
)+
  geom_line(
    linewidth = 0.8,
    alpha = 0.5,
    color = Nord_frost[4]
  )+
  geom_point(
    alpha = 0.5,
    size = 2.5,
    color = Nord_frost[4]
  )+
  geom_line(
    data = df_gut_mod_plot, 
    aes(
      x = t, 
      y = Per_Weight_pred
    ),
    linewidth = 2,
    color = Nord_polar[2],
    alpha = 0.2
  )+
  
  labs(
    x = "Time (hours)",
    y = "Percentage of initial weight (%)"
  )+
  scale_color_manual(values = c(Nord_aurora, Nord_frost, Nord_polar))+
  theme_minimal()

p_mod
```
