```{r, include=F}
library(here)
source(file = here::here("functions/fun_2.R"))
f_load_libraries_colors()
col_Molecule <- rev(col_Molecule)
```

# Toxicokinetics of Epoxiconazole

## Results of the experiment

### Data importation

Notations :

-   `Date_start` : Start of the experiement (t0)
-   `Molecule` : Substance to which the earthworm is exposed
-   `Dose` : Exposure dose (mg/kg)
-   `ID_recipient` : Recipient in which the soil was prepared
-   `ID_camp` : ID of the earthworm campagne and generation (see XXX for more information)
-   `ID` : ID of the earthworm
-   `Nb_rep` : Identification number of the replicate
-   `Time_point` : Time point to which the earthworm is dedicated
-   `Phase` : Uptake or Elimination phase
-   `Time_introduction_D0` : Time of the day when the earthworm was introduced into his contaminated cosm
-   `w0` : Body weight at t0
-   `w_Tp` : Body weight at the given time point
-   `w_frozen` : Body weight before congelation
-   `C_worm` : Measured concentration of the substance in the earthworm
-   `C_soil` : Measured concentration of the substance in the soil at the given time point

```{r data, warning=F, message=F}
df_TK_full <- read_excel(here::here("data/Data_TK_long.xlsx")) |> 
  mutate(
    Time_point_f = as.factor(Time_point),
    ID = as.factor(ID),
    w = w/1000, # Conversion mg to g
    Dose = Dose*1000, # mg/kg to ng/g (mg/kg = microg/g = 1000 ng/g),
    CiIMD = C_worm_IMD,
    CiEPX = C_worm_EPX
  ) |> 
  mutate(
    C_soil_IMD = case_when(
      t == 0 & ID_recipient == "1" ~ 0.089, # ng/g
      t == 0 & ID_recipient == "2" ~ 0.072  # ng/g
    ),
    C_soil_EPX = case_when(
      t == 0 & ID_recipient == "1" ~ 0.780, # ng/g
      t == 0 & ID_recipient == "2" ~ 1.070  # ng/g
    )
  ) |> 
  mutate(expo = case_when(
    Phase == "Uptake" ~ 1,
    Phase == "Elimination" ~ 0,
    Phase == "Frozen" ~ 2
    )
  ) |> 
  filter(Keep == "Yes") |> 
  group_by(ID) |> 
  mutate(t = as.numeric(difftime(Date, first(Date), units = "days"))) |> 
  dplyr::ungroup()

C_clx_IMD <- 16/1000 # ng/g
C_clx_EPX <- 90/1000 # ng/g
# Dose_EPX <- subset(df_TK_full, Molecule=="EPX")$Dose[1]
# Dose_IMD <- subset(df_TK_full, Molecule=="IMD")$Dose[1]
C_worm_t0_IMD <- mean(subset(df_TK_full,Molecule =="EPX")$C_worm_IMD, na.rm = T)
C_worm_t0_EPX <- mean(subset(df_TK_full,Molecule =="IMD")$C_worm_EPX, na.rm = T)

# EPX

df_TK_EPX <- df_TK_full |>  
  dplyr::select(Molecule, Dose, ID, Phase, w, C_worm_EPX, C_worm_IMD, t, Time_point, Nb_rep, expo)|> 
  filter(Molecule == "EPX") |> 
  # group_by(t) |> 
  # summarise(across(where(is.numeric), mean, na.rm = TRUE)) |> 
  # ungroup() |> 
  mutate(across(where(is.numeric), ~ replace_na(.x, -1))) |> 
  arrange(ID) |> 
  mutate(
    t = round(t,1),
    Molecule = "EPX"
    )

df_TK_EPX[df_TK_EPX$t == 0,]$C_worm_IMD <- C_worm_t0_IMD
df_TK_EPX[df_TK_EPX$t == 0,]$C_worm_EPX <- C_worm_t0_EPX

df_TK_EPX <- df_TK_EPX |> 
  mutate(
    Time = t,
    CiIMD = C_worm_IMD,
    CiEPX = C_worm_EPX,
    Weight_wgc = if_else(Phase == "Frozen", -1, w),
    Weight_ngc = if_else(!(Phase == "Frozen"), -1, w),
    Weight = w,
    Time_point_f = as.factor(Time_point)
  ) |> 
  dplyr::select(Time, CiEPX, CiIMD, Weight, Weight_wgc, Weight_ngc, Molecule, Nb_rep, ID, expo, Time_point_f) |> 
  mutate(
    CiEPX = na_if(CiEPX, -1),
    CiIMD = na_if(CiIMD, -1)
    )

df_TK_EPX_mean <- df_TK_EPX |> 
  dplyr::select(-ID) |> 
  group_by(Time) |> 
  summarise(
    CiEPX = exp(mean(log(CiEPX[CiEPX > 0]), na.rm = TRUE)),
    CiIMD = exp(mean(log(CiIMD[CiIMD > 0]), na.rm = TRUE)),
    Weight_wgc = mean(Weight_wgc, na.rm = TRUE),
    Weight_ngc = mean(Weight_ngc, na.rm = TRUE),
    Weight = mean(Weight, na.rm = TRUE),
    expo = mean(expo),
    .groups = "drop"
  ) |> 
  mutate(Molecule = "EPX")
```

### Initial state

```{r, warning=F, message=F}
#| fig-cap: Initial weights of earthworms. 
#| label: fig-init
#| fig-width: 6
#| fig-height: 4

# Weights at t=0
plot_D0 <- ggplot(
  data=subset(df_TK_EPX, Time==0), 
  aes(
    x=Time_point_f, 
    y=Weight_wgc, 
    color=Molecule, 
    fill=Molecule
    )
  )+

  geom_boxplot(alpha=0.2)+
  geom_dotplot(
    binaxis='y', 
    stackdir='center', 
    dotsize=0.7, 
    alpha=0.7
    )+
  facet_wrap(~Molecule, ncol=1, scales="free")+
  
  scale_color_manual(values=col_Molecule)+
  scale_fill_manual(values=col_Molecule)+

  labs(x="Dose (mg/kg)", y="Weight (mg)")+
  

  theme_classic(14)+
  theme(
    legend.position = "none", 
    legend.title=element_text(size=sizetitle-2,face="bold"),
    legend.text = element_text(size=sizetitle-2,face="plain"),
    
    title=element_text(size=sizetitle, face="bold"), 
    
    axis.title.x = element_blank(),
    axis.title.y = element_text(size=sizetitle,face="plain"),
    
    axis.text.x = element_blank(),
    axis.line.x=element_blank(),
    axis.ticks.x=element_blank(),
    
    
    strip.background = element_rect(
      color="black", 
      fill=Nord_snow[3], 
      size=0, 
      linetype="solid"
      ),
    strip.text = element_text(face = "bold")
    )
plot_D0
```

```{r, include=F}
ggsave(
  filename="TK_EPX_initial_weights.png", 
  plot=plot_D0, 
  width=6, 
  height = 4, 
  path=here::here("fig/TK")
  )
```

### Growth curves

```{r, warning=F, message=F}
#| fig-cap: Evolution of earthworms body weight throughout the experiment. 
#| label: fig-growthcurves
#| fig-width: 8
#| fig-height: 4

p <- ggplot() +
  geom_vline(
    xintercept = 21, 
    color = Nord_snow[1],
    linetype = "dashed"
    )+
  # geom_smooth(
  #   data = subset(df_TK_EPX, !expo==2),
  #   aes(
  #     x = Time,
  #     y = Weight_wgc,
  #     color = Molecule,
  #     fill = Molecule
  #     ),
  #   alpha = 0.2
  # )+
  geom_point(
    data = subset(df_TK_EPX, (!expo==2) & (!Weight_wgc == -1)),
    aes(
      x = Time,
      y = Weight_wgc,
      group = ID,
      color = Molecule
      ),
    alpha=0.5
    ) +
  geom_point(
    data = subset(df_TK_EPX_mean, (!expo==2) & (!Weight_wgc == -1)),
    aes(
      x = Time,
      y = Weight_wgc,
      color = Molecule
      ),
    alpha=1,
    size = 3
    ) +
  
  annotate(
    geom = "text",
    x = 10,
    y = 1.200,
    label = "Uptake\n phase",
    color = Nord_aurora[1],
    fontface = "bold",
    size = 3.5
  )+
  annotate(
    geom = "text",
    x = 35,
    y = 1.200,
    label = "Elimination\n phase",
    color = Nord_aurora[4],
    fontface = "bold",
    size = 3.5
  )+
  facet_wrap(~Molecule)+
  scale_color_manual(values=col_Molecule)+
  scale_fill_manual(values=col_Molecule)+
  labs(
   # title = "Growth Curves",
    x = "Time (days)",
    y = "Weight",
    color = ""
  ) +
  theme_minimal(base_size = 15) +  # Thème minimaliste
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    legend.position = "none",
    strip.background = element_rect(
      color="black", 
      fill=Nord_snow[3], 
      size=0, 
      linetype="solid"
      ),
    strip.text = element_text(face = "bold")
  )
p
```

```{r, include=F}
ggsave(
  filename="TK_EPX_growth_curves.png", 
  plot=p, 
  width=8, 
  height = 4, 
  path=here::here("fig/TK")
  )
ggsave(
  filename="TK_EPX_growth_curves.svg", 
  plot=p, 
  width=8, 
  height = 4, 
  path=here::here("fig/TK")
  )
```

```{r, warning=F, message=F}
#| fig-cap: Evolution of earthworms body weight before and after fasting 
#| label: fig-fasting
#| fig-width: 8
#| fig-height: 10

p_EPX <- ggplot() +
  geom_vline(
    xintercept = 21, 
    color = Nord_snow[1],
    linetype = "dashed"
    )+
  geom_point(
    data = df_TK_EPX,
    aes(
      x = Time,
      y = Weight,
      group = ID
      ),
    alpha=0.5,
    color = col_EPX
    ) +

  facet_wrap(~ID)+
  labs(
    title = "Growth Curves",
    x = "Time (days)",
    y = "Weight",
    color = ""
  ) +
  theme_minimal(base_size = 12) +  # Thème minimaliste
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    legend.position = "none",
    strip.background = element_rect(
      color="black", 
      fill=Nord_snow[3], 
      size=0, 
      linetype="solid"
      ),
    strip.text = element_text(face = "bold")
  )

p_EPX
```

```{r, warning=F, message=F}

# t1 = dernière masse avant expo == 2
t1_df <- df_TK_EPX %>%
  filter(expo != 2) %>%
  group_by(ID) %>%
  filter(Time == max(Time)) %>%
  dplyr::select(ID, w1 = Weight, Molecule)

# t2 = première masse pendant expo == 2
t2_df <- df_TK_EPX %>%
  filter(expo == 2) %>%
  group_by(ID) %>%
  dplyr::select(ID, w2 = Weight, Molecule)

# Joindre les deux et calculer le pourcentage de perte
df_TK_fasting <- t1_df %>%
  inner_join(t2_df, by = c("ID", "Molecule")) %>%
  mutate(
    Per_loss = 100 * (w1 - w2) / w1,
    #Loss = (w1 - w2)
    Loss = w2
    )

summary(df_TK_fasting)

```

```{r}
#intercept <- 1.0
#fit <- lm(I(x - intercept) ~ 0 + y, lin)> summary(fit)
lm.fasting <- lm(Loss ~ w1+0, data = df_TK_fasting)
summary(lm.fasting)
#plot(lm.fasting)

ggplot(
  data = df_TK_fasting
)+
  geom_point(
    aes(
      x=w1,
      y=Loss,
      color = Molecule
      ),
    alpha = 0.3
  )+
  geom_abline(
    intercept = 0,
    slope = lm.fasting$coefficients[1],
    color = col_red
  )+
  scale_color_manual(values = col_Molecule)+
  theme_minimal()


```

!!!!!!!! Growth rates !!!!!

### Measured internal concentrations

```{r, message=F, warning=F}
#| fig-cap: Measurements of EPX concentration in earthworms exposed to 10 mg/kg of EPX and related weight measurement of earthworms. Points represent the experimental data, the blue curve and the transparent blue band are produced with geom_smooth. 
#| fig-label: fig-curvesmooth
#| fig-width: 8
#| fig-height: 4

p <- ggplot(
  data = df_TK_EPX,
  aes(
    x = Time
  )
  )+
  geom_point(
    mapping = aes(
      y = CiEPX
    ),
    color = col_EPX,
    fill = col_EPX
  )+
  geom_point(
    mapping = aes(
      y = CiIMD
    ),
    color = col_IMD,
    fill = col_IMD
  )+
  facet_wrap(~Molecule, ncol = 2, scales = "free")+
  labs(
    x = "Time (days)",
    y = "Concentration in earthworm (ng/g)"
  )+
  theme_minimal()
p
```

## Modeling of the toxicokinetics

```{bash, eval=F, execute=F}
pwd
cd ..
cd ..
cd mod/TK_EPX
pwd

makemcsim m_TK_EPX.model &
wait
./mcsim.m_TK_EPX TK_EPX_C1.in &
./mcsim.m_TK_EPX TK_EPX_C2.in &
./mcsim.m_TK_EPX TK_EPX_C3.in &
wait
```

```{r, message=F, warning=F}
path_mod_EPX <- here::here("mod/TK_EPX")
```

The first step is to retrieve the information of the MCMC simulation experiments.

The inputs :

-   Input files must a name like "xxxxx.1.in"
-   Output files must a name like "xxxxx.1.out"

```{r EPXreadMCMC, message=F, warning=F, results='hidden'}
MCMC_out_EPX <- f_MCSim_ind(path_mod_EPX)

NC <- MCMC_out_EPX$NC
Nb_param <- MCMC_out_EPX$Nb_param
Nb_experiement <- MCMC_out_EPX$Nb_experiement
Nb_iter_kept <- MCMC_out_EPX$Nb_iter_kept
N_iter_setpoint <- MCMC_out_EPX$N_iter_setpoint

L_parameters <- unique(MCMC_out_EPX$Priors$Nom)

```

We can retrieve different information from the model :

-   The number of chains used : `r NC`
-   The number of parameters : `r Nb_param`
-   The number of experiments : `r Nb_experiement`
-   The number of last iterations used to describe the posterior distribution : `r Nb_iter_kept`
-   The number of last iterations used to create the `tab_setpoint.out` file : `r N_iter_setpoint`

Warning : Run the command `./mcsim.m_TK_EPX TK_EPX_Setpoint.in` in the terminal while being in the folder `mod/TK_EPX` to create the `Setpoints.out` now. Do the same with `./mcsim.m_TK_EPX TK_EPX_Setpoint_ind.in` to create the `Setpoints_ind.out` and with `./mcsim.m_TK_EPX TK_EPX_Setpoint_ind_full.in` to create the `Setpoints_ind_full.out`.

### Priors used for the model

```{r EPXreadpriors, message = F, warning = F}
#| tbl-cap: Priors used for the model
#| tbl-label: tbl-EPXPriors

#colnames(MCMC_out_EPX$Priors) <- c("Nom", "Distribution", "Mean", "Sd", "Min", "Max")

MCMC_out_EPX$Priors |> datatable(
  options = list(
    dom = 't',
    autoWidth = TRUE,
    columnDefs = list(
      list(className = 'dt-left', targets = "_all")
      )
    ), 
  class="hover"
  ) 
```

```{r EPXpriors, message=F, warning=F}
#| fig-cap: Distributions of the priors.
#| label: fig-EPXprior
#| fig-height: 6
#| fig-width: 8

n_samples <- 1e6 # Simulation of the distribution

df_priors_dist <- MCMC_out_EPX$Priors |> 
  dplyr::select(Nom, Distribution, P1, P2) |> 
  rowwise() |> 
  mutate(samples = case_when(
    !(Distribution == "Uniform") ~ list(rnorm(n_samples, mean = P1, sd = P2)),
    Distribution == "Uniform" ~ list(runif(n_samples, min=P1, max = P2))
    )
    ) |> 
  unnest(samples)

col_prior <- Nord_polar[4]
alpha_prior <- 0.5

p <- ggplot() +
  facet_wrap(~Nom, scales = "free")+
  
  stat_halfeye(
    data = df_priors_dist, 
    aes(
       x = samples
       ),
    alpha = alpha_prior,
    fill = col_prior,
    color = col_prior,
    normalize = "xy" 
    ) +
  
  labs(
    title = "Priors distributions", 
    x = "Parameter value", 
    y = "Density"
    ) +
  theme_minimal()

p 

```

```{r, include = F}
ggsave(
  filename="TK_EPX_priors.png", 
  plot=p, 
  width=8, height = 6, 
  path=here::here("fig/TK/")
  )
ggsave(
  filename="TK_EPX_priors.svg", 
  plot=p, 
  width=8, height = 6, 
  path=here::here("fig/TK/")
  )
```

### Chains

```{r EPXChains, message=F, warning=F}
#| fig-cap: Parameters chains. Only the first iteration and the last `r Nb_iter_kept` are represented.
#| label: fig-EPXchains
#| fig-height: 5
#| fig-width: 8

plot <-  
  ggplot(
    data = MCMC_out_EPX$Chains, 
    aes(
      x = Iteration, 
      y = value, 
      color = as.factor(Chain), 
      group = as.factor(Chain)
      )
  )+
  geom_line(alpha=0.7)+
  facet_wrap(~Parameter, scales = "free", ncol = 2)+
  
  scale_color_manual(name = "Chains", values = nord(palette = "frost"))+
  
  theme_bw()+
  theme(
    legend.position = "right", 
    title=element_text(size=12, face="plain"), 
    axis.title.x = element_text(face="plain"),
    strip.background = element_rect(fill="white")
    )

plot
  
```

```{r, include = F}
ggsave(
  filename="TK_EPX_chains.png", 
  plot=plot, 
  width=8, height = 5, 
  path=here::here("fig/TK/")
  )
ggsave(
  filename="TK_EPX_chains.svg", 
  plot=plot, 
  width=8, height = 5, 
  path=here::here("fig/TK/")
  )
```

We can also take a look at the likelihood and the deviance ratio.

```{r EPXlike, message=F, warning=F}
#| fig-cap: Evolution of likelihood and deviance ratio through the iterations.
#| label: fig-EPXlike
#| fig-height: 5
#| fig-width: 8

p1 <- ggplot(
  MCMC_out_EPX$df_LnPost_start, 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = c("1", "2", "3"), values = Nord_frost) +
  labs(
    x = "First half iterations", 
    y = "LnPosterior"
    ) +
  theme_minimal()

p2 <- ggplot(
  MCMC_out_EPX$df_LnPost, 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = c("1", "2", "3"), values = Nord_frost) +
  labs(
    x = paste(MCMC_out_EPX$Nb_iter_kept, "last iterations"), 
    y = "LnPosterior"
    ) +
  theme_minimal()

p3 <- ggplot(
  MCMC_out_EPX$df_Devc, 
  aes(
    x = iteration, 
    y = RatioDeviance, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = c("1", "2", "3"), values = Nord_frost) +
  labs(
    x = paste(MCMC_out_EPX$Nb_iter_kept, "last iterations"), 
    y = "Ratio Deviance"
    ) +
  theme_minimal()

p <- p1 + p2 + p3 +
  plot_layout(ncol=3, guides = "collect")
p

```

```{r, include = F}
ggsave(
  filename="TK_EPX_likedevratio.png", 
  plot=p, 
  width=8, height = 5, 
  path=here::here("fig/TK/")
  )
ggsave(
  filename="TK_EPX_likedevratio.svg", 
  plot=p, 
  width=8, height = 5, 
  path=here::here("fig/TK/")
  )
```

### Parameter estimation results

```{r EPXpost, message=F, warning=F}
#| fig-cap: Distributions of the priors and the posteriors.
#| label: fig-EPXpost
#| fig-height: 6
#| fig-width: 8

alpha_prior <- 0.5
alpha_post <- 0.5
col_prior <- Nord_snow[1]
col_post <- col_EPX


MCMC_out_EPX$Chains <- MCMC_out_EPX$Chains |> 
  mutate(Nom = str_remove(Parameter, "\\.\\d+\\.$"))

p <- ggplot() +
  
  # Priors
  stat_halfeye(
    data = df_priors_dist, 
    aes(
       x = samples,
       #y = ..scaled..
       ),
    alpha = alpha_prior,
    fill = col_prior,
    color = col_prior,
    normalize = "xy" 
    ) +
  
  # Posterior
  stat_halfeye(
    data = subset(MCMC_out_EPX$Chains, Nom %in% L_parameters),
    mapping = aes(
      x=value
    ),
    fill = col_post,
    color = col_post,
    alpha = alpha_post,
    normalize = "xy"
  ) +
  
  facet_wrap(~Nom, scales = "free")+
  labs(
    title = "<span style = 'color:#88C0D0;'>Posterior</span>
       and <span style = 'color:#D8DEE9;'>prior</span> distributions", 
    x = "Parameter value", 
    y = "Density"
    ) +
  theme_minimal()+
  theme(
    title=element_markdown(face="bold")
  )

p
```

```{r, include = F}
ggsave(
  filename="TK_EPX_post.png", 
  plot=p, 
  width=8, height = 6, 
  path=here::here("fig/TK/")
  )
ggsave(
  filename="TK_EPX_post.svg", 
  plot=p, 
  width=8, height = 6, 
  path=here::here("fig/TK/")
  )
```

```{r calcBCFEPX, message=F, warning=F}

ku_samples <- MCMC_out_EPX$Chains |> filter(Nom == "kuEPX")
ke_samples <- MCMC_out_EPX$Chains |> filter(Nom == "keEPX")

BCF_samples <- ku_samples$value / ke_samples$value

BCF_mode <- density(BCF_samples)$x[which.max(density(BCF_samples)$y)]
BCF_CI <- quantile(BCF_samples, probs = c(0.025, 0.975))
BCF_CI_low <- as.numeric(BCF_CI[1])
BCF_CI_up <- as.numeric(BCF_CI[2])
BCF_min <- min(BCF_samples)
BCF_max <- max(BCF_samples)
BCF_mean <- mean(BCF_samples)
BCF_sd <- sd(BCF_samples)

BCF <- c(
  BCF_mode, 
  BCF_CI_low, BCF_CI_up, 
  BCF_min, BCF_max, 
  BCF_mean, BCF_sd
  )

```

```{r EPXSummaryRes, message=F, warning=F}
#| tbl-cap: Results summary
#| tbl-label: tbl-EPXressum

Summary_res_EPX_tmp <- cbind(as.data.frame(MCMC_out_EPX$Summary_res)[1:length(L_parameters)], BCF)

Summary_res_EPX_f <- Summary_res_EPX_tmp |> 
  mutate(across(where(is.numeric), signif, 2))

Summary_res_EPX_f |> datatable(
  options = list(
    dom = 't',
    autoWidth = TRUE,
    columnDefs = list(
      list(className = 'dt-left', targets = "_all")
      )
    ), 
  class="hover"
  ) 

```

### Comparison of observed vs. predicted data

```{bash, eval=F, execute=F}
pwd
cd ..
cd ..
cd mod/TK_EPX
pwd
./mcsim.m_TK_EPX TK_EPX_Setpoint_ind.in
wait
```

```{r EPXdataObs, message=F, warning=F}

dObs_ind <- df_TK_EPX |> 
  mutate(ID = as.numeric(ID))
colnames(dObs_ind)[colnames(dObs_ind) == "Weight_wgc"] <- "Weight_wgc_obs"
colnames(dObs_ind)[colnames(dObs_ind) == "Weight_ngc"] <- "Weight_ngc_obs"
colnames(dObs_ind)[colnames(dObs_ind) == "CiEPX"] <- "CiEPX_obs"
colnames(dObs_ind)[colnames(dObs_ind) == "t"] <- "Times"

```

```{r EPXdatapred, message=F, warning=F}
nb_rows_ind <- NC*N_iter_setpoint+1

Sim.Res.ind <- as.data.frame(fread(here::here(path_mod_EPX, "Setpoints_ind.out"),sep="\t"))

df_mod_ind <- NULL

for (i in 1:Nb_experiement){
  
  ID_i <- unique(dObs_ind$ID)[i]
  
  start = nb_rows_ind*(i-1)
  end = nb_rows_ind*i

  Sim.Res.ind_i  <- Sim.Res.ind[start:end,]
  
  dObs_i <- subset(dObs_ind, ID == ID_i)
  
  Sim.Res.ind_i <- Sim.Res.ind_i|> 
    dplyr::select(matches(paste0("_", i, "\\.[0-9]+$")))
  
  Time_pred = dObs_i$Time # !!!
  
  Nom_Endpoints = c("Weight_wgc", "Weight_ngc", "CiEPX")
  
  Nsortie = 3
  
  MPV = IC_min = IC_max = Endpoint = index = NULL
  
  for (j in 1:length(Nom_Endpoints)){
    
    index =grep(paste0("^",Nom_Endpoints[j],"_") , colnames(Sim.Res.ind_i), fixed=FALSE)

    
    Data_sim = as.matrix( Sim.Res.ind_i[ , index] )
    
    MPV    = c(  MPV,  as.numeric( Data_sim[nrow(Data_sim), ] ) )
    IC_min = c(IC_min,  apply(Data_sim, 2, quantile,  0.025, na.rm=TRUE) )
    IC_max = c(IC_max,  apply(Data_sim, 2, quantile,  0.975, na.rm=TRUE) ) 
    
    Endpoint = c(Endpoint, rep(Nom_Endpoints[j], ncol(Data_sim)))
  }
  
  df_mod_ind_i <- data.frame(
    predict.endpoint = MPV,
    Time    = rep(Time_pred, Nsortie),
    low     = IC_min,
    up      = IC_max,
    Endpt   = Endpoint
    )
  
  df_mod_ind_i <- df_mod_ind_i %>%
    mutate(ID=ID_i)

  df_mod_ind <- rbind(df_mod_ind, df_mod_ind_i)
}

df_mod_Weight_wgc_ind <- subset(df_mod_ind, Endpt == "Weight_wgc")
df_mod_Weight_ngc_ind <- subset(df_mod_ind, Endpt == "Weight_ngc")
df_mod_CiEPX_ind <- subset(df_mod_ind, Endpt == "CiEPX")

```

```{r EPXdatapredobs, message=F, warning=F}

df_predobs_CiEPX_ind <- dObs_ind |> 
  left_join(df_mod_CiEPX_ind, suffix = c("_obs", "_pred")) |> 
  dplyr::select(-c(Weight_wgc_obs, CiIMD)) |> 
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

df_predobs_Weight_wgc_ind <- dObs_ind |> 
  filter(!(expo == 2)) |> 
  left_join(df_mod_Weight_wgc_ind, suffix = c("_obs", "_pred"))|>
  dplyr::select(-c(CiEPX_obs, CiIMD, Weight_ngc_obs)) |> 
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) 

df_predobs_Weight_ngc_ind <- dObs_ind |> 
  filter((expo == 2)) |> 
  left_join(df_mod_Weight_ngc_ind, suffix = c("_obs", "_pred"))|>
  dplyr::select(-c(CiEPX_obs, CiIMD, Weight_wgc_obs)) |> 
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) 

```

```{r predobsEPX, message=F, warning=F}
#| fig-cap: Results of the model fit on experimental data. Predicted values are represented with points with their respective credibility interval of 95%. Thin black and grey lines represent the 2-folds and 5-fold changes, respectively. The thicker black line represents the identity line. 
#| label: fig-EPXpredobs
#| fig-height: 4
#| fig-width: 6

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]

seq_line <- seq(0.5, 1.5, 0.001)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_W_wgc <- ggplot(
  data = df_predobs_Weight_wgc_ind,
  mapping = aes(
      x = Weight_wgc_obs,
      y = predict.endpoint
    )
  )+
  geom_line(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up
    ),
    alpha = 0.5,
    color = col_EPX
  )+
  xlim(
    xmin = 0.5,
    xmax = max(df_predobs_Weight_wgc_ind$Weight_obs)
  )+
  ylim(
    ymin = 0.5,
    ymax = max(df_predobs_Weight_wgc_ind$predict.endpoint)
  )+
  scale_x_log10(limits=c(0.5, 1.2))+
  scale_y_log10(limits=c(0.5, 1.2))+
  labs(
    x = "Observed weight of earthworms (g)",
    y = "Predicted weight of earthworms (g)"
  )+
  theme_minimal()

p_W_ngc <- ggplot(
  data = df_predobs_Weight_ngc_ind,
  mapping = aes(
      x = Weight_ngc_obs,
      y = predict.endpoint
    )
  )+
  geom_line(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up
    ),
    alpha = 0.5,
    color = col_EPX
  )+
  xlim(
    xmin = 0.5,
    xmax = max(df_predobs_Weight_ngc_ind$Weight_obs)
  )+
  ylim(
    ymin = 0.5,
    ymax = max(df_predobs_Weight_ngc_ind$predict.endpoint)
  )+
  scale_x_log10(limits=c(0.5, 1.2))+
  scale_y_log10(limits=c(0.5, 1.2))+
  labs(
    x = "Observed weight of earthworms (g)",
    y = "Predicted weight of earthworms (g)"
  )+
  theme_minimal()

fact_1 <- 2
fact_2 <- 5

seq_line <- seq(0.5, 1500, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )


p_CiEPX_predobs <- ggplot(
  data = df_predobs_CiEPX_ind,
  mapping = aes(
      x = CiEPX_obs,
      y = predict.endpoint
    )
  )+
  geom_path(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up
    ),
    alpha = 0.5,
    color = col_EPX
  )+
  
  xlim(
    xmin = 0.5,
    xmax = max(df_predobs_CiEPX_ind$CiEPX_obs)
  )+
  ylim(
    ymin = 0.5,
    ymax = max(df_predobs_CiEPX_ind$predict.endpoint)
  )+
  labs(
    x = "Observed concentrations of EPX\nin earthworms (ng/g)",
    y = "Predicted concentrations of EPX\nin earthworms (ng/g)"
  )+
  scale_x_log10(limits=c(1, 500))+
  scale_y_log10(limits=c(1, 500))+
  theme_minimal()

p_CiEPX_zoom_predobs <- ggplot(
  data = df_predobs_CiEPX_ind,
  mapping = aes(
      x = CiEPX_obs,
      y = predict.endpoint
    )
  )+
  geom_path(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up
    ),
    alpha = 0.5,
    color = col_EPX
  )+
  
  xlim(
    xmin = 0.5,
    xmax = max(df_predobs_CiEPX_ind$CiEPX_obs)
  )+
  ylim(
    ymin = 0.5,
    ymax = max(df_predobs_CiEPX_ind$predict.endpoint)
  )+
  labs(
    x = "Observed concentrations of EPX\nin earthworms (ng/g)",
    y = "Predicted concentrations of EPX\nin earthworms (ng/g)"
  )+
  scale_x_log10(limits=c(100, 2000))+
  scale_y_log10(limits=c(100, 2000))+
  theme_minimal()


p <- p_W_wgc + p_W_ngc + p_CiEPX_predobs
p

```

```{r, include = F}
ggsave(
  filename="TK_EPX_predobs.png", 
  plot=p, 
  width=10, height = 6, 
  path=here::here("fig/TK/")
  )
ggsave(
  filename="TK_EPX_predobs.svg", 
  plot=p, 
  width=10, height = 6, 
  path=here::here("fig/TK/")
  )
```

```{r countfoldEPX, warning=F}

df_predobs_Weight_ind <- df_predobs_Weight_ind |> 
  mutate(
    Ratio_predobs = predict.endpoint/Weight_obs,
    Residuals = predict.endpoint-Weight_obs
  )

Weight_count_fold2 <- length(subset(df_predobs_Weight_ind, Ratio_predobs >= 0.5 & Ratio_predobs <= 2)$Weight_obs)/length(df_predobs_Weight_ind$Weight_obs)*100

Weight_count_fold5 <- length(subset(df_predobs_Weight_ind, Ratio_predobs >= 0.2 & Ratio_predobs <= 5)$Weight_obs)/length(df_predobs_Weight_ind$Weight_obs)*100

df_predobs_CiEPX_ind <- df_predobs_CiEPX_ind |> 
  mutate(
    Ratio_predobs = predict.endpoint/CiEPX_obs,
    Residuals = predict.endpoint-CiEPX_obs
  )

CiEPX_count_fold2 <- length(subset(df_predobs_CiEPX_ind, Ratio_predobs >= 0.5 & Ratio_predobs <= 2)$CiEPX_obs)/length(df_predobs_CiEPX_ind$CiEPX_obs)*100

CiEPX_count_fold5 <- length(subset(df_predobs_CiEPX_ind, Ratio_predobs >= 0.2 & Ratio_predobs <= 5)$CiEPX_obs)/length(df_predobs_CiEPX_ind$CiEPX_obs)*100



cat("For weights : \n\n",
  "Percentage of prediction in fold 2 = ", round(Weight_count_fold2, 1), "%\n",
    "Percentage of prediction in fold 5 = ", round(Weight_count_fold5, 1), "%")
cat("\n\nFor internal concentrations : \n\n",
  "Percentage of prediction in fold 2 = ", round(CiEPX_count_fold2, 1), "%\n",
    "Percentage of prediction in fold 5 = ", round(CiEPX_count_fold5, 1), "%")
```

### Full individual trajectories

```{bash, results=F, eval=F}
pwd
cd ..
cd ..
cd mod/TK_EPX
pwd

./mcsim.m_TK_EPX TK_EPX_Setpoint_ind_full_1.in &
./mcsim.m_TK_EPX TK_EPX_Setpoint_ind_full_2.in &
 ./mcsim.m_TK_EPX TK_EPX_Setpoint_ind_full_3.in &
 ./mcsim.m_TK_EPX TK_EPX_Setpoint_ind_full_4.in &
wait
```

```{r EPXdatapredfull, message=F, warning=F}
#| cache: false

dObs_ind <- df_TK_EPX |> 
  mutate(ID = as.numeric(ID))
colnames(dObs_ind)[colnames(dObs_ind) == "Weight"] <- "Weight_obs"
colnames(dObs_ind)[colnames(dObs_ind) == "CiEPX"] <- "CiEPX_obs"
colnames(dObs_ind)[colnames(dObs_ind) == "t"] <- "Times"

nb_rows_ind <- NC*N_iter_setpoint+1

Sim.Res.ind.full_1 <- as.data.frame(fread(here::here(path_mod_EPX, "Setpoints_ind_full_1.out"))) # Very heavy to import but it works !
Sim.Res.ind.full_2 <- as.data.frame(fread(here::here(path_mod_EPX, "Setpoints_ind_full_2.out"))) # Very heavy to import but it works !
Sim.Res.ind.full_3 <- as.data.frame(fread(here::here(path_mod_EPX, "Setpoints_ind_full_3.out"))) # Very heavy to import but it works !
Sim.Res.ind.full_4 <- as.data.frame(fread(here::here(path_mod_EPX, "Setpoints_ind_full_4.out"))) # Very heavy to import but it works !

l_Setpoint <- c(Sim.Res.ind.full_1, Sim.Res.ind.full_2, Sim.Res.ind.full_3, Sim.Res.ind.full_4)

# Faut absolument les coller sinon ça décale tout

df_mod_ind_1 <- NULL
df_mod_ind_2 <- NULL
df_mod_ind_3 <- NULL
df_mod_ind_4 <- NULL

In_1 <- readLines(paste(path_mod_EPX, "TK_EPX_Setpoint_ind_full_1.in", sep = "/"))
nb_sim_1 <- length(grep(pattern = "*Simulation*", In_1))
In_2 <- readLines(paste(path_mod_EPX, "TK_EPX_Setpoint_ind_full_2.in", sep = "/"))
nb_sim_2 <- length(grep(pattern = "*Simulation*", In_2))
In_3 <- readLines(paste(path_mod_EPX, "TK_EPX_Setpoint_ind_full_3.in", sep = "/"))
nb_sim_3 <- length(grep(pattern = "*Simulation*", In_3))

nb_split <- 4

for (i in 1:Nb_experiement){
  print(i)
  
  idx_split <- ceiling(i / (length(unique(df_TK_EPX$ID)) / nb_split))
  
  if(idx_split == 1){
    Res <- Sim.Res.ind.full_1
    nb_sim <- 0
  }
  if(idx_split == 2){
    Res <- Sim.Res.ind.full_2
     nb_sim <- nb_sim_1
  }
  if(idx_split == 3){
    Res <- Sim.Res.ind.full_3
    nb_sim <- nb_sim_1 + nb_sim_2
  }
  if(idx_split == 4){
    Res <- Sim.Res.ind.full_4
    nb_sim <- nb_sim_1 + nb_sim_2 + nb_sim_3
  }
  
  ID_i <- unique(dObs_ind$ID)[i]
  
  i_sim <- i-nb_sim 
  
  start = nb_rows_ind*(i_sim-1)
  end = nb_rows_ind*(i_sim)

  Sim.Res.ind.full_i  <- Res[start:end,]
  
  dObs_i <- subset(dObs_ind, ID == ID_i)
  
  Sim.Res.ind.full_i <- Sim.Res.ind.full_i|> 
    dplyr::select(matches(paste0("_", i_sim, "\\.[0-9]+$")))
  
  Time_pred = seq(0,44,0.25) # !!!
  
  Nom_Endpoints = c("Weight", "CiEPX")
  
  Nsortie = 2
  
  MPV = IC_min = IC_max = Endpoint = index = NULL
  
  for (j in 1:length(Nom_Endpoints)){
    
    index =grep(paste0("^",Nom_Endpoints[j],"_") , colnames(Sim.Res.ind.full_i), fixed=FALSE)
    
    Data_sim = as.matrix( Sim.Res.ind.full_i[ , index] )
    
    MPV    = c(  MPV,  as.numeric( Data_sim[nrow(Data_sim), ] ) )
    IC_min = c(IC_min,  apply(Data_sim, 2, quantile,  0.025, na.rm=TRUE) )
    IC_max = c(IC_max,  apply(Data_sim, 2, quantile,  0.975, na.rm=TRUE) ) 
    
    Endpoint = c(Endpoint, rep(Nom_Endpoints[j], ncol(Data_sim)))
  }
  
  df_mod_ind_i <- data.frame(
    predict.endpoint = MPV,
    Time    = rep(Time_pred, Nsortie),
    low     = IC_min,
    up      = IC_max,
    Endpt   = Endpoint
    )
  
  df_mod_ind_i <- df_mod_ind_i %>%
    mutate(ID=ID_i)
  
  if(i <= 16){
    df_mod_ind_1 <- rbind(df_mod_ind_1, df_mod_ind_i)
  }
  if(16 < i & i <= 32){
    df_mod_ind_2 <- rbind(df_mod_ind_2, df_mod_ind_i)
  }
  if(32 < i & i <= 48){
    df_mod_ind_3 <- rbind(df_mod_ind_3, df_mod_ind_i)
  }
  if(48 < i){
    df_mod_ind_4 <- rbind(df_mod_ind_4, df_mod_ind_i)
  }
}

rm(
  Sim.Res.ind.full_1, 
  Sim.Res.ind.full_2, 
  Sim.Res.ind.full_3, 
  Sim.Res.ind.full_4
  )

df_mod_ind <- rbind(
  df_mod_ind_1,
  df_mod_ind_2,
  df_mod_ind_3,
  df_mod_ind_4
)

rm(
  df_mod_ind_1,
  df_mod_ind_2,
  df_mod_ind_3,
  df_mod_ind_4
)

df_mod_Weight_ind <- subset(df_mod_ind, Endpt == "Weight")
df_mod_CiEPX_ind <- subset(df_mod_ind, Endpt == "CiEPX")

time_limits <- dObs_ind %>%
  group_by(ID) %>%
  summarise(time_cutoff = max(Time, na.rm = TRUE) + 2)

df_mod_CiEPX_ind_t <- df_mod_CiEPX_ind %>%
  left_join(time_limits, by = "ID") %>%
  filter(Time <= time_cutoff) %>%
  dplyr::select(-time_cutoff) 

df_mod_Weight_ind_t <- df_mod_Weight_ind %>%
  left_join(time_limits, by = "ID") %>%
  filter(Time <= time_cutoff) %>%
  dplyr::select(-time_cutoff) 

```

```{r EPXpredcurvesdata, message=F, warning=F}
#| fig-cap: Estimated toxicokinetic of the EPX concentration in earthworms exposed to 1000 ng/g of EPX. Red points represent the experimental data, the blue curve represent the estimated toxicokinetic curve and the transparent blue band correspond to the credibility interval of the model. 
#| fig-label: fig-EPXdatapredfull
#| fig-width: 10
#| fig-height: 20

dObs_ind_plot <- dObs_ind |> 
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

alpha_point <- 0.5

p_CiEPX <- ggplot()+
  geom_line(
    data=df_mod_CiEPX_ind_t,
    aes(
      x=Time,
      y= low,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX_ind_t,
    aes(
      x=Time,
      y= up,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX_ind_t,
    aes(
      x=Time,
      y= predict.endpoint,
      group = ID
      ),
    color = col_EPX,
    lwd=1
    )+
  geom_ribbon(
    data=df_mod_CiEPX_ind_t, 
    aes(
      x=Time, 
      ymax= up, 
      ymin= low,
      group = ID
      ),
    fill = col_EPX,
    alpha=0.1
    )+
  geom_point(
    data = dObs_ind_plot,
    aes(
      x = Time,
      y = CiEPX_obs
    ),
    size = 2,
    alpha = 0.7,
    color = col_red
  )+
  facet_wrap(
    ~ID,
    ncol = 4,
    scales = "free_x"
    )+
  labs(
    x = "Time (days)",
    y = "CiEPX (ng/g)"
  )+
  lims(y=c(0, 300))+
  theme_minimal()

p_CiEPX 

```

```{r, include = F}
ggsave(
  filename="TK_EPX_comptrajpred.png", 
  plot=p_CiEPX , 
  width=10, height = 20, 
  path=here::here("fig/TK/")
  )
ggsave(
  filename="TK_EPX_comptrajpred.svg", 
  plot=p_CiEPX , 
  width=10, height = 20, 
  path=here::here("fig/TK/")
  )
```

```{r EPXpredcurvesdataW, message=F, warning=F}
#| fig-cap: Weight predictions
#| fig-label: fig-EPXdatapredfullW
#| fig-width: 10
#| fig-height: 20

alpha_point <- 0.5

p_W <- ggplot()+
  geom_line(
    data=df_mod_Weight_ind_t,
    aes(
      x=Time,
      y= low,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_Weight_ind_t,
    aes(
      x=Time,
      y= up,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_Weight_ind_t,
    aes(
      x=Time,
      y= predict.endpoint,
      group = ID
      ),
    color = col_EPX,
    lwd=1
    )+
  geom_ribbon(
    data=df_mod_Weight_ind_t, 
    aes(
      x=Time, 
      ymax= up, 
      ymin= low,
      group = ID
      ),
    fill = col_EPX,
    alpha=0.1
    )+
  geom_point(
    data = dObs_ind_plot,
    aes(
      x = Time,
      y = Weight_obs
    ),
    size = 2,
    alpha = 0.7,
    color = col_red
  )+
  facet_wrap(
    ~ID,
    ncol = 4,
    scales = "free"
    )+
  #lims(y=c(0, 1500))+
  labs(
    x = "Time (days)",
    y = "Weight (g)"
  )+
  theme_minimal()

p_W

```

```{r, include = F}
ggsave(
  filename="TK_EPX_comptrajpredW.png", 
  plot=p_W , 
  width=10, height = 20, 
  path=here::here("fig/TK/")
  )
ggsave(
  filename="TK_EPX_comptrajpredW.svg", 
  plot=p_W , 
  width=10, height = 20, 
  path=here::here("fig/TK/")
  )
```

### Simulation of the toxicodynamic in earthworms throughout the exposition

The goal here is to recreate the concentration dynamic in the average earthworm during our exposition scheme but without the fasting phase that was required for chemical analysis and during which elimination was happening.

```{bash, results=F, eval=F}
pwd
cd ..
cd ..
cd mod/TK_EPX
pwd
./mcsim.m_TK_EPX TK_EPX_Setpoint.in
wait
```

```{r EPXreadSetpoint, message=F, warning=F}

Sim.Res <- as.data.frame(fread(here::here(path_mod_EPX, "Setpoints.out"),sep="\t"))
  Time_pred = seq( 0, 42, 0.01) # A changer !!!
  
  Nom_Endpoints =c("Weight_1", "CiEPX_1")
  Nsortie = 2
  MPV = IC_min = IC_max = Endpoint = index = NULL

  for (i in 1:length(Nom_Endpoints)){
    
    index =grep(paste("^",Nom_Endpoints[i],"\\.", sep="") , colnames(Sim.Res), fixed=FALSE )
    
    Data_sim = as.matrix( Sim.Res[ , index] )
    
    MPV    = c(  MPV,  as.numeric( Data_sim[nrow(Data_sim), ] ) )
    IC_min = c(IC_min,  apply(Data_sim, 2, quantile,  0.025) )
    IC_max = c(IC_max,  apply(Data_sim, 2, quantile,  0.975) ) 
    
    Endpoint = c(Endpoint, rep(Nom_Endpoints[i], ncol(Data_sim)))

    }

  df_mod <- data.frame(predict.endpoint = MPV,
                       Time    = c( rep(Time_pred, Nsortie))  ,
                       low     = IC_min,
                       up      = IC_max,
                       Endpt   = Endpoint,
                       Experiment = c(rep(rep("Experience 1", length(Time_pred)), Nsortie)))
  
df_mod_Weight <- subset(df_mod, Endpt == "Weight_1")
df_mod_CiEPX <- subset(df_mod, Endpt == "CiEPX_1") 
  
  # length(MPV)
  # length(df_Cin$Time)
  # length(Endpoint)
  # length(df_Cin$Experiment)
   
```

```{r EPXpredcurves, message=F, warning=F}
#| fig-cap: Estimated toxicokinetic of the EPX concentration in earthworms exposed to 0.1 mg/kg of EPX. Blue points represent the experimental data, the blue curve represents the estimated toxicokinetic curve and the transparent blue band corresponds to the credibility interval of the model. 
#| fig-label: fig-EPXcurvemod
#| fig-width: 8
#| fig-height: 4

alpha_point <- 0.5

p_CiEPX <- ggplot()+
  geom_line(
    data=df_mod_CiEPX,
    aes(
      x=Time,
      y= low
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX,
    aes(
      x=Time,
      y= up
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX,
    aes(
      x=Time,
      y= predict.endpoint
      ),
    color = col_EPX,
    lwd=1
    )+
  geom_ribbon(
    data=df_mod_CiEPX, 
    aes(
      x=Time, 
      ymax= up, 
      ymin= low
      ),
    fill = col_EPX,
    alpha=0.1
    )+
  labs(
    x = "Time (days)",
    y = "Internal EPX concentration (ng/g)"
  )+
  theme_minimal()

p <- p_CiEPX 
p

```

```{r, include = F}
  ggsave(
    filename="TK_EPX_predcurves.png", 
    plot=p, 
    width=3, height = 2.5, 
    path=here::here("fig/TK/")
    )
  ggsave(
    filename="TK_EPX_predcurves.svg", 
    plot=p, 
    width=6, height = 4, 
    path=here::here("fig/TK/")
    )
```

<!-- ```{r, warning = F, message = F} -->

<!-- #| fig-cap: Estimated toxicokinetic of IMD & EPX concentration in earthworms exposed to 100 ng/g of IMD and 1000 ng/g of EPX, respectively (IMD in dark blue and EPX in light blue). Estimated toxicokinetic of the EPX concentration in earthworms exposed to 0.1 mg/kg of EPX. Points represent the experimental data, the curve represents the estimated toxicokinetic curve and the transparent band corresponds to the credibility interval of the model.  -->

<!-- #| fig-label: fig-EPXIMD -->

<!-- #| fig-width: 8 -->

<!-- #| fig-height: 4 -->

<!-- p <- p_CiIMD + p_CiEPX -->

<!-- p -->

<!-- ``` -->

<!-- ```{r, include=F} -->

<!-- ggsave( -->

<!--   filename="TK_IMDEPX_predcurves.png",  -->

<!--   plot=p,  -->

<!--   width=10, height = 4,  -->

<!--   path=here::here("fig/TK/") -->

<!--   ) -->

<!-- ggsave( -->

<!--   filename="TK_IMDEPX_predcurves.svg",  -->

<!--   plot=p,  -->

<!--   width=10, height = 4,  -->

<!--   path=here::here("fig/TK/") -->

<!--   ) -->

<!-- ``` -->

<!-- ```{r, warning = F, message = F} -->

<!-- #| fig-cap: Results of the model fit on experimental data. Predicted values are represented with points with their respective credibility interval of 95%. Thin black and grey lines represent the 2-folds and 5-fold changes, respectively. The thicker black line represents the identity line.  -->

<!-- #| label: fig-IMDEPXpredobs -->

<!-- #| fig-height: 4 -->

<!-- #| fig-width: 6 -->

<!-- p <- p_CiIMD_zoom_predobs + p_CiEPX_predobs -->

<!-- p -->

<!-- ``` -->

<!-- ```{r, include=F} -->

<!-- ggsave( -->

<!--   filename="TK_IMDEPX_predobs.jpg",  -->

<!--   plot=p,  -->

<!--   width=8, height = 4,  -->

<!--   path=here::here("fig/TK/") -->

<!--   ) -->

<!-- ggsave( -->

<!--   filename="TK_IMDEPX_predobs.png",  -->

<!--   plot=p,  -->

<!--   width=8, height = 4,  -->

<!--   path=here::here("fig/TK/") -->

<!--   ) -->

<!-- ggsave( -->

<!--   filename="TK_IMDEPX_predobs.svg",  -->

<!--   plot=p,  -->

<!--   width=8, height = 4,  -->

<!--   path=here::here("fig/TK/") -->

<!--   ) -->

<!-- ``` -->

<button class="accordion-button" type="button" data-bs-toggle="collapse" data-bs-target="#collapseOne">

<b> Session Information </b>

</button>

:::: {#collapseOne .accordion-collapse .collapse}
<div>

```{r}
sessionInfo()
```

</div>
::::
