```{r lib, include=F}
library(here)
source(file = here::here("functions/fun.R"))
f_load_libraries_colors()
col_Molecule <- rev(col_Molecule)
```

# Toxicokinetics of Epoxiconazole

## Results of the experiment

### Data importation

Notations :

-   `Date_start` : Start of the experiement (t0)
-   `Molecule` : Substance to which the earthworm is exposed
-   `Dose` : Exposure dose (mg/kg)
-   `ID_recipient` : Recipient in which the soil was prepared
-   `ID_camp` : ID of the earthworm campagne and generation (see XXX for more information)
-   `ID` : ID of the earthworm
-   `Nb_rep` : Identification number of the replicate
-   `Time_point` : Time point to which the earthworm is dedicated
-   `Phase` : Uptake or Elimination phase
-   `Time_introduction_D0` : Time of the day when the earthworm was introduced into his contaminated cosm
-   `w0` : Body weight at t0
-   `w_Tp` : Body weight at the given time point
-   `w_frozen` : Body weight before congelation
-   `C_worm` : Measured concentration of the substance in the earthworm
-   `C_soil` : Measured concentration of the substance in the soil at the given time point

```{r data, warning=F, message=F}

Levels_time_points <- c("0,25b", "1", "1b", "2", "3", "3b", as.character(seq(4,42,1)))


df_TK_EPX <- f_read_data_TK("EPX") %>%
  mutate(across(where(is.numeric), ~ na_if(.x, -1)))


df_TK_EPX <- df_TK_EPX |> 
  mutate(
    Time = t,
    CiIMD = C_worm_IMD,
    CiEPX = C_worm_EPX,
    Weight = Weight_nog,
    Time_point_f = as.factor(Time_point)
  ) |> 
  dplyr::select(Time, CiEPX, CiIMD, Weight, w, Molecule, ID, expo, Time_point_f, Nb_rep, Experiment) |> 
  mutate(
    CiEPX = na_if(CiEPX, -1),
    CiIMD = na_if(CiIMD, -1)
    )|> 
  mutate(
    Time_point_f = fct_relevel(Time_point_f, Levels_time_points)
  )

df_TK_EPX_mean <- df_TK_EPX |> 
  dplyr::select(-ID) |> 
  group_by(Time) |> 
  summarise(
    CiEPX = exp(mean(log(CiEPX[CiEPX > 0]), na.rm = TRUE)),
    CiIMD = exp(mean(log(CiIMD[CiIMD > 0]), na.rm = TRUE)),
    Weight = mean(Weight, na.rm = TRUE),
    w = mean(w, na.rm = TRUE),
    expo = mean(expo),
    .groups = "drop"
  ) |> 
  mutate(Molecule = "EPX")
```

### Initial state

```{r D0}
summary(subset(df_TK_EPX, Time==0 & Experiment == "TK"))
summary(subset(df_TK_EPX, Time==0 & Experiment == "TKBIS"))
```

```{r, warning=F, message=F}
#| fig-cap: Initial weights (with gut content) of earthworms. 
#| label: fig-init
#| fig-width: 8
#| fig-height: 4

# Weights at t=0
plot_D0 <- ggplot(
  data=subset(df_TK_EPX, Time==0), 
  aes(
    x=Time_point_f, 
    y=w, 
    color=Molecule, 
    fill=Molecule
    )
  )+

  geom_boxplot(alpha=0.2)+
  geom_dotplot(
    binaxis='y', 
    stackdir='center', 
    dotsize=0.7, 
    alpha=0.7
    )+
  facet_wrap(~Molecule+Experiment, ncol=2, scales="free_x")+
  
  scale_color_manual(values=rev(col_Molecule))+
  scale_fill_manual(values=rev(col_Molecule))+

  labs(x="Dose (mg/kg)", y="Weight (mg)")+
  

  theme_classic(14)+
  theme(
    legend.position = "none", 
    legend.title=element_text(size=sizetitle-2,face="bold"),
    legend.text = element_text(size=sizetitle-2,face="plain"),
    
    title=element_text(size=sizetitle, face="bold"), 
    
    axis.title.x = element_blank(),
    axis.title.y = element_text(size=sizetitle,face="plain"),
    
    axis.text.x = element_text(size=sizetitle-4),
    axis.line.x=element_blank(),
    axis.ticks.x=element_blank(),
    
    
    strip.background = element_rect(
      color="black", 
      #fill=Nord_snow[3], 
      size=0, 
      linetype="solid"
      ),
    strip.text = element_text(face = "bold")
    )
plot_D0
```

```{r saveinit, include=F}
ggsave(
  filename="TK_EPX_initial_weights.png", 
  plot=plot_D0, 
  width=8, 
  height = 4, 
  path=here::here("fig/TK_single")
  )
```

### Growth curves

```{r, warning=F, message=F}
#| fig-cap: Evolution of earthworms body weight before and after fasting. 
#| label: fig-growthcurves
#| fig-width: 8
#| fig-height: 8


col_exposure <- c(Nord_aurora[2], Nord_aurora[3], Nord_aurora[4])
ID_tri <- c(1, 9, 17, 25, 33, 41, 49, 57, 65, 73, 81, 89, 97, 107, 115, 123, 131, 134, 137)

df_TK_EPX_plot <- df_TK_EPX |> 
  filter(!is.na(Weight))

y_segment <- 1.5

df_phases <- df_TK_EPX |> 
  filter(ID %in% ID_tri)|>
  arrange(Time_point_f, Time) |>
  group_by(Time_point_f) |>
  mutate(
    row = row_number(),
    t_start = Time,
    t_end = lead(Time),  
    segment = row,
    y = y_segment
  ) |>
  filter(!is.na(t_end)) |>  
  dplyr::select(Time_point_f, segment, t_start, t_end, y, Experiment) |>
  ungroup() |> 
  mutate(
    Time_point = as.numeric(as.character(Time_point_f)),
    Phase = case_when(
      (segment == 1 & Time_point <= 21) ~ 1,
      (segment == 2 & Time_point <= 21) ~ 3,
      (segment == 1 & Time_point > 21) ~ 1,
      (segment == 2 & Time_point > 21) ~ 2,
      (segment == 3 & Time_point > 21) ~ 3,
      (Experiment == "TKBIS" & segment == 1)~1,
      (Experiment == "TKBIS" & segment == 2)~3
    )
  ) |> 
  mutate(
    Time_point_f = fct_relevel(Time_point_f, Levels_time_points)
  )


p_EPX <- ggplot() +
  
  geom_segment(
    data = df_phases,
    aes(
      x = t_start,
      xend = t_end,
      y = y,
      yend = y,
      color = factor(Phase)
    ),
    linewidth = 2,
    alpha = 0.7
  ) +
  
  geom_line(
    data = df_TK_EPX_plot,
    aes(
      x = Time,
      y = w,
      group = ID
      ),
    alpha=1,
    color = col_EPX,
    linetype = "dashed"
    ) +
  geom_point(
    data = df_TK_EPX,
    aes(
      x = Time,
      y = w,
      group = ID
      ),
    alpha=0.5,
    color = col_EPX
    ) +

  facet_wrap(~Time_point_f)+
  labs(
    title = "Growth Curves",
    x = "Time (days)",
    y = "Weight",
    color = ""
  ) +
  scale_color_manual(
    values = col_exposure,
    label = c("Uptake", "Elimination", "Depuration"),
    name = "Phase"
    )+
  theme_minimal(base_size = 12) +  # Thème minimaliste
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    legend.position = "top",
    strip.background = element_rect(
      color="black", 
      fill=Nord_snow[3], 
      size=0, 
      linetype="solid"
      ),
    strip.text = element_text(face = "bold")
  )

p_EPX
```

```{r savegrowthcuves, include=F}
ggsave(
  filename="TK_EPX_growth_curves.png", 
  plot=p_EPX, 
  width=8, 
  height = 4, 
  path=here::here("fig/TK_single")
  )
ggsave(
  filename="TK_EPX_growth_curves.svg", 
  plot=p_EPX, 
  width=8, 
  height = 4, 
  path=here::here("fig/TK_single")
  )
```

### Measured internal concentrations

```{r, message=F, warning=F}
#| fig-cap: Measurements of EPX concentration in earthworms exposed to 10 mg/kg of EPX and related weight measurement of earthworms. Points represent the experimental data, the blue curve and the transparent blue band are produced with geom_smooth. 
#| fig-label: fig-curvesmooth
#| fig-width: 8
#| fig-height: 4

p <- ggplot(
  data = df_TK_EPX |> filter(Time!=0 & !is.na(CiEPX)),
  aes(
    x = Time
  )
  )+
  geom_point(
    mapping = aes(
      y = CiEPX,
    color = Experiment,
    fill = Experiment
    )
  )+
  facet_wrap(~Molecule, ncol = 2, scales = "free")+
  scale_color_manual(values = c(col_EPX, Nord_aurora[4]))+
  scale_fill_manual(values = c(col_EPX, Nord_aurora[4]))+
  labs(
    x = "Time (days)",
    y = "Concentration in earthworm (ng/g)"
  )+
  #lims(x=c(0,5))+
  theme_minimal()
p
```

## Modeling of the toxicokinetics

Names of models :

-   C1 : One compartement only.
-   C1P : One compartment and exposure in Petri dishes via gut content.
-   C2 : Two compartements.
-   C2P : Two compartments and exposure in Petri dishes via gut content.

### In files creation for MCMC

```{r increation, message=F, warning=F}
#| code-show: show

Molecule <- "EPX"

########## C1 ################################################################

path_mod_EPX_C1 <- here::here("mod/TK_EPX_C1")
path_fig_C1 <- here::here("fig/TK_single/EPX_C1/")

Nb_Iter <- 100000
seeds <- c(C1 = 3333, C2 = 6656, C3 = 111222)

text_priors <- "Distrib(kuEPX,     LogUniform,   0.00001, 10000); # min, max 
Distrib(keEPX,    LogUniform,   0.00001, 10000); # min, max

Distrib(a_growth,  TruncNormal,   0.005,   0.005,    -0.5,    1); # mean, sd, min, max
Distrib (Vr_a_growth,  TruncNormal, 0.0015, 0.01, 0, 1);

Distrib(Sigma_W,     TruncNormal,  0.03, 0.01, 0.0001, 1);
Distrib(Sigma_CiEPX, TruncNormal,  3.0, 3.0,    1, 1000);"

text_likelihood <- "Likelihood(CiEPX,  LogNormal, Prediction(CiEPX),  Sigma_CiEPX);  # Calcul des vraisemblances (geometric mean, geometric standard deviation)
Likelihood(Weight, Normal,    Prediction(Weight), Sigma_W);      # Calcul des vraisemblances"

text_param_ind <- "Distrib(a_growth,  TruncNormal, a_growth,  Vr_a_growth, -1.0, 1);"

f_In_tot(path_mod_EPX_C1, Molecule, text_priors, text_likelihood, text_param_ind, Nb_Iter, seeds)

########## C1P ################################################################

path_mod_EPX_C1P <- here::here("mod/TK_EPX_C1P")
path_fig_C1P <- here::here("fig/TK_single/EPX_C1P/")

Nb_Iter <- 300000
seeds <- c(C1 = 333266, C2 = 660660, C3 = 110110) # Done on CEA servers (CCRT)

text_priors <- "Distrib(kuEPX,     LogUniform,   0.00001, 100000); # min, max 
Distrib(keEPX,    LogUniform,   0.00001, 100000); # min, max

Distrib(phi,     Uniform,   0.0, 1); # min, max

Distrib(a_growth,  TruncNormal,   0.005,   0.005,    -0.5,    1); # mean, sd, min, max
Distrib (Vr_a_growth,  TruncNormal, 0.0015, 0.01, 0, 1);

Distrib(Sigma_W,     TruncNormal,  0.03, 0.01, 0.0001, 1);
Distrib(Sigma_CiEPX, TruncNormal,  3.0, 3.0,    1, 1000);"

text_likelihood <- "Likelihood(CiEPX,  LogNormal, Prediction(CiEPX),  Sigma_CiEPX);  # Calcul des vraisemblances (geometric mean, geometric standard deviation)
Likelihood(Weight, Normal,    Prediction(Weight), Sigma_W);      # Calcul des vraisemblances"

text_param_ind <- "Distrib(a_growth,  TruncNormal, a_growth,  Vr_a_growth, -1.0, 1);"

f_In_tot(path_mod_EPX_C1P, Molecule, text_priors, text_likelihood, text_param_ind, Nb_Iter, seeds)

########## C2 ################################################################

Molecule <- "EPX"
path_mod_EPX_C2 <- here::here("mod/TK_EPX_C2")
path_fig_C2 <- here::here("fig/TK_single/EPX_C2/")

Nb_Iter <- 100000
seeds <- c(C1 = 33033, C2 = 6666, C3 = 1201)

text_priors <- "Distrib(kuEPX,     LogUniform,   0.00001, 100000); # min, max 
Distrib(keEPX,    LogUniform,   0.00001, 100000); # min, max

Distrib(kperiph,     LogUniform,   0.00001, 100000); # min, max 

Distrib(a_growth,  TruncNormal,   0.005,   0.005,    -0.5,    1); # mean, sd, min, max
Distrib (Vr_a_growth,  TruncNormal, 0.0015, 0.01, 0, 1);

Distrib(Sigma_W,     TruncNormal,  0.03, 0.01, 0.0001, 1);
Distrib(Sigma_CiEPX, TruncNormal,  3.0, 3.0,    1, 1000);"

text_likelihood <- "Likelihood(CiEPX,  LogNormal, Prediction(CiEPX),  Sigma_CiEPX);  # Calcul des vraisemblances (geometric mean, geometric standard deviation)
Likelihood(Weight, Normal,    Prediction(Weight), Sigma_W);      # Calcul des vraisemblances"

text_param_ind <- "Distrib(a_growth,  TruncNormal, a_growth,  Vr_a_growth, -1.0, 1);"

f_In_tot(path_mod_EPX_C2, Molecule, text_priors, text_likelihood, text_param_ind, Nb_Iter, seeds)

########## C2P ################################################################

path_mod_EPX_C2P <- here::here("mod/TK_EPX_C2P")
path_fig_C2P <- here::here("fig/TK_single/EPX_C2P/")

Nb_Iter <- 300000
seeds <- c(C1 = 333266, C2 = 660660, C3 = 110110) # Done on CEA servers (CCRT)

text_priors <- "Distrib(kuEPX,     LogUniform,   0.00001, 100000); # min, max 
Distrib(keEPX,    LogUniform,   0.00001, 100000); # min, max

Distrib(kperiph,     LogUniform,   0.00001, 100000); # min, max
Distrib(phi,     Uniform,   0.0, 1); # min, max

Distrib(a_growth,  TruncNormal,   0.005,   0.005,    -0.5,    1); # mean, sd, min, max
Distrib (Vr_a_growth,  TruncNormal, 0.0015, 0.01, 0, 1);

Distrib(Sigma_W,     TruncNormal,  0.03, 0.01, 0.0001, 1);
Distrib(Sigma_CiEPX, TruncNormal,  3.0, 3.0,    1, 1000);"

text_likelihood <- "Likelihood(CiEPX,  LogNormal, Prediction(CiEPX),  Sigma_CiEPX);  # Calcul des vraisemblances (geometric mean, geometric standard deviation)
Likelihood(Weight, Normal,    Prediction(Weight), Sigma_W);      # Calcul des vraisemblances"

text_param_ind <- "Distrib(a_growth,  TruncNormal, a_growth,  Vr_a_growth, -1.0, 1);"

f_In_tot(path_mod_EPX_C2P, Molecule, text_priors, text_likelihood, text_param_ind, Nb_Iter, seeds)

# ./mcsim.m_TK_EPX TK_EPX_C1.in
```

An example of how to run the models MCMC is given in the bash code block below. You need to be in the right folder to launch a given model.

```{bash, eval=F, execute=F}
pwd
cd ..
cd ..
cd mod/TK_EPX
pwd

makemcsim m_TK_EPX.model &
for j in $(seq 1 3); do
./mcsim.m_TK_EPX TK_EPX_C${j}.in
done
```

The first step is to retrieve the information of the MCMC simulation experiments.

The inputs :

-   Input files must a name like "xxxxx.1.in"
-   Output files must a name like "xxxxx.1.out"

### Get MCMC results

```{r EPXreadMCMC, message=F, warning=F, results='hidden'}

########## C1 ################################################################

MCMC_out_EPX_C1 <- f_MCSim_ind(path_mod_EPX_C1)

NC_C1 <- MCMC_out_EPX_C1$NC
Nb_param_C1 <- MCMC_out_EPX_C1$Nb_param
Nb_experiment_C1 <- MCMC_out_EPX_C1$Nb_experiment
Nb_iter_kept_C1 <- MCMC_out_EPX_C1$Nb_iter_kept
N_iter_setpoint_C1 <- MCMC_out_EPX_C1$N_iter_setpoint
L_parameters_C1 <- unique(MCMC_out_EPX_C1$Priors$Nom)

########## C1P ################################################################

MCMC_out_EPX_C1P <- f_MCSim_ind(path_mod_EPX_C1P)

NC_C1P <- MCMC_out_EPX_C1P$NC
Nb_param_C1P <- MCMC_out_EPX_C1P$Nb_param
Nb_experiment_C1P <- MCMC_out_EPX_C1P$Nb_experiment
Nb_iter_kept_C1P <- MCMC_out_EPX_C1P$Nb_iter_kept
N_iter_setpoint_C1P <- MCMC_out_EPX_C1P$N_iter_setpoint
L_parameters_C1P <- unique(MCMC_out_EPX_C1P$Priors$Nom)

########## C2 ################################################################

MCMC_out_EPX_C2 <- f_MCSim_ind(path_mod_EPX_C2)

NC_C2 <- MCMC_out_EPX_C2$NC
Nb_param_C2 <- MCMC_out_EPX_C2$Nb_param
Nb_experiment_C2 <- MCMC_out_EPX_C2$Nb_experiment
Nb_iter_kept_C2 <- MCMC_out_EPX_C2$Nb_iter_kept
N_iter_setpoint_C2 <- MCMC_out_EPX_C2$N_iter_setpoint
L_parameters_C2 <- unique(MCMC_out_EPX_C2$Priors$Nom)

########## C2P ################################################################

MCMC_out_EPX_C2P <- f_MCSim_ind(path_mod_EPX_C2P)

NC_C2P <- MCMC_out_EPX_C2P$NC
Nb_param_C2P <- MCMC_out_EPX_C2P$Nb_param
Nb_experiment_C2P <- MCMC_out_EPX_C2P$Nb_experiment
Nb_iter_kept_C2P <- MCMC_out_EPX_C2P$Nb_iter_kept
N_iter_setpoint_C2P <- MCMC_out_EPX_C2P$N_iter_setpoint
L_parameters_C2P <- unique(MCMC_out_EPX_C2P$Priors$Nom)

```

We can retrieve different information from the models :

-   C1
    -   The number of chains used : `r NC_C1`
    -   The number of parameters : `r Nb_param_C1`
    -   The number of experiments : `r Nb_experiment_C1`
    -   The number of last iterations used to describe the posterior distribution : `r Nb_iter_kept_C1`
    -   The number of last iterations used to create the `tab_setpoint.out` file : `r N_iter_setpoint_C1`
-   C1P
    -   The number of parameters : `r Nb_param_C1P`
-   C2
    -   The number of parameters : `r Nb_param_C2`
-   C2P
    -   The number of parameters : `r Nb_param_C2P`

### Priors used for the model

::: panel-tabset
## C1

```{r EPXreadpriorsC1, message = F, warning = F}
#| tbl-cap: Priors used for the model
#| tbl-label: tbl-EPXPriorsC1

colnames(MCMC_out_EPX_C1$Priors) <- c("Nom", "Distribution", "P1", "P2", "P3", "P4")

MCMC_out_EPX_C1$Priors |> datatable(
  options = list(
    dom = 't',
    autoWidth = TRUE,
    columnDefs = list(
      list(className = 'dt-left', targets = "_all")
      )
    ),
  class="hover"
  )

#MCMC_out_EPX$Priors
```

```{r EPXpriorsC1, message=F, warning=F}
#| fig-cap: Distributions of the priors.
#| label: fig-EPXpriorC1
#| fig-height: 6
#| fig-width: 8

n_samples <- 1e6 # Simulation of the distribution
col_prior <- Nord_polar[4]
alpha_prior <- 0.5

df_priors_dist_C1 <- MCMC_out_EPX_C1$Priors |> 
  dplyr::select(Nom, Distribution, P1, P2, P3, P4) |> 
  rowwise() |> 
  mutate(samples = case_when(
    Distribution == "Uniform" ~ list(runif(n_samples, min = P1, max = P2)),
    Distribution == "Normal" ~ list(rnorm(n_samples, mean = P1, sd = P2)),
    Distribution == "LogUniform" ~ list(exp(runif(n_samples, min = log(P1), max = log(P2)))),
    Distribution == "TruncNormal" ~ list(rtruncnorm(n_samples, a = P3, b = P4, mean = P1, sd = P2))
  )) |> 
  unnest(samples) |> 
  filter(!(Nom %in% c("kuEPX", "keEPX","kcomp_in", "kcomp_out") & samples > 0.01))

p_priors <- ggplot() +
  facet_wrap(~Nom, scales = "free")+
  
  stat_halfeye(
    data = df_priors_dist_C1, 
    aes(
       x = samples
       ),
    alpha = alpha_prior,
    fill = col_prior,
    color = col_prior,
    normalize = "xy" 
    ) +
  
  labs(
    title = "Priors distributions", 
    x = "Parameter value", 
    y = "Density"
    ) +
  theme_minimal()

p_priors 

```

```{r savepriorC1, include = F}
ggsave(
  filename="TK_EPX_priors.png", 
  plot=p_priors, 
  width=8, height = 6, 
  path=path_fig_C1
  )
ggsave(
  filename="TK_EPX_priors.svg", 
  plot=p_priors, 
  width=8, height = 6, 
  path=path_fig_C1
  )
```

## C1P

```{r EPXreadpriorsC1P, message = F, warning = F}
#| tbl-cap: Priors used for the model
#| tbl-label: tbl-EPXPriorsC1P

colnames(MCMC_out_EPX_C1P$Priors) <- c("Nom", "Distribution", "P1", "P2", "P3", "P4")

MCMC_out_EPX_C1P$Priors |> datatable(
  options = list(
    dom = 't',
    autoWidth = TRUE,
    columnDefs = list(
      list(className = 'dt-left', targets = "_all")
      )
    ),
  class="hover"
  )

#MCMC_out_EPX$Priors
```

```{r EPXpriorsC1P, message=F, warning=F}
#| fig-cap: Distributions of the priors.
#| label: fig-EPXpriorC1P
#| fig-height: 6
#| fig-width: 8

n_samples <- 1e6 # Simulation of the distribution
col_prior <- Nord_polar[4]
alpha_prior <- 0.5

df_priors_dist_C1P <- MCMC_out_EPX_C1P$Priors |> 
  dplyr::select(Nom, Distribution, P1, P2, P3, P4) |> 
  rowwise() |> 
  mutate(samples = case_when(
    Distribution == "Uniform" ~ list(runif(n_samples, min = P1, max = P2)),
    Distribution == "Normal" ~ list(rnorm(n_samples, mean = P1, sd = P2)),
    Distribution == "LogUniform" ~ list(exp(runif(n_samples, min = log(P1), max = log(P2)))),
    Distribution == "TruncNormal" ~ list(rtruncnorm(n_samples, a = P3, b = P4, mean = P1, sd = P2))
  )) |> 
  unnest(samples) |> 
  filter(!(Nom %in% c("kuEPX", "keEPX","kcomp_in", "kcomp_out") & samples > 0.01))

p_priors <- ggplot() +
  facet_wrap(~Nom, scales = "free")+
  
  stat_halfeye(
    data = df_priors_dist_C1P, 
    aes(
       x = samples
       ),
    alpha = alpha_prior,
    fill = col_prior,
    color = col_prior,
    normalize = "xy" 
    ) +
  
  labs(
    title = "Priors distributions", 
    x = "Parameter value", 
    y = "Density"
    ) +
  theme_minimal()

p_priors 

```

```{r savepriorC1P, include = F}
ggsave(
  filename="TK_EPX_priors.png", 
  plot=p_priors, 
  width=8, height = 6, 
  path=path_fig_C1P
  )
ggsave(
  filename="TK_EPX_priors.svg", 
  plot=p_priors, 
  width=8, height = 6, 
  path=path_fig_C1P
  )
```

## C2

```{r EPXreadpriorsC2, message = F, warning = F}
#| tbl-cap: Priors used for the model
#| tbl-label: tbl-EPXPriorsC2

colnames(MCMC_out_EPX_C2$Priors) <- c("Nom", "Distribution", "P1", "P2", "P3", "P4")

MCMC_out_EPX_C2$Priors |> datatable(
  options = list(
    dom = 't',
    autoWidth = TRUE,
    columnDefs = list(
      list(className = 'dt-left', targets = "_all")
      )
    ),
  class="hover"
  )

#MCMC_out_EPX$Priors
```

```{r EPXpriorsC2, message=F, warning=F}
#| fig-cap: Distributions of the priors.
#| label: fig-EPXpriorC2
#| fig-height: 6
#| fig-width: 8

n_samples <- 1e6 # Simulation of the distribution
col_prior <- Nord_polar[4]
alpha_prior <- 0.5

df_priors_dist_C2 <- MCMC_out_EPX_C2$Priors |> 
  dplyr::select(Nom, Distribution, P1, P2, P3, P4) |> 
  rowwise() |> 
  mutate(samples = case_when(
    Distribution == "Uniform" ~ list(runif(n_samples, min = P1, max = P2)),
    Distribution == "Normal" ~ list(rnorm(n_samples, mean = P1, sd = P2)),
    Distribution == "LogUniform" ~ list(exp(runif(n_samples, min = log(P1), max = log(P2)))),
    Distribution == "TruncNormal" ~ list(rtruncnorm(n_samples, a = P3, b = P4, mean = P1, sd = P2))
  )) |> 
  unnest(samples) |> 
  filter(!(Nom %in% c("kuEPX", "keEPX","kcomp_in", "kcomp_out") & samples > 0.01))

p_priors <- ggplot() +
  facet_wrap(~Nom, scales = "free")+
  
  stat_halfeye(
    data = df_priors_dist_C2, 
    aes(
       x = samples
       ),
    alpha = alpha_prior,
    fill = col_prior,
    color = col_prior,
    normalize = "xy" 
    ) +
  
  labs(
    title = "Priors distributions", 
    x = "Parameter value", 
    y = "Density"
    ) +
  theme_minimal()

p_priors 

```

```{r savepriorC2, include = F}
ggsave(
  filename="TK_EPX_priors.png", 
  plot=p_priors, 
  width=8, height = 6, 
  path=path_fig_C2
  )
ggsave(
  filename="TK_EPX_priors.svg", 
  plot=p_priors, 
  width=8, height = 6, 
  path=path_fig_C2
  )
```

## C2P

```{r EPXreadpriorsC2P, message = F, warning = F}
#| tbl-cap: Priors used for the model
#| tbl-label: tbl-EPXPriorsC2P

colnames(MCMC_out_EPX_C2P$Priors) <- c("Nom", "Distribution", "P1", "P2", "P3", "P4")

MCMC_out_EPX_C2P$Priors |> datatable(
  options = list(
    dom = 't',
    autoWidth = TRUE,
    columnDefs = list(
      list(className = 'dt-left', targets = "_all")
      )
    ),
  class="hover"
  )

#MCMC_out_EPX$Priors
```

```{r EPXpriorsC2P, message=F, warning=F}
#| fig-cap: Distributions of the priors.
#| label: fig-EPXpriorC2P
#| fig-height: 6
#| fig-width: 8

n_samples <- 1e6 # Simulation of the distribution
col_prior <- Nord_polar[4]
alpha_prior <- 0.5

df_priors_dist_C2P <- MCMC_out_EPX_C2P$Priors |> 
  dplyr::select(Nom, Distribution, P1, P2, P3, P4) |> 
  rowwise() |> 
  mutate(samples = case_when(
    Distribution == "Uniform" ~ list(runif(n_samples, min = P1, max = P2)),
    Distribution == "Normal" ~ list(rnorm(n_samples, mean = P1, sd = P2)),
    Distribution == "LogUniform" ~ list(exp(runif(n_samples, min = log(P1), max = log(P2)))),
    Distribution == "TruncNormal" ~ list(rtruncnorm(n_samples, a = P3, b = P4, mean = P1, sd = P2))
  )) |> 
  unnest(samples) |> 
  filter(!(Nom %in% c("kuEPX", "keEPX","kcomp_in", "kcomp_out") & samples > 0.01))

p_priors <- ggplot() +
  facet_wrap(~Nom, scales = "free")+
  
  stat_halfeye(
    data = df_priors_dist_C2P, 
    aes(
       x = samples
       ),
    alpha = alpha_prior,
    fill = col_prior,
    color = col_prior,
    normalize = "xy" 
    ) +
  
  labs(
    title = "Priors distributions", 
    x = "Parameter value", 
    y = "Density"
    ) +
  theme_minimal()

p_priors 

```

```{r savepriorC2P, include = F}
ggsave(
  filename="TK_EPX_priors.png", 
  plot=p_priors, 
  width=8, height = 6, 
  path=path_fig_C2P
  )
ggsave(
  filename="TK_EPX_priors.svg", 
  plot=p_priors, 
  width=8, height = 6, 
  path=path_fig_C2P
  )
```
:::

### Chains

::: panel-tabset
## C1

```{r EPXChainsC1, message=F, warning=F}
#| fig-cap: Parameters chains. Only the first iteration and the last `r Nb_iter_kept` are represented.
#| label: fig-EPXchainsC1
#| fig-height: 5
#| fig-width: 8

p_chains <-  
  ggplot(
    data = MCMC_out_EPX_C1$Chains |> filter(Iteration > 1), 
    aes(
      x = Iteration, 
      y = value, 
      color = as.factor(Chain), 
      group = as.factor(Chain)
      )
  )+
  geom_line(alpha=0.7)+
  scale_y_log10()+
  facet_wrap(~Parameter, scales = "free", ncol = 2)+
  
  scale_color_manual(name = "Chains", values = nord(palette = "frost"))+
  
  theme_bw()+
  theme(
    legend.position = "right", 
    title=element_text(size=12, face="plain"), 
    axis.title.x = element_text(face="plain"),
    strip.background = element_rect(fill="white")
    )

p_chains
  
```

```{r savechainsC1, include = F}
ggsave(
  filename="TK_EPX_chains.png", 
  plot=p_chains, 
  width=8, height = 5, 
  path=path_fig_C1
  )
ggsave(
  filename="TK_EPX_chains.svg", 
  plot=p_chains, 
  width=8, height = 5, 
  path=path_fig_C1
  )
```

## C1P

```{r EPXChainsC1P, message=F, warning=F}
#| fig-cap: Parameters chains. Only the first iteration and the last `r Nb_iter_kept` are represented.
#| label: fig-EPXchainsC1P
#| fig-height: 5
#| fig-width: 8

p_chains <-  
  ggplot(
    data = MCMC_out_EPX_C1P$Chains|> filter(Iteration > 1), 
    aes(
      x = Iteration, 
      y = value, 
      color = as.factor(Chain), 
      group = as.factor(Chain)
      )
  )+
  geom_line(alpha=0.7)+
  scale_y_log10()+
  facet_wrap(~Parameter, scales = "free", ncol = 2)+
  
  scale_color_manual(name = "Chains", values = nord(palette = "frost"))+
  
  theme_bw()+
  theme(
    legend.position = "right", 
    title=element_text(size=12, face="plain"), 
    axis.title.x = element_text(face="plain"),
    strip.background = element_rect(fill="white")
    )

p_chains
  
```

```{r savechainsC1P, include = F}
ggsave(
  filename="TK_EPX_chains.png", 
  plot=p_chains, 
  width=8, height = 5, 
  path=path_fig_C1P
  )
ggsave(
  filename="TK_EPX_chains.svg", 
  plot=p_chains, 
  width=8, height = 5, 
  path=path_fig_C1P
  )
```

## C2

```{r EPXChainsC2, message=F, warning=F}
#| fig-cap: Parameters chains. Only the first iteration and the last `r Nb_iter_kept` are represented.
#| label: fig-EPXchainsC2
#| fig-height: 5
#| fig-width: 8

p_chains <-  
  ggplot(
    data = MCMC_out_EPX_C2$Chains|> filter(Iteration > 1), 
    aes(
      x = Iteration, 
      y = value, 
      color = as.factor(Chain), 
      group = as.factor(Chain)
      )
  )+
  geom_line(alpha=0.7)+
  scale_y_log10()+
  facet_wrap(~Parameter, scales = "free", ncol = 2)+
  
  scale_color_manual(name = "Chains", values = nord(palette = "frost"))+
  
  theme_bw()+
  theme(
    legend.position = "right", 
    title=element_text(size=12, face="plain"), 
    axis.title.x = element_text(face="plain"),
    strip.background = element_rect(fill="white")
    )

p_chains
  
```

```{r savechainsC2, include = F}
ggsave(
  filename="TK_EPX_chains.png", 
  plot=p_chains, 
  width=8, height = 5, 
  path=path_fig_C2
  )
ggsave(
  filename="TK_EPX_chains.svg", 
  plot=p_chains, 
  width=8, height = 5, 
  path=path_fig_C2
  )
```

## C2P

```{r EPXChainsC2P, message=F, warning=F}
#| fig-cap: Parameters chains. Only the first iteration and the last `r Nb_iter_kept` are represented.
#| label: fig-EPXchainsC2P
#| fig-height: 5
#| fig-width: 8

p_chains <-  
  ggplot(
    data = MCMC_out_EPX_C2P$Chains|> filter(Iteration > 1), 
    aes(
      x = Iteration, 
      y = value, 
      color = as.factor(Chain), 
      group = as.factor(Chain)
      )
  )+
  geom_line(alpha=0.7)+
  scale_y_log10()+
  facet_wrap(~Parameter, scales = "free", ncol = 2)+
  
  scale_color_manual(name = "Chains", values = nord(palette = "frost"))+
  
  theme_bw()+
  theme(
    legend.position = "right", 
    title=element_text(size=12, face="plain"), 
    axis.title.x = element_text(face="plain"),
    strip.background = element_rect(fill="white")
    )

p_chains
  
```

```{r savechainsC2P, include = F}
ggsave(
  filename="TK_EPX_chains.png", 
  plot=p_chains, 
  width=8, height = 5, 
  path=path_fig_C2P
  )
ggsave(
  filename="TK_EPX_chains.svg", 
  plot=p_chains, 
  width=8, height = 5, 
  path=path_fig_C2P
  )
```
:::

We can also take a look at the likelihood and the deviance ratio.

::: panel-tabset
## C1

```{r EPXlikeC1, message=F, warning=F}
#| fig-cap: Evolution of likelihood and deviance ratio through the iterations.
#| label: fig-EPXlikeC1
#| fig-height: 4
#| fig-width: 8

p1 <- ggplot(
  MCMC_out_EPX_C1$df_LnPost_start, 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = c("1", "2", "3"), values = Nord_frost) +
  labs(
    x = "First half iterations", 
    y = "LnPosterior"
    ) +
  theme_minimal()

p2 <- ggplot(
  MCMC_out_EPX_C1$df_LnPost |> filter(iteration > 1), 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = c("1", "2", "3"), values = Nord_frost) +
  labs(
    x = paste(MCMC_out_EPX_C1$Nb_iter_kept, "last iterations"), 
    y = "LnPosterior"
    ) +
  theme_minimal()

p3 <- ggplot(
  MCMC_out_EPX_C1$df_Devc|> filter(iteration > 1), 
  aes(
    x = iteration, 
    y = RatioDeviance, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = c("1", "2", "3"), values = Nord_frost) +
  labs(
    x = paste(MCMC_out_EPX_C1$Nb_iter_kept, "last iterations"), 
    y = "Ratio Deviance"
    ) +
  theme_minimal()

p_LL <- p1 + p2 + p3 +
  plot_layout(ncol=3, guides = "collect")
p_LL

```

```{r saveEPXlikeC1, include = F}
ggsave(
  filename="TK_EPX_likedevratio.png", 
  plot=p_LL, 
  width=8, height = 4, 
  path=path_fig_C1
  )
ggsave(
  filename="TK_EPX_likedevratio.svg", 
  plot=p_LL, 
  width=8, height = 4, 
  path=path_fig_C1
  )
```

## C1P

```{r EPXlikeC1P, message=F, warning=F}
#| fig-cap: Evolution of likelihood and deviance ratio through the iterations.
#| label: fig-EPXlikeC1P
#| fig-height: 4
#| fig-width: 8

p1 <- ggplot(
  MCMC_out_EPX_C1P$df_LnPost_start, 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = c("1", "2", "3"), values = Nord_frost) +
  labs(
    x = "First half iterations", 
    y = "LnPosterior"
    ) +
  theme_minimal()

p2 <- ggplot(
  MCMC_out_EPX_C1P$df_LnPost |> filter(iteration > 1), 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = c("1", "2", "3"), values = Nord_frost) +
  labs(
    x = paste(MCMC_out_EPX_C1P$Nb_iter_kept, "last iterations"), 
    y = "LnPosterior"
    ) +
  theme_minimal()

p3 <- ggplot(
  MCMC_out_EPX_C1P$df_Devc |> filter(iteration > 1), 
  aes(
    x = iteration, 
    y = RatioDeviance, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = c("1", "2", "3"), values = Nord_frost) +
  labs(
    x = paste(MCMC_out_EPX_C1P$Nb_iter_kept, "last iterations"), 
    y = "Ratio Deviance"
    ) +
  theme_minimal()

p_LL <- p1 + p2 + p3 +
  plot_layout(ncol=3, guides = "collect")
p_LL

```

```{r saveEPXlikeC1P, include = F}
ggsave(
  filename="TK_EPX_likedevratio.png", 
  plot=p_LL, 
  width=8, height = 4, 
  path=path_fig_C1P
  )
ggsave(
  filename="TK_EPX_likedevratio.svg", 
  plot=p_LL, 
  width=8, height = 4, 
  path=path_fig_C1P
  )
```

## C2

```{r EPXlikeC2, message=F, warning=F}
#| fig-cap: Evolution of likelihood and deviance ratio through the iterations.
#| label: fig-EPXlikeC2
#| fig-height: 4
#| fig-width: 8

p1 <- ggplot(
  MCMC_out_EPX_C2$df_LnPost_start, 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = c("1", "2", "3"), values = Nord_frost) +
  labs(
    x = "First half iterations", 
    y = "LnPosterior"
    ) +
  theme_minimal()

p2 <- ggplot(
  MCMC_out_EPX_C2$df_LnPost |> filter(iteration > 1), 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = c("1", "2", "3"), values = Nord_frost) +
  labs(
    x = paste(MCMC_out_EPX_C2$Nb_iter_kept, "last iterations"), 
    y = "LnPosterior"
    ) +
  theme_minimal()

p3 <- ggplot(
  MCMC_out_EPX_C2$df_Devc |> filter(iteration > 1), 
  aes(
    x = iteration, 
    y = RatioDeviance, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = c("1", "2", "3"), values = Nord_frost) +
  labs(
    x = paste(MCMC_out_EPX_C2$Nb_iter_kept, "last iterations"), 
    y = "Ratio Deviance"
    ) +
  theme_minimal()

p_LL <- p1 + p2 + p3 +
  plot_layout(ncol=3, guides = "collect")
p_LL

```

```{r saveEPXlikeC2, include = F}
ggsave(
  filename="TK_EPX_likedevratio.png", 
  plot=p_LL, 
  width=8, height = 4, 
  path=path_fig_C2
  )
ggsave(
  filename="TK_EPX_likedevratio.svg", 
  plot=p_LL, 
  width=8, height = 4, 
  path=path_fig_C2
  )
```

## C2P

```{r EPXlikeC2P, message=F, warning=F}
#| fig-cap: Evolution of likelihood and deviance ratio through the iterations.
#| label: fig-EPXlikeC2P
#| fig-height: 4
#| fig-width: 8

p1 <- ggplot(
  MCMC_out_EPX_C2P$df_LnPost_start, 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = c("1", "2", "3"), values = Nord_frost) +
  labs(
    x = "First half iterations", 
    y = "LnPosterior"
    ) +
  theme_minimal()

p2 <- ggplot(
  MCMC_out_EPX_C2P$df_LnPost |> filter(iteration > 1), 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = c("1", "2", "3"), values = Nord_frost) +
  labs(
    x = paste(MCMC_out_EPX_C2P$Nb_iter_kept, "last iterations"), 
    y = "LnPosterior"
    ) +
  theme_minimal()

p3 <- ggplot(
  MCMC_out_EPX_C2P$df_Devc |> filter(iteration > 1), 
  aes(
    x = iteration, 
    y = RatioDeviance, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = c("1", "2", "3"), values = Nord_frost) +
  labs(
    x = paste(MCMC_out_EPX_C2P$Nb_iter_kept, "last iterations"), 
    y = "Ratio Deviance"
    ) +
  theme_minimal()

p_LL <- p1 + p2 + p3 +
  plot_layout(ncol=3, guides = "collect")
p_LL

```

```{r saveEPXlikeC2P, include = F}
ggsave(
  filename="TK_EPX_likedevratio.png", 
  plot=p_LL, 
  width=8, height = 4, 
  path=path_fig_C2P
  )
ggsave(
  filename="TK_EPX_likedevratio.svg", 
  plot=p_LL, 
  width=8, height = 4, 
  path=path_fig_C2P
  )
```
:::

```{r mcmclist, message=F, warning=F}
# Large format per chain
mcmc_list_C1 <- lapply(split(MCMC_out_EPX_C1$Chains, MCMC_out_EPX_C1$Chains$Chain), function(d) {
  wide <- d %>%
    dplyr::select(Iteration, Parameter, value) %>%
    pivot_wider(names_from = Parameter, values_from = value) %>%
    arrange(Iteration)
  
  mcmc(as.matrix(wide[,-1]))
})
mcmc_list_C1 <- as.mcmc.list(mcmc_list_C1)

mcmc_list_C1P <- lapply(split(MCMC_out_EPX_C1P$Chains, MCMC_out_EPX_C1P$Chains$Chain), function(d) {
  wide <- d %>%
    dplyr::select(Iteration, Parameter, value) %>%
    pivot_wider(names_from = Parameter, values_from = value) %>%
    arrange(Iteration)
  
  mcmc(as.matrix(wide[,-1]))
})
mcmc_list_C1P <- as.mcmc.list(mcmc_list_C1P)

mcmc_list_C2 <- lapply(split(MCMC_out_EPX_C2$Chains, MCMC_out_EPX_C2$Chains$Chain), function(d) {
  wide <- d %>%
    dplyr::select(Iteration, Parameter, value) %>%
    pivot_wider(names_from = Parameter, values_from = value) %>%
    arrange(Iteration)
  
  mcmc(as.matrix(wide[,-1]))
})
mcmc_list_C2 <- as.mcmc.list(mcmc_list_C2)

mcmc_list_C2P <- lapply(split(MCMC_out_EPX_C2P$Chains, MCMC_out_EPX_C2P$Chains$Chain), function(d) {
  wide <- d %>%
    dplyr::select(Iteration, Parameter, value) %>%
    pivot_wider(names_from = Parameter, values_from = value) %>%
    arrange(Iteration)
  
  mcmc(as.matrix(wide[,-1]))
})
mcmc_list_C2P <- as.mcmc.list(mcmc_list_C2P)

```

::: panel-tabset
## C1

```{r}
#| fig-cap: Chains convergence.
#| label: fig-EPXchainsconvergenceC1
#| fig-height: 8
#| fig-width: 8

  par(mfrow=c(1,3))

  gelman.plot(mcmc_list_C1,
            bin.width = 10,      # Number of observations per segment,
            # first segment --> at least 50 iterations.
            max.bins = 50,       # Maximum number of bins, excluding the last one
            confidence = 0.95,   # Coverage probability of confidence interval.
            transform = FALSE,   # improve the normality of the distribution
            autoburnin=TRUE)     # Remove first half of sequence

  
  gelman <- gelman.diag(mcmc_list_C1, confidence = 0.95, transform=FALSE, autoburnin=TRUE, multivariate=TRUE)
  print(gelman)
```

## C1P

```{r}
#| fig-cap: Chains convergence.
#| label: fig-EPXchainsconvergenceC1P
#| fig-height: 8
#| fig-width: 8

  par(mfrow=c(1,3))

  gelman.plot(mcmc_list_C1P,
            bin.width = 10,      # Number of observations per segment,
            # first segment --> at least 50 iterations.
            max.bins = 50,       # Maximum number of bins, excluding the last one
            confidence = 0.95,   # Coverage probability of confidence interval.
            transform = FALSE,   # improve the normality of the distribution
            autoburnin=TRUE)     # Remove first half of sequence

  
  gelman <- gelman.diag(mcmc_list_C1P, confidence = 0.95, transform=FALSE, autoburnin=TRUE, multivariate=TRUE)
  print(gelman)
```

## C2

```{r}
#| fig-cap: Chains convergence.
#| label: fig-EPXchainsconvergenceC2
#| fig-height: 8
#| fig-width: 8

  par(mfrow=c(1,3))

  gelman.plot(mcmc_list_C2,
            bin.width = 10,      # Number of observations per segment,
            # first segment --> at least 50 iterations.
            max.bins = 50,       # Maximum number of bins, excluding the last one
            confidence = 0.95,   # Coverage probability of confidence interval.
            transform = FALSE,   # improve the normality of the distribution
            autoburnin=TRUE)     # Remove first half of sequence

  
  gelman <- gelman.diag(mcmc_list_C2, confidence = 0.95, transform=FALSE, autoburnin=TRUE, multivariate=TRUE)
  print(gelman)
```

## C2P

```{r}
#| fig-cap: Chains convergence.
#| label: fig-EPXchainsconvergenceC2P
#| fig-height: 8
#| fig-width: 8

  par(mfrow=c(1,3))

  gelman.plot(mcmc_list_C2P,
            bin.width = 10,      # Number of observations per segment,
            # first segment --> at least 50 iterations.
            max.bins = 50,       # Maximum number of bins, excluding the last one
            confidence = 0.95,   # Coverage probability of confidence interval.
            transform = FALSE,   # improve the normality of the distribution
            autoburnin=TRUE)     # Remove first half of sequence

  
  gelman <- gelman.diag(mcmc_list_C2P, confidence = 0.95, transform=FALSE, autoburnin=TRUE, multivariate=TRUE)
  print(gelman)
```
:::

Chains converged.

::: panel-tabset
## C1

```{r corr, message=F, warning=F}
#| fig-cap: Parameter correlations.
#| label: fig-corrC1
#| fig-height: 5
#| fig-width: 6

mcmc_list_corr <- mcmc.list(
  lapply(mcmc_list_C1, function(x) {
    mcmc(as.matrix(x)[-1, , drop = FALSE])  # <- reconvertir en mcmc
  })
)

colramp_aurora <- colorRampPalette(rev(Nord_aurora[1:4]))
ipairs(as.matrix(mcmc_list_corr), colramp = colramp_aurora, pixs=0.25, cex.diag = 0.5)
```

## C1P

```{r corr, message=F, warning=F}
#| fig-cap: Parameter correlations.
#| label: fig-corrC1P
#| fig-height: 5
#| fig-width: 6

mcmc_list_corr <- mcmc.list(
  lapply(mcmc_list_C1P, function(x) {
    mcmc(as.matrix(x)[-1, , drop = FALSE])  # <- reconvertir en mcmc
  })
)

colramp_aurora <- colorRampPalette(rev(Nord_aurora[1:4]))
ipairs(as.matrix(mcmc_list_corr), colramp = colramp_aurora, pixs=0.25, cex.diag = 0.5)
```

## C2

```{r corr, message=F, warning=F}
#| fig-cap: Parameter correlations.
#| label: fig-corrC2
#| fig-height: 5
#| fig-width: 6

mcmc_list_corr <- mcmc.list(
  lapply(mcmc_list_C2, function(x) {
    mcmc(as.matrix(x)[-1, , drop = FALSE])  # <- reconvertir en mcmc
  })
)

colramp_aurora <- colorRampPalette(rev(Nord_aurora[1:4]))
ipairs(as.matrix(mcmc_list_corr), colramp = colramp_aurora, pixs=0.25, cex.diag = 0.5)
```

## C2P

```{r corr, message=F, warning=F}
#| fig-cap: Parameter correlations.
#| label: fig-corrC2P
#| fig-height: 5
#| fig-width: 6

mcmc_list_corr <- mcmc.list(
  lapply(mcmc_list_C2P, function(x) {
    mcmc(as.matrix(x)[-1, , drop = FALSE])  # <- reconvertir en mcmc
  })
)

colramp_aurora <- colorRampPalette(rev(Nord_aurora[1:4]))
ipairs(as.matrix(mcmc_list_corr), colramp = colramp_aurora, pixs=0.25, cex.diag = 0.5)
```
:::

### Parameter estimation results

::: panel-tabset
## C1

```{r EPXpost, message=F, warning=F}
#| fig-cap: Distributions of the priors and the posteriors.
#| label: fig-EPXpostC1
#| fig-height: 6
#| fig-width: 8

alpha_prior <- 0.5
alpha_post <- 0.5
col_prior <- Nord_snow[1]
col_post <- col_EPX


MCMC_out_EPX_C1$Chains_plot <- MCMC_out_EPX_C1$Chains |> 
  mutate(Nom = str_remove(Parameter, "\\.\\d+\\.$")) |> 
  filter(!((Nom %in% c("kcomp_in","kcomp_out") & value > 0.02)))|> 
  filter(!((Nom %in% c("kuEPX") & value > 5)))

p_post <- ggplot() +
  
  # Priors
  stat_halfeye(
    data = df_priors_dist_C1,
    aes(
       x = samples,
       #y = ..scaled..
       ),
    alpha = alpha_prior,
    fill = col_prior,
    color = col_prior,
    normalize = "xy"
    ) +
  
  # Posterior
  stat_halfeye(
    data = subset(MCMC_out_EPX_C1$Chains_plot, Nom %in% L_parameters_C1),
    mapping = aes(
      x=value
    ),
    fill = col_post,
    color = col_post,
    alpha = alpha_post,
    normalize = "xy"
  ) +
  
  facet_wrap(~Nom, scales = "free")+
  labs(
    title = "Posterior and prior distributions", 
    x = "Parameter value", 
    y = "Density"
    ) +
  theme_minimal()+
  theme(
    title=element_markdown(face="bold")
  )

p_post
```

```{r savepostC1, include = F}
ggsave(
  filename="TK_EPX_post.png", 
  plot=p_post, 
  width=8, height = 6, 
  path=path_fig_C1
  )
ggsave(
  filename="TK_EPX_post.svg", 
  plot=p_post, 
  width=8, height = 6, 
  path=path_fig_C1
  )
```

## C1P

```{r EPXpost, message=F, warning=F}
#| fig-cap: Distributions of the priors and the posteriors.
#| label: fig-EPXpostC1P
#| fig-height: 6
#| fig-width: 8

alpha_prior <- 0.5
alpha_post <- 0.5
col_prior <- Nord_snow[1]
col_post <- col_EPX


MCMC_out_EPX_C1P$Chains_plot <- MCMC_out_EPX_C1P$Chains |> 
  mutate(Nom = str_remove(Parameter, "\\.\\d+\\.$")) |> 
  filter(!((Nom %in% c("kcomp_in","kcomp_out") & value > 0.02)))|> 
  filter(!((Nom %in% c("kuEPX") & value > 5)))

p_post <- ggplot() +
  
  # Priors
  stat_halfeye(
    data = df_priors_dist_C1P,
    aes(
       x = samples,
       #y = ..scaled..
       ),
    alpha = alpha_prior,
    fill = col_prior,
    color = col_prior,
    normalize = "xy"
    ) +
  
  # Posterior
  stat_halfeye(
    data = subset(MCMC_out_EPX_C1P$Chains_plot, Nom %in% L_parameters_C1P),
    mapping = aes(
      x=value
    ),
    fill = col_post,
    color = col_post,
    alpha = alpha_post,
    normalize = "xy"
  ) +
  
  facet_wrap(~Nom, scales = "free")+
  labs(
    title = "Posterior and prior distributions", 
    x = "Parameter value", 
    y = "Density"
    ) +
  theme_minimal()+
  theme(
    title=element_markdown(face="bold")
  )

p_post
```

```{r savepostC1P, include = F}
ggsave(
  filename="TK_EPX_post.png", 
  plot=p_post, 
  width=8, height = 6, 
  path=path_fig_C1P
  )
ggsave(
  filename="TK_EPX_post.svg", 
  plot=p_post, 
  width=8, height = 6, 
  path=path_fig_C1P
  )
```

## C2

```{r EPXpost, message=F, warning=F}
#| fig-cap: Distributions of the priors and the posteriors.
#| label: fig-EPXpostC2
#| fig-height: 6
#| fig-width: 8

alpha_prior <- 0.5
alpha_post <- 0.5
col_prior <- Nord_snow[1]
col_post <- col_EPX


MCMC_out_EPX_C2$Chains_plot <- MCMC_out_EPX_C2$Chains |> 
  mutate(Nom = str_remove(Parameter, "\\.\\d+\\.$")) |> 
  filter(!((Nom %in% c("kcomp_in","kcomp_out") & value > 0.02)))|> 
  filter(!((Nom %in% c("kuEPX") & value > 5)))

p_post <- ggplot() +
  
  # Priors
  stat_halfeye(
    data = df_priors_dist_C2,
    aes(
       x = samples,
       #y = ..scaled..
       ),
    alpha = alpha_prior,
    fill = col_prior,
    color = col_prior,
    normalize = "xy"
    ) +
  
  # Posterior
  stat_halfeye(
    data = subset(MCMC_out_EPX_C2$Chains_plot, Nom %in% L_parameters_C2),
    mapping = aes(
      x=value
    ),
    fill = col_post,
    color = col_post,
    alpha = alpha_post,
    normalize = "xy"
  ) +
  
  facet_wrap(~Nom, scales = "free")+
  labs(
    title = "Posterior and prior distributions", 
    x = "Parameter value", 
    y = "Density"
    ) +
  theme_minimal()+
  theme(
    title=element_markdown(face="bold")
  )

p_post
```

```{r savepostC2, include = F}
ggsave(
  filename="TK_EPX_post.png", 
  plot=p_post, 
  width=8, height = 6, 
  path=path_fig_C2
  )
ggsave(
  filename="TK_EPX_post.svg", 
  plot=p_post, 
  width=8, height = 6, 
  path=path_fig_C2
  )
```

## C2P

```{r EPXpost, message=F, warning=F}
#| fig-cap: Distributions of the priors and the posteriors.
#| label: fig-EPXpostC2P
#| fig-height: 6
#| fig-width: 8

alpha_prior <- 0.5
alpha_post <- 0.5
col_prior <- Nord_snow[1]
col_post <- col_EPX


MCMC_out_EPX_C2P$Chains_plot <- MCMC_out_EPX_C2P$Chains |> 
  mutate(Nom = str_remove(Parameter, "\\.\\d+\\.$")) |> 
  filter(!((Nom %in% c("kcomp_in","kcomp_out") & value > 0.02)))|> 
  filter(!((Nom %in% c("kuEPX") & value > 5)))

p_post <- ggplot() +
  
  # Priors
  stat_halfeye(
    data = df_priors_dist_C2P,
    aes(
       x = samples,
       #y = ..scaled..
       ),
    alpha = alpha_prior,
    fill = col_prior,
    color = col_prior,
    normalize = "xy"
    ) +
  
  # Posterior
  stat_halfeye(
    data = subset(MCMC_out_EPX_C2P$Chains_plot, Nom %in% L_parameters_C2P),
    mapping = aes(
      x=value
    ),
    fill = col_post,
    color = col_post,
    alpha = alpha_post,
    normalize = "xy"
  ) +
  
  facet_wrap(~Nom, scales = "free")+
  labs(
    title = "Posterior and prior distributions", 
    x = "Parameter value", 
    y = "Density"
    ) +
  theme_minimal()+
  theme(
    title=element_markdown(face="bold")
  )

p_post
```

```{r savepostC2P, include = F}
ggsave(
  filename="TK_EPX_post.png", 
  plot=p_post, 
  width=8, height = 6, 
  path=path_fig_C2P
  )
ggsave(
  filename="TK_EPX_post.svg", 
  plot=p_post, 
  width=8, height = 6, 
  path=path_fig_C2P
  )
```
:::

```{r calcBCFEPX, message=F, warning=F}

f_get_mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}

########## C1 #######################################################

MCMC_out_EPX_C1$Chains <- MCMC_out_EPX_C1$Chains |> 
  mutate(Nom = str_remove(Parameter, "\\.\\d+\\.$"))

ku_samples_C1 <- MCMC_out_EPX_C1$Chains |> filter(Nom == "kuEPX")
ke_samples_C1 <- MCMC_out_EPX_C1$Chains |> filter(Nom == "keEPX")

BCF_samples_C1 <- ku_samples_C1$value / ke_samples_C1$value

BCF_mode_C1 <- f_get_mode(BCF_samples_C1)
BCF_CI_C1 <- quantile(BCF_samples_C1, probs = c(0.025, 0.975))
BCF_CI_low_C1 <- as.numeric(BCF_CI_C1[1])
BCF_CI_up_C1 <- as.numeric(BCF_CI_C1[2])
BCF_min_C1 <- min(BCF_samples_C1)
BCF_max_C1 <- max(BCF_samples_C1)
BCF_mean_C1 <- mean(BCF_samples_C1)
BCF_sd_C1 <- sd(BCF_samples_C1)

BCF_C1 <- c(
  BCF_mode_C1, 
  BCF_CI_low_C1, BCF_CI_up_C1, 
  BCF_min_C1, BCF_max_C1, 
  BCF_mean_C1, BCF_sd_C1
  )

########## C1P #######################################################

MCMC_out_EPX_C1P$Chains <- MCMC_out_EPX_C1P$Chains |> 
  mutate(Nom = str_remove(Parameter, "\\.\\d+\\.$"))

ku_samples_C1P <- MCMC_out_EPX_C1P$Chains |> filter(Nom == "kuEPX")
ke_samples_C1P <- MCMC_out_EPX_C1P$Chains |> filter(Nom == "keEPX")

BCF_samples_C1P <- ku_samples_C1P$value / ke_samples_C1P$value

BCF_mode_C1P <- f_get_mode(BCF_samples_C1P)
BCF_CI_C1P <- quantile(BCF_samples_C1P, probs = c(0.025, 0.975))
BCF_CI_low_C1P <- as.numeric(BCF_CI_C1P[1])
BCF_CI_up_C1P <- as.numeric(BCF_CI_C1P[2])
BCF_min_C1P <- min(BCF_samples_C1P)
BCF_max_C1P <- max(BCF_samples_C1P)
BCF_mean_C1P <- mean(BCF_samples_C1P)
BCF_sd_C1P <- sd(BCF_samples_C1P)

BCF_C1P <- c(
  BCF_mode_C1P, 
  BCF_CI_low_C1P, BCF_CI_up_C1P, 
  BCF_min_C1P, BCF_max_C1P, 
  BCF_mean_C1P, BCF_sd_C1P
  )

########## C2 #######################################################

MCMC_out_EPX_C2$Chains <- MCMC_out_EPX_C2$Chains |> 
  mutate(Nom = str_remove(Parameter, "\\.\\d+\\.$"))

ku_samples_C2 <- MCMC_out_EPX_C2$Chains |> filter(Nom == "kuEPX")
ke_samples_C2 <- MCMC_out_EPX_C2$Chains |> filter(Nom == "keEPX")

BCF_samples_C2 <- ku_samples_C2$value / ke_samples_C2$value

BCF_mode_C2 <- f_get_mode(BCF_samples_C2)
BCF_CI_C2 <- quantile(BCF_samples_C2, probs = c(0.025, 0.975))
BCF_CI_low_C2 <- as.numeric(BCF_CI_C2[1])
BCF_CI_up_C2 <- as.numeric(BCF_CI_C2[2])
BCF_min_C2 <- min(BCF_samples_C2)
BCF_max_C2 <- max(BCF_samples_C2)
BCF_mean_C2 <- mean(BCF_samples_C2)
BCF_sd_C2 <- sd(BCF_samples_C2)

BCF_C2 <- c(
  BCF_mode_C2, 
  BCF_CI_low_C2, BCF_CI_up_C2, 
  BCF_min_C2, BCF_max_C2, 
  BCF_mean_C2, BCF_sd_C2
  )

########## C2P #######################################################

MCMC_out_EPX_C2P$Chains <- MCMC_out_EPX_C2P$Chains |> 
  mutate(Nom = str_remove(Parameter, "\\.\\d+\\.$"))

ku_samples_C2P <- MCMC_out_EPX_C2P$Chains |> filter(Nom == "kuEPX")
ke_samples_C2P <- MCMC_out_EPX_C2P$Chains |> filter(Nom == "keEPX")

BCF_samples_C2P <- ku_samples_C2P$value / ke_samples_C2P$value

BCF_mode_C2P <- f_get_mode(BCF_samples_C2P)
BCF_CI_C2P <- quantile(BCF_samples_C2P, probs = c(0.025, 0.975))
BCF_CI_low_C2P <- as.numeric(BCF_CI_C2P[1])
BCF_CI_up_C2P <- as.numeric(BCF_CI_C2P[2])
BCF_min_C2P <- min(BCF_samples_C2P)
BCF_max_C2P <- max(BCF_samples_C2P)
BCF_mean_C2P <- mean(BCF_samples_C2P)
BCF_sd_C2P <- sd(BCF_samples_C2P)

BCF_C2P <- c(
  BCF_mode_C2P, 
  BCF_CI_low_C2P, BCF_CI_up_C2P, 
  BCF_min_C2P, BCF_max_C2P, 
  BCF_mean_C2P, BCF_sd_C2P
  )

```

::: panel-tabset
## C1

```{r EPXSummaryResC1, message=F, warning=F}
#| tbl-cap: Results summary
#| tbl-label: tbl-EPXressumC1

Summary_res_EPX_tmp_C1 <- cbind(as.data.frame(MCMC_out_EPX_C1$Summary_res)[1:length(L_parameters_C1)], BCF_C1)

Summary_res_EPX_f_C1 <- Summary_res_EPX_tmp_C1 |> 
  mutate(across(where(is.numeric), signif, 2))

Summary_res_EPX_f_C1 |> datatable(
  options = list(
    dom = 't',
    autoWidth = TRUE,
    columnDefs = list(
      list(className = 'dt-left', targets = "_all")
      )
    ),
  class="hover"
  )

#Summary_res_EPX_f_C1
```

```{r bicC1}
# BIC calculation

LL <- f_get_mode(MCMC_out_EPX_C1$df_LnData$LnData)
n <- length(na.omit(df_TK_EPX$Weight)) + length(na.omit(df_TK_EPX$CiEPX))
k <- Nb_param_C1 -2

BIC <- -2*LL + k*log(n)

cat("Number of observations, n = ", n,"\nNumber of parameters, k = ", k, "\nLog-likelihood, LL = ", LL, "\nBIC = ", BIC)

```

## C1P

```{r EPXSummaryResC1P, message=F, warning=F}
#| tbl-cap: Results summary
#| tbl-label: tbl-EPXressumC1P

Summary_res_EPX_tmp_C1P <- cbind(as.data.frame(MCMC_out_EPX_C1P$Summary_res)[1:length(L_parameters_C1P)], BCF_C1P)

Summary_res_EPX_f_C1P <- Summary_res_EPX_tmp_C1P |> 
  mutate(across(where(is.numeric), signif, 2))

Summary_res_EPX_f_C1P |> datatable(
  options = list(
    dom = 't',
    autoWidth = TRUE,
    columnDefs = list(
      list(className = 'dt-left', targets = "_all")
      )
    ),
  class="hover"
  )

#Summary_res_EPX_f_C1P
```

```{r bicC1P}
# BIC calculation

LL <- f_get_mode(MCMC_out_EPX_C1P$df_LnData$LnData)
n <- length(na.omit(df_TK_EPX$Weight)) + length(na.omit(df_TK_EPX$CiEPX))
k <- Nb_param_C1P -2

BIC <- -2*LL + k*log(n)

cat("Number of observations, n = ", n,"\nNumber of parameters, k = ", k, "\nLog-likelihood, LL = ", LL, "\nBIC = ", BIC)

```

## C2

```{r EPXSummaryResC2, message=F, warning=F}
#| tbl-cap: Results summary
#| tbl-label: tbl-EPXressumC2

Summary_res_EPX_tmp_C2 <- cbind(as.data.frame(MCMC_out_EPX_C2$Summary_res)[1:length(L_parameters_C2)], BCF_C2)

Summary_res_EPX_f_C2 <- Summary_res_EPX_tmp_C2 |> 
  mutate(across(where(is.numeric), signif, 2))

Summary_res_EPX_f_C2 |> datatable(
  options = list(
    dom = 't',
    autoWidth = TRUE,
    columnDefs = list(
      list(className = 'dt-left', targets = "_all")
      )
    ),
  class="hover"
  )

#Summary_res_EPX_f_C2
```

```{r bicC2}
# BIC calculation

LL <- f_get_mode(MCMC_out_EPX_C2$df_LnData$LnData)
n <- length(na.omit(df_TK_EPX$Weight)) + length(na.omit(df_TK_EPX$CiEPX))
k <- Nb_param_C2 -2

BIC <- -2*LL + k*log(n)

cat("Number of observations, n = ", n,"\nNumber of parameters, k = ", k, "\nLog-likelihood, LL = ", LL, "\nBIC = ", BIC)

```

## C2P

```{r EPXSummaryResC2P, message=F, warning=F}
#| tbl-cap: Results summary
#| tbl-label: tbl-EPXressumC2P

Summary_res_EPX_tmp_C2P <- cbind(as.data.frame(MCMC_out_EPX_C2P$Summary_res)[1:length(L_parameters_C2P)], BCF_C2P)

Summary_res_EPX_f_C2P <- Summary_res_EPX_tmp_C2P |> 
  mutate(across(where(is.numeric), signif, 2))

Summary_res_EPX_f_C2P |> datatable(
  options = list(
    dom = 't',
    autoWidth = TRUE,
    columnDefs = list(
      list(className = 'dt-left', targets = "_all")
      )
    ),
  class="hover"
  )

#Summary_res_EPX_f_C2P
```

```{r bicC2P}
# BIC calculation

LL <- f_get_mode(MCMC_out_EPX_C2P$df_LnData$LnData)
n <- length(na.omit(df_TK_EPX$Weight)) + length(na.omit(df_TK_EPX$CiEPX))
k <- Nb_param_C2P -2

BIC <- -2*LL + k*log(n)

cat("Number of observations, n = ", n,"\nNumber of parameters, k = ", k, "\nLog-likelihood, LL = ", LL, "\nBIC = ", BIC)

```
:::

### Comparison of observed vs. predicted data

```{r setpointindin, message=F, warning=F, eval=T}

######### C1 #################################################
l_param_name_C1 <- "kuEPX, keEPX, a_growth"
f_Setpoint_ind(path_mod_EPX_C1, Molecule, l_param_name_C1)

######### C1P #################################################
l_param_name_C1P <- "kuEPX, keEPX, phi, a_growth"
f_Setpoint_ind(path_mod_EPX_C1P, Molecule, l_param_name_C1P)

######### C2 #################################################
l_param_name_C2 <- "kuEPX, keEPX, kperiph, a_growth"
f_Setpoint_ind(path_mod_EPX_C2, Molecule, l_param_name_C2)

######### C2P #################################################
l_param_name_C2P <- "kuEPX, keEPX, kperiph, phi, a_growth"
f_Setpoint_ind(path_mod_EPX_C2P, Molecule, l_param_name_C2P)

```

An example of how to run the simulations for the predicted-observed data is given in the bash code block below. You need to be in the right folder to launch a given model.

```{bash, eval=F, execute=F}
pwd
cd ..
cd ..
cd mod/TK_EPX
pwd

for j in $(seq 1 71); do
./mcsim.m_TK_EPX TK_EPX_Setpoint_ind_${j}.in
done
```

```{r EPXdatapred, message=F, warning=F}

Nb_experiment <- Nb_experiment_C1

######### Observed data ######################################################
dObs_ind <- df_TK_EPX |> 
  mutate(
    ID = as.numeric(ID),
    Group_tmp = case_when(
      ID < 65 ~ "Uptake",
      (ID > 64 & ID <= 128) ~ "Elimination",
      ID > 128 ~ "Uptake bis"),
    Group = fct_relevel(Group_tmp, c("Uptake", "Elimination", "Uptake bis"))
    )

colnames(dObs_ind)[colnames(dObs_ind) == "Weight"] <- "Weight_obs"
colnames(dObs_ind)[colnames(dObs_ind) == "CiEPX"] <- "CiEPX_obs"
colnames(dObs_ind)[colnames(dObs_ind) == "t"] <- "Times"


############ C1 ##############################################################

Sim.Res.ind_C1 <- lapply(1:Nb_experiment, function(j) {
  read_tsv(file.path(path_mod_EPX_C1, paste0("Setpoints_ind_", j, ".out"))) %>%
    mutate(sim = j)
}) %>%
  bind_rows()

df_mod_ind_C1 <- NULL

for (i in 1:Nb_experiment_C1){
  
  ID_i <- unique(dObs_ind$ID)[i]

  Sim.Res.ind_i  <- subset(Sim.Res.ind_C1, sim == i) |> 
    dplyr::select(where(~ !all(is.na(.x))))
  
  dObs_i <- subset(dObs_ind, ID == ID_i)
  
  Time_pred = dObs_i$Time # !!!
  
  Nom_Endpoints = c("Weight", "CiEPX")
  
  Nsortie = 2
  
  MPV = IC_min = IC_max = Endpoint = index = NULL
  
  for (j in 1:length(Nom_Endpoints)){
    
    index =grep(paste0("^",Nom_Endpoints[j],"_") , colnames(Sim.Res.ind_i), fixed=FALSE)

    
    Data_sim = as.matrix( Sim.Res.ind_i[ , index] )
    
    MPV    = c(  MPV,  as.numeric( Data_sim[nrow(Data_sim), ] ) )
    IC_min = c(IC_min,  apply(Data_sim, 2, quantile,  0.025, na.rm=TRUE) )
    IC_max = c(IC_max,  apply(Data_sim, 2, quantile,  0.975, na.rm=TRUE) ) 
    
    Endpoint = c(Endpoint, rep(Nom_Endpoints[j], ncol(Data_sim)))
  }
  
  df_mod_ind_i <- data.frame(
    predict.endpoint = MPV,
    Time    = rep(Time_pred, Nsortie),
    low     = IC_min,
    up      = IC_max,
    Endpt   = Endpoint
    )
  
  df_mod_ind_i <- df_mod_ind_i %>%
    mutate(ID=ID_i)

  df_mod_ind_C1 <- rbind(df_mod_ind_C1, df_mod_ind_i)
}

df_mod_Weight_ind_C1 <- subset(df_mod_ind_C1, Endpt == "Weight" & Time !=0)
df_mod_CiEPX_ind_C1 <- subset(df_mod_ind_C1, Endpt == "CiEPX" & Time !=0)

df_predobs_CiEPX_ind_C1 <- dObs_ind |> 
  filter(Time !=0) |> 
  left_join(df_mod_CiEPX_ind_C1, suffix = c("_obs", "_pred")) |> 
  dplyr::select(-c(Weight_obs, CiIMD)) |> 
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

df_predobs_Weight_ind_C1 <- dObs_ind |> 
  filter(Time !=0) |> 
  left_join(df_mod_Weight_ind_C1, suffix = c("_obs", "_pred"))|>
  dplyr::select(-c(CiEPX_obs, CiIMD)) |> 
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

############ C1P ##############################################################

Sim.Res.ind_C1P <- lapply(1:Nb_experiment, function(j) {
  read_tsv(file.path(path_mod_EPX_C1P, paste0("Setpoints_ind_", j, ".out"))) %>%
    mutate(sim = j)
}) %>%
  bind_rows()

df_mod_ind_C1P <- NULL

for (i in 1:Nb_experiment_C1P){
  
  ID_i <- unique(dObs_ind$ID)[i]

  Sim.Res.ind_i  <- subset(Sim.Res.ind_C1P, sim == i) |> 
    dplyr::select(where(~ !all(is.na(.x))))
  
  dObs_i <- subset(dObs_ind, ID == ID_i)
  
  Time_pred = dObs_i$Time # !!!
  
  Nom_Endpoints = c("Weight", "CiEPX")
  
  Nsortie = 2
  
  MPV = IC_min = IC_max = Endpoint = index = NULL
  
  for (j in 1:length(Nom_Endpoints)){
    
    index =grep(paste0("^",Nom_Endpoints[j],"_") , colnames(Sim.Res.ind_i), fixed=FALSE)

    
    Data_sim = as.matrix( Sim.Res.ind_i[ , index] )
    
    MPV    = c(  MPV,  as.numeric( Data_sim[nrow(Data_sim), ] ) )
    IC_min = c(IC_min,  apply(Data_sim, 2, quantile,  0.025, na.rm=TRUE) )
    IC_max = c(IC_max,  apply(Data_sim, 2, quantile,  0.975, na.rm=TRUE) ) 
    
    Endpoint = c(Endpoint, rep(Nom_Endpoints[j], ncol(Data_sim)))
  }
  
  df_mod_ind_i <- data.frame(
    predict.endpoint = MPV,
    Time    = rep(Time_pred, Nsortie),
    low     = IC_min,
    up      = IC_max,
    Endpt   = Endpoint
    )
  
  df_mod_ind_i <- df_mod_ind_i %>%
    mutate(ID=ID_i)

  df_mod_ind_C1P <- rbind(df_mod_ind_C1P, df_mod_ind_i)
}

df_mod_Weight_ind_C1P <- subset(df_mod_ind_C1P, Endpt == "Weight" & Time !=0)
df_mod_CiEPX_ind_C1P <- subset(df_mod_ind_C1P, Endpt == "CiEPX" & Time !=0)

df_predobs_CiEPX_ind_C1P <- dObs_ind |> 
  filter(Time !=0) |> 
  left_join(df_mod_CiEPX_ind_C1P, suffix = c("_obs", "_pred")) |> 
  dplyr::select(-c(Weight_obs, CiIMD)) |> 
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

df_predobs_Weight_ind_C1P <- dObs_ind |> 
  filter(Time !=0) |> 
  left_join(df_mod_Weight_ind_C1P, suffix = c("_obs", "_pred"))|>
  dplyr::select(-c(CiEPX_obs, CiIMD)) |> 
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

############ C2 ##############################################################

Sim.Res.ind_C2 <- lapply(1:Nb_experiment, function(j) {
  read_tsv(file.path(path_mod_EPX_C2, paste0("Setpoints_ind_", j, ".out"))) %>%
    mutate(sim = j)
}) %>%
  bind_rows()

df_mod_ind_C2 <- NULL

for (i in 1:Nb_experiment_C2){
  
  ID_i <- unique(dObs_ind$ID)[i]

  Sim.Res.ind_i  <- subset(Sim.Res.ind_C2, sim == i) |> 
    dplyr::select(where(~ !all(is.na(.x))))
  
  dObs_i <- subset(dObs_ind, ID == ID_i)
  
  Time_pred = dObs_i$Time # !!!
  
  Nom_Endpoints = c("Weight", "CiEPX")
  
  Nsortie = 2
  
  MPV = IC_min = IC_max = Endpoint = index = NULL
  
  for (j in 1:length(Nom_Endpoints)){
    
    index =grep(paste0("^",Nom_Endpoints[j],"_") , colnames(Sim.Res.ind_i), fixed=FALSE)

    
    Data_sim = as.matrix( Sim.Res.ind_i[ , index] )
    
    MPV    = c(  MPV,  as.numeric( Data_sim[nrow(Data_sim), ] ) )
    IC_min = c(IC_min,  apply(Data_sim, 2, quantile,  0.025, na.rm=TRUE) )
    IC_max = c(IC_max,  apply(Data_sim, 2, quantile,  0.975, na.rm=TRUE) ) 
    
    Endpoint = c(Endpoint, rep(Nom_Endpoints[j], ncol(Data_sim)))
  }
  
  df_mod_ind_i <- data.frame(
    predict.endpoint = MPV,
    Time    = rep(Time_pred, Nsortie),
    low     = IC_min,
    up      = IC_max,
    Endpt   = Endpoint
    )
  
  df_mod_ind_i <- df_mod_ind_i %>%
    mutate(ID=ID_i)

  df_mod_ind_C2 <- rbind(df_mod_ind_C2, df_mod_ind_i)
}

df_mod_Weight_ind_C2 <- subset(df_mod_ind_C2, Endpt == "Weight" & Time !=0)
df_mod_CiEPX_ind_C2 <- subset(df_mod_ind_C2, Endpt == "CiEPX" & Time !=0)

df_predobs_CiEPX_ind_C2 <- dObs_ind |> 
  filter(Time !=0) |> 
  left_join(df_mod_CiEPX_ind_C2, suffix = c("_obs", "_pred")) |> 
  dplyr::select(-c(Weight_obs, CiIMD)) |> 
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

df_predobs_Weight_ind_C2 <- dObs_ind |> 
  filter(Time !=0) |> 
  left_join(df_mod_Weight_ind_C2, suffix = c("_obs", "_pred"))|>
  dplyr::select(-c(CiEPX_obs, CiIMD)) |> 
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

############ C2P ##############################################################

Sim.Res.ind_C2P <- lapply(1:Nb_experiment, function(j) {
  read_tsv(file.path(path_mod_EPX_C2P, paste0("Setpoints_ind_", j, ".out"))) %>%
    mutate(sim = j)
}) %>%
  bind_rows()

df_mod_ind_C2P <- NULL

for (i in 1:Nb_experiment_C2P){
  
  ID_i <- unique(dObs_ind$ID)[i]

  Sim.Res.ind_i  <- subset(Sim.Res.ind_C2P, sim == i) |> 
    dplyr::select(where(~ !all(is.na(.x))))
  
  dObs_i <- subset(dObs_ind, ID == ID_i)
  
  Time_pred = dObs_i$Time # !!!
  
  Nom_Endpoints = c("Weight", "CiEPX")
  
  Nsortie = 2
  
  MPV = IC_min = IC_max = Endpoint = index = NULL
  
  for (j in 1:length(Nom_Endpoints)){
    
    index =grep(paste0("^",Nom_Endpoints[j],"_") , colnames(Sim.Res.ind_i), fixed=FALSE)

    
    Data_sim = as.matrix( Sim.Res.ind_i[ , index] )
    
    MPV    = c(  MPV,  as.numeric( Data_sim[nrow(Data_sim), ] ) )
    IC_min = c(IC_min,  apply(Data_sim, 2, quantile,  0.025, na.rm=TRUE) )
    IC_max = c(IC_max,  apply(Data_sim, 2, quantile,  0.975, na.rm=TRUE) ) 
    
    Endpoint = c(Endpoint, rep(Nom_Endpoints[j], ncol(Data_sim)))
  }
  
  df_mod_ind_i <- data.frame(
    predict.endpoint = MPV,
    Time    = rep(Time_pred, Nsortie),
    low     = IC_min,
    up      = IC_max,
    Endpt   = Endpoint
    )
  
  df_mod_ind_i <- df_mod_ind_i %>%
    mutate(ID=ID_i)

  df_mod_ind_C2P <- rbind(df_mod_ind_C2P, df_mod_ind_i)
}

df_mod_Weight_ind_C2P <- subset(df_mod_ind_C2P, Endpt == "Weight" & Time !=0)
df_mod_CiEPX_ind_C2P <- subset(df_mod_ind_C2P, Endpt == "CiEPX" & Time !=0)

df_predobs_CiEPX_ind_C2P <- dObs_ind |> 
  filter(Time !=0) |> 
  left_join(df_mod_CiEPX_ind_C2P, suffix = c("_obs", "_pred")) |> 
  dplyr::select(-c(Weight_obs, CiIMD)) |> 
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

df_predobs_Weight_ind_C2P <- dObs_ind |> 
  filter(Time !=0) |> 
  left_join(df_mod_Weight_ind_C2P, suffix = c("_obs", "_pred"))|>
  dplyr::select(-c(CiEPX_obs, CiIMD)) |> 
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

```

```{r rmse, message=F, warning=F}
RMSE_C1 <- sqrt(mean((c(df_predobs_CiEPX_ind_C1$CiEPX_obs, df_predobs_Weight_ind_C1$Weight_obs) - c(df_predobs_CiEPX_ind_C1$predict.endpoint, df_predobs_Weight_ind_C1$predict.endpoint))^2, na.rm = TRUE))
cat("RMSE(C1) = ", RMSE_C1)

RMSE_C1P <- sqrt(mean((c(df_predobs_CiEPX_ind_C1P$CiEPX_obs, df_predobs_Weight_ind_C1P$Weight_obs) - c(df_predobs_CiEPX_ind_C1P$predict.endpoint, df_predobs_Weight_ind_C1P$predict.endpoint))^2, na.rm = TRUE))
cat("RMSE(C1P) = ", RMSE_C1P)

RMSE_C2 <- sqrt(mean((c(df_predobs_CiEPX_ind_C2$CiEPX_obs, df_predobs_Weight_ind_C2$Weight_obs) - c(df_predobs_CiEPX_ind_C2$predict.endpoint, df_predobs_Weight_ind_C2$predict.endpoint))^2, na.rm = TRUE))
cat("RMSE(C2) = ", RMSE_C2)

RMSE_C2P <- sqrt(mean((c(df_predobs_CiEPX_ind_C2P$CiEPX_obs, df_predobs_Weight_ind_C2P$Weight_obs) - c(df_predobs_CiEPX_ind_C2P$predict.endpoint, df_predobs_Weight_ind_C2P$predict.endpoint))^2, na.rm = TRUE))
cat("RMSE(C2P) = ", RMSE_C2P)
```

::: panel-tabset
## C1

```{r predobsEPXC1, message=F, warning=F}
#| fig-cap: Results of the model fit on experimental data. Predicted values are represented with points with their respective credibility interval of 95%. Thin black and grey lines represent the 2-folds and 5-fold changes, respectively. The thicker black line represents the identity line. 
#| label: fig-EPXpredobsC1
#| fig-height: 4
#| fig-width: 8

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]

col_exposure_bis <- c(Nord_aurora[1], Nord_aurora[4], Nord_aurora[5])
shape_exposure_bis <- c(shape_IMD, shape_IMD, shape_EPX)
# "#BF616A" "#A3BE8C" "#B48EAD"

lim_min <-  min(df_predobs_Weight_ind_C1$predict.endpoint, df_predobs_Weight_ind_C1$Weight)
lim_max <- max(df_predobs_Weight_ind_C1$predict.endpoint, df_predobs_Weight_ind_C1$Weight)
seq_line <- seq(lim_min, lim_max, 0.001)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_W <- ggplot(
  data = df_predobs_Weight_ind_C1,
  mapping = aes(
      x = Weight_obs,
      y = predict.endpoint
    )
  )+
  geom_line(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up
    ),
    alpha = 0.5,
    color = col_EPX
  )+
  xlim(
    xmin = min(df_predobs_Weight_ind_C1$predict.endpoint)-0.05,
    xmax = max(df_predobs_Weight_ind_C1$predict.endpoint)
  )+
  ylim(
    ymin = min(df_predobs_Weight_ind_C1$predict.endpoint)-0.05,
    ymax = max(df_predobs_Weight_ind_C1$predict.endpoint)
  )+
  scale_x_log10(limits=c(lim_min, lim_max))+
  scale_y_log10(limits=c(lim_min, lim_max))+
  labs(
    x = "Observed weight of earthworms (g)",
    y = "Predicted weight of earthworms (g)"
  )+
  theme_minimal()

fact_1 <- 2
fact_2 <- 5

seq_line <- seq(0.5, 1500, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

lim_plot <- 1000

p_CiEPX_predobs <- ggplot(
  data = df_predobs_CiEPX_ind_C1,
  mapping = aes(
      x = CiEPX_obs,
      y = predict.endpoint
    )
  )+
  geom_path(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
      color = Group,
      shape = Group
    ),
    alpha = 0.5#,
    #color = col_EPX
  )+
  
  xlim(
    xmin = 0.5,
    xmax = max(df_predobs_CiEPX_ind_C1$CiEPX_obs)
  )+
  ylim(
    ymin = 0.5,
    ymax = max(df_predobs_CiEPX_ind_C1$predict.endpoint)
  )+
  labs(
    x = "Observed concentrations of EPX\nin earthworms (ng/g)",
    y = "Predicted concentrations of EPX\nin earthworms (ng/g)"
  )+
  scale_color_manual(
    values = col_exposure_bis
    )+
  scale_shape_manual(values = shape_exposure_bis)+
  scale_x_log10(
    limits=c(1, lim_plot)
    )+
  scale_y_log10(
    limits=c(1, lim_plot)
    )+
  theme_minimal()

p_predobs <- p_W + p_CiEPX_predobs
p_predobs

```

```{r savepredobs_C1, include = F}
ggsave(
  filename = "TK_EPX_predobs.png",
  plot = p_predobs,
  width = 8, height = 4,
  path = path_fig_C1
)
ggsave(
  filename = "TK_EPX_predobs.svg",
  plot = p_predobs,
  width = 8, height = 4,
  path = path_fig_C1
)
```

```{r countfoldEPXC1, warning=F}

df_predobs_Weight_ind_C1 <- df_predobs_Weight_ind_C1 |>
  mutate(
    Ratio_predobs = predict.endpoint / Weight_obs,
    Residuals = predict.endpoint - Weight_obs
  )

Weight_count_fold2 <- length(subset(df_predobs_Weight_ind_C1, Ratio_predobs >= 0.5 & Ratio_predobs <= 2)$Weight_obs) / length(df_predobs_Weight_ind_C1$Weight_obs) * 100

Weight_count_fold5 <- length(subset(df_predobs_Weight_ind_C1, Ratio_predobs >= 0.2 & Ratio_predobs <= 5)$Weight_obs) / length(df_predobs_Weight_ind_C1$Weight_obs) * 100

df_predobs_CiEPX_ind_C1 <- df_predobs_CiEPX_ind_C1 |>
  mutate(
    Ratio_predobs = predict.endpoint / CiEPX_obs,
    Residuals = predict.endpoint - CiEPX_obs
  )

CiEPX_count_fold2 <- length(subset(df_predobs_CiEPX_ind_C1, Ratio_predobs >= 0.5 & Ratio_predobs <= 2)$CiEPX_obs) / length(df_predobs_CiEPX_ind_C1$CiEPX_obs) * 100

CiEPX_count_fold5 <- length(subset(df_predobs_CiEPX_ind_C1, Ratio_predobs >= 0.2 & Ratio_predobs <= 5)$CiEPX_obs) / length(df_predobs_CiEPX_ind_C1$CiEPX_obs) * 100

cat(
  "For weights : \n\n",
  "Percentage of prediction in fold 2 = ", round(Weight_count_fold2, 1), "%\n",
  "Percentage of prediction in fold 5 = ", round(Weight_count_fold5, 1), "%"
)
cat(
  "\n\nFor internal concentrations : \n\n",
  "Percentage of prediction in fold 2 = ", round(CiEPX_count_fold2, 1), "%\n",
  "Percentage of prediction in fold 5 = ", round(CiEPX_count_fold5, 1), "%"
)
```

## C1P

```{r predobsEPXC1P, message=F, warning=F}
#| fig-cap: Results of the model fit on experimental data. Predicted values are represented with points with their respective credibility interval of 95%. Thin black and grey lines represent the 2-folds and 5-fold changes, respectively. The thicker black line represents the identity line. 
#| label: fig-EPXpredobsC1P
#| fig-height: 4
#| fig-width: 8

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]

col_exposure_bis <- c(Nord_aurora[1], Nord_aurora[4], Nord_aurora[5])
shape_exposure_bis <- c(shape_IMD, shape_IMD, shape_EPX)
# "#BF616A" "#A3BE8C" "#B48EAD"

lim_min <-  min(df_predobs_Weight_ind_C1P$predict.endpoint, df_predobs_Weight_ind_C1P$Weight)
lim_max <- max(df_predobs_Weight_ind_C1P$predict.endpoint, df_predobs_Weight_ind_C1P$Weight)
seq_line <- seq(lim_min, lim_max, 0.001)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_W <- ggplot(
  data = df_predobs_Weight_ind_C1P,
  mapping = aes(
      x = Weight_obs,
      y = predict.endpoint
    )
  )+
  geom_line(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up
    ),
    alpha = 0.5,
    color = col_EPX
  )+
  xlim(
    xmin = min(df_predobs_Weight_ind_C1P$predict.endpoint)-0.05,
    xmax = max(df_predobs_Weight_ind_C1P$predict.endpoint)
  )+
  ylim(
    ymin = min(df_predobs_Weight_ind_C1P$predict.endpoint)-0.05,
    ymax = max(df_predobs_Weight_ind_C1P$predict.endpoint)
  )+
  scale_x_log10(limits=c(lim_min, lim_max))+
  scale_y_log10(limits=c(lim_min, lim_max))+
  labs(
    x = "Observed weight of earthworms (g)",
    y = "Predicted weight of earthworms (g)"
  )+
  theme_minimal()

fact_1 <- 2
fact_2 <- 5

seq_line <- seq(0.5, 1500, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

lim_plot <- 1000

p_CiEPX_predobs <- ggplot(
  data = df_predobs_CiEPX_ind_C1P,
  mapping = aes(
      x = CiEPX_obs,
      y = predict.endpoint
    )
  )+
  geom_path(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
      color = Group,
      shape = Group
    ),
    alpha = 0.5#,
    #color = col_EPX
  )+
  
  xlim(
    xmin = 0.5,
    xmax = max(df_predobs_CiEPX_ind_C1P$CiEPX_obs)
  )+
  ylim(
    ymin = 0.5,
    ymax = max(df_predobs_CiEPX_ind_C1P$predict.endpoint)
  )+
  labs(
    x = "Observed concentrations of EPX\nin earthworms (ng/g)",
    y = "Predicted concentrations of EPX\nin earthworms (ng/g)"
  )+
  scale_color_manual(
    values = col_exposure_bis
    )+
  scale_shape_manual(values = shape_exposure_bis)+
  scale_x_log10(
    limits=c(1, lim_plot)
    )+
  scale_y_log10(
    limits=c(1, lim_plot)
    )+
  theme_minimal()

p_predobs <- p_W + p_CiEPX_predobs
p_predobs

```

```{r savepredobs_C1P, include = F}
ggsave(
  filename = "TK_EPX_predobs.png",
  plot = p_predobs,
  width = 8, height = 4,
  path = path_fig_C1P
)
ggsave(
  filename = "TK_EPX_predobs.svg",
  plot = p_predobs,
  width = 8, height = 4,
  path = path_fig_C1P
)
```

```{r countfoldEPXC1P, warning=F}

df_predobs_Weight_ind_C1P <- df_predobs_Weight_ind_C1P |>
  mutate(
    Ratio_predobs = predict.endpoint / Weight_obs,
    Residuals = predict.endpoint - Weight_obs
  )

Weight_count_fold2 <- length(subset(df_predobs_Weight_ind_C1P, Ratio_predobs >= 0.5 & Ratio_predobs <= 2)$Weight_obs) / length(df_predobs_Weight_ind_C1P$Weight_obs) * 100

Weight_count_fold5 <- length(subset(df_predobs_Weight_ind_C1P, Ratio_predobs >= 0.2 & Ratio_predobs <= 5)$Weight_obs) / length(df_predobs_Weight_ind_C1P$Weight_obs) * 100

df_predobs_CiEPX_ind_C1P <- df_predobs_CiEPX_ind_C1P |>
  mutate(
    Ratio_predobs = predict.endpoint / CiEPX_obs,
    Residuals = predict.endpoint - CiEPX_obs
  )

CiEPX_count_fold2 <- length(subset(df_predobs_CiEPX_ind_C1P, Ratio_predobs >= 0.5 & Ratio_predobs <= 2)$CiEPX_obs) / length(df_predobs_CiEPX_ind_C1P$CiEPX_obs) * 100

CiEPX_count_fold5 <- length(subset(df_predobs_CiEPX_ind_C1P, Ratio_predobs >= 0.2 & Ratio_predobs <= 5)$CiEPX_obs) / length(df_predobs_CiEPX_ind_C1P$CiEPX_obs) * 100

cat(
  "For weights : \n\n",
  "Percentage of prediction in fold 2 = ", round(Weight_count_fold2, 1), "%\n",
  "Percentage of prediction in fold 5 = ", round(Weight_count_fold5, 1), "%"
)
cat(
  "\n\nFor internal concentrations : \n\n",
  "Percentage of prediction in fold 2 = ", round(CiEPX_count_fold2, 1), "%\n",
  "Percentage of prediction in fold 5 = ", round(CiEPX_count_fold5, 1), "%"
)
```

## C2

```{r predobsEPXC2, message=F, warning=F}
#| fig-cap: Results of the model fit on experimental data. Predicted values are represented with points with their respective credibility interval of 95%. Thin black and grey lines represent the 2-folds and 5-fold changes, respectively. The thicker black line represents the identity line. 
#| label: fig-EPXpredobsC2
#| fig-height: 4
#| fig-width: 8

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]

col_exposure_bis <- c(Nord_aurora[1], Nord_aurora[4], Nord_aurora[5])
shape_exposure_bis <- c(shape_IMD, shape_IMD, shape_EPX)
# "#BF616A" "#A3BE8C" "#B48EAD"

lim_min <-  min(df_predobs_Weight_ind_C2$predict.endpoint, df_predobs_Weight_ind_C2$Weight)
lim_max <- max(df_predobs_Weight_ind_C2$predict.endpoint, df_predobs_Weight_ind_C2$Weight)
seq_line <- seq(lim_min, lim_max, 0.001)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_W <- ggplot(
  data = df_predobs_Weight_ind_C2,
  mapping = aes(
      x = Weight_obs,
      y = predict.endpoint
    )
  )+
  geom_line(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up
    ),
    alpha = 0.5,
    color = col_EPX
  )+
  xlim(
    xmin = min(df_predobs_Weight_ind_C2$predict.endpoint)-0.05,
    xmax = max(df_predobs_Weight_ind_C2$predict.endpoint)
  )+
  ylim(
    ymin = min(df_predobs_Weight_ind_C2$predict.endpoint)-0.05,
    ymax = max(df_predobs_Weight_ind_C2$predict.endpoint)
  )+
  scale_x_log10(limits=c(lim_min, lim_max))+
  scale_y_log10(limits=c(lim_min, lim_max))+
  labs(
    x = "Observed weight of earthworms (g)",
    y = "Predicted weight of earthworms (g)"
  )+
  theme_minimal()

fact_1 <- 2
fact_2 <- 5

seq_line <- seq(0.5, 1500, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

lim_plot <- 1000

p_CiEPX_predobs <- ggplot(
  data = df_predobs_CiEPX_ind_C2,
  mapping = aes(
      x = CiEPX_obs,
      y = predict.endpoint
    )
  )+
  geom_path(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
      color = Group,
      shape = Group
    ),
    alpha = 0.5#,
    #color = col_EPX
  )+
  
  xlim(
    xmin = 0.5,
    xmax = max(df_predobs_CiEPX_ind_C2$CiEPX_obs)
  )+
  ylim(
    ymin = 0.5,
    ymax = max(df_predobs_CiEPX_ind_C2$predict.endpoint)
  )+
  labs(
    x = "Observed concentrations of EPX\nin earthworms (ng/g)",
    y = "Predicted concentrations of EPX\nin earthworms (ng/g)"
  )+
  scale_color_manual(
    values = col_exposure_bis
    )+
  scale_shape_manual(values = shape_exposure_bis)+
  scale_x_log10(
    limits=c(1, lim_plot)
    )+
  scale_y_log10(
    limits=c(1, lim_plot)
    )+
  theme_minimal()

p_predobs <- p_W + p_CiEPX_predobs
p_predobs

```

```{r savepredobs_C2, include = F}
ggsave(
  filename = "TK_EPX_predobs.png",
  plot = p_predobs,
  width = 8, height = 4,
  path = path_fig_C2
)
ggsave(
  filename = "TK_EPX_predobs.svg",
  plot = p_predobs,
  width = 8, height = 4,
  path = path_fig_C2
)
```

```{r countfoldEPXC2, warning=F}

df_predobs_Weight_ind_C2 <- df_predobs_Weight_ind_C2 |>
  mutate(
    Ratio_predobs = predict.endpoint / Weight_obs,
    Residuals = predict.endpoint - Weight_obs
  )

Weight_count_fold2 <- length(subset(df_predobs_Weight_ind_C2, Ratio_predobs >= 0.5 & Ratio_predobs <= 2)$Weight_obs) / length(df_predobs_Weight_ind_C2$Weight_obs) * 100

Weight_count_fold5 <- length(subset(df_predobs_Weight_ind_C2, Ratio_predobs >= 0.2 & Ratio_predobs <= 5)$Weight_obs) / length(df_predobs_Weight_ind_C2$Weight_obs) * 100

df_predobs_CiEPX_ind_C2 <- df_predobs_CiEPX_ind_C2 |>
  mutate(
    Ratio_predobs = predict.endpoint / CiEPX_obs,
    Residuals = predict.endpoint - CiEPX_obs
  )

CiEPX_count_fold2 <- length(subset(df_predobs_CiEPX_ind_C2, Ratio_predobs >= 0.5 & Ratio_predobs <= 2)$CiEPX_obs) / length(df_predobs_CiEPX_ind_C2$CiEPX_obs) * 100

CiEPX_count_fold5 <- length(subset(df_predobs_CiEPX_ind_C2, Ratio_predobs >= 0.2 & Ratio_predobs <= 5)$CiEPX_obs) / length(df_predobs_CiEPX_ind_C2$CiEPX_obs) * 100

cat(
  "For weights : \n\n",
  "Percentage of prediction in fold 2 = ", round(Weight_count_fold2, 1), "%\n",
  "Percentage of prediction in fold 5 = ", round(Weight_count_fold5, 1), "%"
)
cat(
  "\n\nFor internal concentrations : \n\n",
  "Percentage of prediction in fold 2 = ", round(CiEPX_count_fold2, 1), "%\n",
  "Percentage of prediction in fold 5 = ", round(CiEPX_count_fold5, 1), "%"
)
```

## C2P

```{r predobsEPXC2P, message=F, warning=F}
#| fig-cap: Results of the model fit on experimental data. Predicted values are represented with points with their respective credibility interval of 95%. Thin black and grey lines represent the 2-folds and 5-fold changes, respectively. The thicker black line represents the identity line. 
#| label: fig-EPXpredobsC2P
#| fig-height: 4
#| fig-width: 8

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]

col_exposure_bis <- c(Nord_aurora[1], Nord_aurora[4], Nord_aurora[5])
shape_exposure_bis <- c(shape_IMD, shape_IMD, shape_EPX)
# "#BF616A" "#A3BE8C" "#B48EAD"

lim_min <-  min(df_predobs_Weight_ind_C2P$predict.endpoint, df_predobs_Weight_ind_C2P$Weight)
lim_max <- max(df_predobs_Weight_ind_C2P$predict.endpoint, df_predobs_Weight_ind_C2P$Weight)
seq_line <- seq(lim_min, lim_max, 0.001)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_W <- ggplot(
  data = df_predobs_Weight_ind_C2P,
  mapping = aes(
      x = Weight_obs,
      y = predict.endpoint
    )
  )+
  geom_line(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up
    ),
    alpha = 0.5,
    color = col_EPX
  )+
  xlim(
    xmin = min(df_predobs_Weight_ind_C2P$predict.endpoint)-0.05,
    xmax = max(df_predobs_Weight_ind_C2P$predict.endpoint)
  )+
  ylim(
    ymin = min(df_predobs_Weight_ind_C2P$predict.endpoint)-0.05,
    ymax = max(df_predobs_Weight_ind_C2P$predict.endpoint)
  )+
  scale_x_log10(limits=c(lim_min, lim_max))+
  scale_y_log10(limits=c(lim_min, lim_max))+
  labs(
    x = "Observed weight of earthworms (g)",
    y = "Predicted weight of earthworms (g)"
  )+
  theme_minimal()

fact_1 <- 2
fact_2 <- 5

seq_line <- seq(0.5, 1500, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

lim_plot <- 1000

p_CiEPX_predobs <- ggplot(
  data = df_predobs_CiEPX_ind_C2P,
  mapping = aes(
      x = CiEPX_obs,
      y = predict.endpoint
    )
  )+
  geom_path(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
      color = Group,
      shape = Group
    ),
    alpha = 0.5#,
    #color = col_EPX
  )+
  
  xlim(
    xmin = 0.5,
    xmax = max(df_predobs_CiEPX_ind_C2P$CiEPX_obs)
  )+
  ylim(
    ymin = 0.5,
    ymax = max(df_predobs_CiEPX_ind_C2P$predict.endpoint)
  )+
  labs(
    x = "Observed concentrations of EPX\nin earthworms (ng/g)",
    y = "Predicted concentrations of EPX\nin earthworms (ng/g)"
  )+
  scale_color_manual(
    values = col_exposure_bis
    )+
  scale_shape_manual(values = shape_exposure_bis)+
  scale_x_log10(
    limits=c(1, lim_plot)
    )+
  scale_y_log10(
    limits=c(1, lim_plot)
    )+
  theme_minimal()

p_predobs <- p_W + p_CiEPX_predobs
p_predobs

```

```{r savepredobs_C2P, include = F}
ggsave(
  filename = "TK_EPX_predobs.png",
  plot = p_predobs,
  width = 8, height = 4,
  path = path_fig_C2P
)
ggsave(
  filename = "TK_EPX_predobs.svg",
  plot = p_predobs,
  width = 8, height = 4,
  path = path_fig_C2P
)
```

```{r countfoldEPXC2P, warning=F}

df_predobs_Weight_ind_C2P <- df_predobs_Weight_ind_C2P |>
  mutate(
    Ratio_predobs = predict.endpoint / Weight_obs,
    Residuals = predict.endpoint - Weight_obs
  )

Weight_count_fold2 <- length(subset(df_predobs_Weight_ind_C2P, Ratio_predobs >= 0.5 & Ratio_predobs <= 2)$Weight_obs) / length(df_predobs_Weight_ind_C2P$Weight_obs) * 100

Weight_count_fold5 <- length(subset(df_predobs_Weight_ind_C2P, Ratio_predobs >= 0.2 & Ratio_predobs <= 5)$Weight_obs) / length(df_predobs_Weight_ind_C2P$Weight_obs) * 100

df_predobs_CiEPX_ind_C2P <- df_predobs_CiEPX_ind_C2P |>
  mutate(
    Ratio_predobs = predict.endpoint / CiEPX_obs,
    Residuals = predict.endpoint - CiEPX_obs
  )

CiEPX_count_fold2 <- length(subset(df_predobs_CiEPX_ind_C2P, Ratio_predobs >= 0.5 & Ratio_predobs <= 2)$CiEPX_obs) / length(df_predobs_CiEPX_ind_C2P$CiEPX_obs) * 100

CiEPX_count_fold5 <- length(subset(df_predobs_CiEPX_ind_C2P, Ratio_predobs >= 0.2 & Ratio_predobs <= 5)$CiEPX_obs) / length(df_predobs_CiEPX_ind_C2P$CiEPX_obs) * 100

cat(
  "For weights : \n\n",
  "Percentage of prediction in fold 2 = ", round(Weight_count_fold2, 1), "%\n",
  "Percentage of prediction in fold 5 = ", round(Weight_count_fold5, 1), "%"
)
cat(
  "\n\nFor internal concentrations : \n\n",
  "Percentage of prediction in fold 2 = ", round(CiEPX_count_fold2, 1), "%\n",
  "Percentage of prediction in fold 5 = ", round(CiEPX_count_fold5, 1), "%"
)
```
:::

::: panel-tabset
## C1

```{r, message=F, warning=FALSE}
#| fig-cap: Residuals
#| label: fig-EPXresidualsC1
#| fig-height: 4
#| fig-width: 8

df_residuals_CiEPX_C1 <- df_predobs_CiEPX_ind_C1 |> 
  mutate(
    Residual = predict.endpoint - CiEPX_obs,
    Ratio_Residual = predict.endpoint/CiEPX_obs
    ) |> 
  mutate(
    Time_point = as.numeric(gsub("([0-9]+).*", "\\1" , as.character(Time_point_f))),
    Group = factor(Group, c("Uptake", "Elimination", "TK_BIS")),
    Time_relative = case_when(
      Group == "Uptake" ~ Time_point,
      Group == "TK_BIS" ~ Time_point,
      Group == "Elimination" ~ Time_point - 21
    )
    )

p_residus <- ggplot(df_residuals_CiEPX_C1)+
  geom_point(
    aes(
      x = Time_point,
      y = Ratio_Residual,
      color = Group
    ),
    alpha=0.7
  )+
  labs(
    x = "Time point (days)",
    y = "Predicted/observed ratio"
  )+
  scale_color_manual(
    values = col_exposure_bis
    )+
  scale_x_continuous(
    breaks = unique(df_residuals_CiEPX_C1$Time_point)
  )+
  scale_y_log10()+
  theme_minimal()

p_residus
```

```{r savepredobsratioC1, include = F}
ggsave(
  filename = "TK_EPX_predobsratio.png",
  plot = p_residus,
  width = 8, height = 4,
  path = path_fig_C1
)
ggsave(
  filename = "TK_EPX_predobsratio.svg",
  plot = p_residus,
  width = 8, height = 4,
  path = path_fig_C1
)
```

## C1P

```{r, message=F, warning=FALSE}
#| fig-cap: Residuals
#| label: fig-EPXresidualsC1P
#| fig-height: 4
#| fig-width: 8

df_residuals_CiEPX_C1P <- df_predobs_CiEPX_ind_C1P |> 
  mutate(
    Residual = predict.endpoint - CiEPX_obs,
    Ratio_Residual = predict.endpoint/CiEPX_obs
    ) |> 
  mutate(
    Time_point = as.numeric(gsub("([0-9]+).*", "\\1" , as.character(Time_point_f))),
    Group = factor(Group, c("Uptake", "Elimination", "TK_BIS")),
    Time_relative = case_when(
      Group == "Uptake" ~ Time_point,
      Group == "TK_BIS" ~ Time_point,
      Group == "Elimination" ~ Time_point - 21
    )
    )

p_residus <- ggplot(df_residuals_CiEPX_C1P)+
  geom_point(
    aes(
      x = Time_point,
      y = Ratio_Residual,
      color = Group
    ),
    alpha=0.7
  )+
  labs(
    x = "Time point (days)",
    y = "Predicted/observed ratio"
  )+
  scale_color_manual(
    values = col_exposure_bis
    )+
  scale_x_continuous(
    breaks = unique(df_residuals_CiEPX_C1P$Time_point)
  )+
  scale_y_log10()+
  theme_minimal()

p_residus
```

```{r savepredobsratioC1P, include = F}
ggsave(
  filename = "TK_EPX_predobsratio.png",
  plot = p_residus,
  width = 8, height = 4,
  path = path_fig_C1P
)
ggsave(
  filename = "TK_EPX_predobsratio.svg",
  plot = p_residus,
  width = 8, height = 4,
  path = path_fig_C1P
)
```

## C2

```{r, message=F, warning=FALSE}
#| fig-cap: Residuals
#| label: fig-EPXresidualsC2
#| fig-height: 4
#| fig-width: 8

df_residuals_CiEPX_C2 <- df_predobs_CiEPX_ind_C2 |> 
  mutate(
    Residual = predict.endpoint - CiEPX_obs,
    Ratio_Residual = predict.endpoint/CiEPX_obs
    ) |> 
  mutate(
    Time_point = as.numeric(gsub("([0-9]+).*", "\\1" , as.character(Time_point_f))),
    Group = factor(Group, c("Uptake", "Elimination", "TK_BIS")),
    Time_relative = case_when(
      Group == "Uptake" ~ Time_point,
      Group == "TK_BIS" ~ Time_point,
      Group == "Elimination" ~ Time_point - 21
    )
    )

p_residus <- ggplot(df_residuals_CiEPX_C2)+
  geom_point(
    aes(
      x = Time_point,
      y = Ratio_Residual,
      color = Group
    ),
    alpha=0.7
  )+
  labs(
    x = "Time point (days)",
    y = "Predicted/observed ratio"
  )+
  scale_color_manual(
    values = col_exposure_bis
    )+
  scale_x_continuous(
    breaks = unique(df_residuals_CiEPX_C2$Time_point)
  )+
  scale_y_log10()+
  theme_minimal()

p_residus
```

```{r savepredobsratioC2, include = F}
ggsave(
  filename = "TK_EPX_predobsratio.png",
  plot = p_residus,
  width = 8, height = 4,
  path = path_fig_C2
)
ggsave(
  filename = "TK_EPX_predobsratio.svg",
  plot = p_residus,
  width = 8, height = 4,
  path = path_fig_C2
)
```

## C2P

```{r, message=F, warning=FALSE}
#| fig-cap: Residuals
#| label: fig-EPXresidualsC2P
#| fig-height: 4
#| fig-width: 8

df_residuals_CiEPX_C2P <- df_predobs_CiEPX_ind_C2P |> 
  mutate(
    Residual = predict.endpoint - CiEPX_obs,
    Ratio_Residual = predict.endpoint/CiEPX_obs
    ) |> 
  mutate(
    Time_point = as.numeric(gsub("([0-9]+).*", "\\1" , as.character(Time_point_f))),
    Group = factor(Group, c("Uptake", "Elimination", "TK_BIS")),
    Time_relative = case_when(
      Group == "Uptake" ~ Time_point,
      Group == "TK_BIS" ~ Time_point,
      Group == "Elimination" ~ Time_point - 21
    )
    )

p_residus <- ggplot(df_residuals_CiEPX_C2P)+
  geom_point(
    aes(
      x = Time_point,
      y = Ratio_Residual,
      color = Group
    ),
    alpha=0.7
  )+
  labs(
    x = "Time point (days)",
    y = "Predicted/observed ratio"
  )+
  scale_color_manual(
    values = col_exposure_bis
    )+
  scale_x_continuous(
    breaks = unique(df_residuals_CiEPX_C2P$Time_point)
  )+
  scale_y_log10()+
  theme_minimal()

p_residus
```

```{r savepredobsratioC2P, include = F}
ggsave(
  filename = "TK_EPX_predobsratio.png",
  plot = p_residus,
  width = 8, height = 4,
  path = path_fig_C2P
)
ggsave(
  filename = "TK_EPX_predobsratio.svg",
  plot = p_residus,
  width = 8, height = 4,
  path = path_fig_C2P
)
```
:::

### Full individual trajectories

```{r setpointindfullin, message=F, warning=F}
Time_min <- 0
Time_max <- 44
Time_step <- 0.25
Time_pred <- seq(Time_min, Time_max, Time_step)
print_times <- paste(Time_min, Time_max, Time_step, sep=", ")
Molecule <- "EPX"

######### C1 ############################################################
l_param_name_C1 <- "kuEPX, keEPX, a_growth"
f_Setpoint_ind_full(path_mod_EPX_C1, Molecule, print_times, l_param_name_C1)

######### C1P ############################################################
l_param_name_C1P <- "kuEPX, keEPX, phi, a_growth"
f_Setpoint_ind_full(path_mod_EPX_C1P, Molecule, print_times, l_param_name_C1P)

######### C2 ############################################################
l_param_name_C2 <- "kuEPX, keEPX, kperiph, a_growth"
f_Setpoint_ind_full(path_mod_EPX_C2, Molecule, print_times, l_param_name_C2)

######### C2P ############################################################
l_param_name_C2P <- "kuEPX, keEPX, kperiph, phi, a_growth"
f_Setpoint_ind_full(path_mod_EPX_C2P, Molecule, print_times, l_param_name_C2P)

########## Observed data ##################

dObs_ind <- df_TK_EPX |> 
  mutate(ID = as.numeric(ID))
colnames(dObs_ind)[colnames(dObs_ind) == "Weight"] <- "Weight_obs"
colnames(dObs_ind)[colnames(dObs_ind) == "CiEPX"] <- "CiEPX_obs"
colnames(dObs_ind)[colnames(dObs_ind) == "t"] <- "Times"

time_limits <- dObs_ind %>%
  group_by(ID) %>%
  summarise(time_cutoff = max(Time, na.rm = TRUE) + 5)

Time_points_Nb_rep <- dObs_ind |> 
  dplyr::select(ID, Time_point_f, Nb_rep)

y_segment <- 750

df_phases <- dObs_ind |>
  arrange(ID, Time) |>
  group_by(ID) |>
  mutate(
    row = row_number(),
    t_start = Time,
    t_end = lead(Time),  
    segment = row,
    y = y_segment
  ) |>
  filter(!is.na(t_end)) |>  
  dplyr::select(ID, segment, t_start, t_end, y, Experiment) |>
  ungroup() |> 
  mutate(
    Phase = case_when(
      (segment == 1 & ID < 65) ~ 1,
      (segment == 2 & ID < 65) ~ 3,
      (segment == 1 & ID > 64) ~ 1,
      (segment == 2 & ID > 64) ~ 2,
      (segment == 3 & ID > 64) ~ 3,
      (Experiment == "TKBIS" & segment == 1)~1,
      (Experiment == "TKBIS" & segment == 2)~3
    )
  )

```

An example of how to run the simulations for the individual trajectories is given in the bash code block below. You need to be in the right folder to launch a given model.

```{bash, results=F, eval=F}
pwd
cd ..
cd ..
cd mod/TK_EPX
pwd

for j in $(seq 1 71); do
./mcsim.m_TK_EPX TK_EPX_Setpoint_ind_full_${j}.in
done

```

```{r EPXdatapredfull, message=F, warning=F}
##| cache: false

#nb_rows_ind_C1 <- NC_C1*N_iter_setpoint_C1+1

########## C1 #############################################

Sim.Res.ind.full_C1 <- lapply(1:Nb_experiment_C1, function(j) {
  read_tsv(file.path(path_mod_EPX_C1, paste0("Setpoints_ind_full_", j, ".out"))) %>%
    mutate(sim = j)
}) %>%
  bind_rows()

df_mod_ind_C1 <- NULL

for (i in 1:Nb_experiment_C1){
  
  ID_i <- unique(dObs_ind$ID)[i]

  Sim.Res.ind.full_i  <- subset(Sim.Res.ind.full_C1, sim == i) |> 
    dplyr::select(where(~ !all(is.na(.x))))
  
  dObs_i <- subset(dObs_ind, ID == ID_i)
  
  Nom_Endpoints = c("Weight", "CiEPX", "C_exposure")
  
  Nsortie = length(Nom_Endpoints)
  
  MPV = IC_min = IC_max = Endpoint = index = NULL
  
  for (j in 1:length(Nom_Endpoints)){
    
    index =grep(paste0("^",Nom_Endpoints[j],"_") , colnames(Sim.Res.ind.full_i), fixed=FALSE)

    
    Data_sim = as.matrix( Sim.Res.ind.full_i[ , index] )
    
    MPV    = c(  MPV,  as.numeric( Data_sim[nrow(Data_sim), ] ) )
    IC_min = c(IC_min,  apply(Data_sim, 2, quantile,  0.025, na.rm=TRUE) )
    IC_max = c(IC_max,  apply(Data_sim, 2, quantile,  0.975, na.rm=TRUE) ) 
    
    Endpoint = c(Endpoint, rep(Nom_Endpoints[j], ncol(Data_sim)))
  }
  
  df_mod_ind_i <- data.frame(
    predict.endpoint = MPV,
    Time    = rep(Time_pred, Nsortie),
    low     = IC_min,
    up      = IC_max,
    Endpt   = Endpoint
    )
  
  df_mod_ind_i <- df_mod_ind_i %>%
    mutate(ID=ID_i)

  df_mod_ind_C1 <- rbind(df_mod_ind_C1, df_mod_ind_i)
}

df_mod_Weight_ind_C1 <- subset(df_mod_ind_C1, Endpt == "Weight")
df_mod_CiEPX_ind_C1 <- subset(df_mod_ind_C1, Endpt == "CiEPX")
df_mod_CeEPX_ind_C1 <- subset(df_mod_ind_C1, Endpt == "C_exposure")


df_mod_CiEPX_ind_t_C1 <- df_mod_CiEPX_ind_C1 %>%
  left_join(time_limits, by = "ID") %>%
  filter(Time <= time_cutoff) %>%
  dplyr::select(-time_cutoff) |> 
  left_join(Time_points_Nb_rep, by="ID")

df_mod_Weight_ind_t_C1 <- df_mod_Weight_ind_C1 %>%
  left_join(time_limits, by = "ID") %>%
  filter(Time <= time_cutoff) %>%
  dplyr::select(-time_cutoff) |> 
  left_join(Time_points_Nb_rep, by="ID")

df_mod_CeEPX_ind_t_C1 <- df_mod_CeEPX_ind_C1 %>%
  left_join(time_limits, by = "ID") %>%
  filter(Time <= time_cutoff) %>%
  dplyr::select(-time_cutoff) |> 
  left_join(Time_points_Nb_rep, by="ID")

########## C1P #############################################

Sim.Res.ind.full_C1P <- lapply(1:Nb_experiment_C1P, function(j) {
  read_tsv(file.path(path_mod_EPX_C1P, paste0("Setpoints_ind_full_", j, ".out"))) %>%
    mutate(sim = j)
}) %>%
  bind_rows()

df_mod_ind_C1P <- NULL

for (i in 1:Nb_experiment_C1P){
  
  ID_i <- unique(dObs_ind$ID)[i]

  Sim.Res.ind.full_i  <- subset(Sim.Res.ind.full_C1P, sim == i) |> 
    dplyr::select(where(~ !all(is.na(.x))))
  
  dObs_i <- subset(dObs_ind, ID == ID_i)
  
  Nom_Endpoints = c("Weight", "CiEPX", "C_exposure")
  
  Nsortie = length(Nom_Endpoints)
  
  MPV = IC_min = IC_max = Endpoint = index = NULL
  
  for (j in 1:length(Nom_Endpoints)){
    
    index =grep(paste0("^",Nom_Endpoints[j],"_") , colnames(Sim.Res.ind.full_i), fixed=FALSE)

    
    Data_sim = as.matrix( Sim.Res.ind.full_i[ , index] )
    
    MPV    = c(  MPV,  as.numeric( Data_sim[nrow(Data_sim), ] ) )
    IC_min = c(IC_min,  apply(Data_sim, 2, quantile,  0.025, na.rm=TRUE) )
    IC_max = c(IC_max,  apply(Data_sim, 2, quantile,  0.975, na.rm=TRUE) ) 
    
    Endpoint = c(Endpoint, rep(Nom_Endpoints[j], ncol(Data_sim)))
  }
  
  df_mod_ind_i <- data.frame(
    predict.endpoint = MPV,
    Time    = rep(Time_pred, Nsortie),
    low     = IC_min,
    up      = IC_max,
    Endpt   = Endpoint
    )
  
  df_mod_ind_i <- df_mod_ind_i %>%
    mutate(ID=ID_i)

  df_mod_ind_C1P <- rbind(df_mod_ind_C1P, df_mod_ind_i)
}

df_mod_Weight_ind_C1P <- subset(df_mod_ind_C1P, Endpt == "Weight")
df_mod_CiEPX_ind_C1P <- subset(df_mod_ind_C1P, Endpt == "CiEPX")
df_mod_CeEPX_ind_C1P <- subset(df_mod_ind_C1P, Endpt == "C_exposure")


df_mod_CiEPX_ind_t_C1P <- df_mod_CiEPX_ind_C1P %>%
  left_join(time_limits, by = "ID") %>%
  filter(Time <= time_cutoff) %>%
  dplyr::select(-time_cutoff) |> 
  left_join(Time_points_Nb_rep, by="ID")

df_mod_Weight_ind_t_C1P <- df_mod_Weight_ind_C1P %>%
  left_join(time_limits, by = "ID") %>%
  filter(Time <= time_cutoff) %>%
  dplyr::select(-time_cutoff) |> 
  left_join(Time_points_Nb_rep, by="ID")

df_mod_CeEPX_ind_t_C1P <- df_mod_CeEPX_ind_C1P %>%
  left_join(time_limits, by = "ID") %>%
  filter(Time <= time_cutoff) %>%
  dplyr::select(-time_cutoff) |> 
  left_join(Time_points_Nb_rep, by="ID")

########## C2 #############################################

Sim.Res.ind.full_C2 <- lapply(1:Nb_experiment_C2, function(j) {
  read_tsv(file.path(path_mod_EPX_C2, paste0("Setpoints_ind_full_", j, ".out"))) %>%
    mutate(sim = j)
}) %>%
  bind_rows()

df_mod_ind_C2 <- NULL

for (i in 1:Nb_experiment_C2){
  
  ID_i <- unique(dObs_ind$ID)[i]

  Sim.Res.ind.full_i  <- subset(Sim.Res.ind.full_C2, sim == i) |> 
    dplyr::select(where(~ !all(is.na(.x))))
  
  dObs_i <- subset(dObs_ind, ID == ID_i)
  
  Nom_Endpoints = c("Weight", "CiEPX", "C_exposure")
  
  Nsortie = length(Nom_Endpoints)
  
  MPV = IC_min = IC_max = Endpoint = index = NULL
  
  for (j in 1:length(Nom_Endpoints)){
    
    index =grep(paste0("^",Nom_Endpoints[j],"_") , colnames(Sim.Res.ind.full_i), fixed=FALSE)

    
    Data_sim = as.matrix( Sim.Res.ind.full_i[ , index] )
    
    MPV    = c(  MPV,  as.numeric( Data_sim[nrow(Data_sim), ] ) )
    IC_min = c(IC_min,  apply(Data_sim, 2, quantile,  0.025, na.rm=TRUE) )
    IC_max = c(IC_max,  apply(Data_sim, 2, quantile,  0.975, na.rm=TRUE) ) 
    
    Endpoint = c(Endpoint, rep(Nom_Endpoints[j], ncol(Data_sim)))
  }
  
  df_mod_ind_i <- data.frame(
    predict.endpoint = MPV,
    Time    = rep(Time_pred, Nsortie),
    low     = IC_min,
    up      = IC_max,
    Endpt   = Endpoint
    )
  
  df_mod_ind_i <- df_mod_ind_i %>%
    mutate(ID=ID_i)

  df_mod_ind_C2 <- rbind(df_mod_ind_C2, df_mod_ind_i)
}

df_mod_Weight_ind_C2 <- subset(df_mod_ind_C2, Endpt == "Weight")
df_mod_CiEPX_ind_C2 <- subset(df_mod_ind_C2, Endpt == "CiEPX")
df_mod_CeEPX_ind_C2 <- subset(df_mod_ind_C2, Endpt == "C_exposure")


df_mod_CiEPX_ind_t_C2 <- df_mod_CiEPX_ind_C2 %>%
  left_join(time_limits, by = "ID") %>%
  filter(Time <= time_cutoff) %>%
  dplyr::select(-time_cutoff) |> 
  left_join(Time_points_Nb_rep, by="ID")

df_mod_Weight_ind_t_C2 <- df_mod_Weight_ind_C2 %>%
  left_join(time_limits, by = "ID") %>%
  filter(Time <= time_cutoff) %>%
  dplyr::select(-time_cutoff) |> 
  left_join(Time_points_Nb_rep, by="ID")

df_mod_CeEPX_ind_t_C2 <- df_mod_CeEPX_ind_C2 %>%
  left_join(time_limits, by = "ID") %>%
  filter(Time <= time_cutoff) %>%
  dplyr::select(-time_cutoff) |> 
  left_join(Time_points_Nb_rep, by="ID")

########## C2P #############################################

Sim.Res.ind.full_C2P <- lapply(1:Nb_experiment_C2P, function(j) {
  read_tsv(file.path(path_mod_EPX_C2P, paste0("Setpoints_ind_full_", j, ".out"))) %>%
    mutate(sim = j)
}) %>%
  bind_rows()

df_mod_ind_C2P <- NULL

for (i in 1:Nb_experiment_C2P){
  
  ID_i <- unique(dObs_ind$ID)[i]

  Sim.Res.ind.full_i  <- subset(Sim.Res.ind.full_C2P, sim == i) |> 
    dplyr::select(where(~ !all(is.na(.x))))
  
  dObs_i <- subset(dObs_ind, ID == ID_i)
  
  Nom_Endpoints = c("Weight", "CiEPX", "C_exposure")
  
  Nsortie = length(Nom_Endpoints)
  
  MPV = IC_min = IC_max = Endpoint = index = NULL
  
  for (j in 1:length(Nom_Endpoints)){
    
    index =grep(paste0("^",Nom_Endpoints[j],"_") , colnames(Sim.Res.ind.full_i), fixed=FALSE)

    
    Data_sim = as.matrix( Sim.Res.ind.full_i[ , index] )
    
    MPV    = c(  MPV,  as.numeric( Data_sim[nrow(Data_sim), ] ) )
    IC_min = c(IC_min,  apply(Data_sim, 2, quantile,  0.025, na.rm=TRUE) )
    IC_max = c(IC_max,  apply(Data_sim, 2, quantile,  0.975, na.rm=TRUE) ) 
    
    Endpoint = c(Endpoint, rep(Nom_Endpoints[j], ncol(Data_sim)))
  }
  
  df_mod_ind_i <- data.frame(
    predict.endpoint = MPV,
    Time    = rep(Time_pred, Nsortie),
    low     = IC_min,
    up      = IC_max,
    Endpt   = Endpoint
    )
  
  df_mod_ind_i <- df_mod_ind_i %>%
    mutate(ID=ID_i)

  df_mod_ind_C2P <- rbind(df_mod_ind_C2P, df_mod_ind_i)
}

df_mod_Weight_ind_C2P <- subset(df_mod_ind_C2P, Endpt == "Weight")
df_mod_CiEPX_ind_C2P <- subset(df_mod_ind_C2P, Endpt == "CiEPX")
df_mod_CeEPX_ind_C2P <- subset(df_mod_ind_C2P, Endpt == "C_exposure")


df_mod_CiEPX_ind_t_C2P <- df_mod_CiEPX_ind_C2P %>%
  left_join(time_limits, by = "ID") %>%
  filter(Time <= time_cutoff) %>%
  dplyr::select(-time_cutoff) |> 
  left_join(Time_points_Nb_rep, by="ID")

df_mod_Weight_ind_t_C2P <- df_mod_Weight_ind_C2P %>%
  left_join(time_limits, by = "ID") %>%
  filter(Time <= time_cutoff) %>%
  dplyr::select(-time_cutoff) |> 
  left_join(Time_points_Nb_rep, by="ID")

df_mod_CeEPX_ind_t_C2P <- df_mod_CeEPX_ind_C2P %>%
  left_join(time_limits, by = "ID") %>%
  filter(Time <= time_cutoff) %>%
  dplyr::select(-time_cutoff) |> 
  left_join(Time_points_Nb_rep, by="ID")


#########################

library(ggforce)

ID_tri <- unique(df_TK_EPX$ID)

dObs_ind_plot <- dObs_ind |> 
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na() |> 
  filter(ID %in% ID_tri)|> 
  mutate(
    No_rep = paste0("No ", Nb_rep),
    Time_point = as.numeric(gsub("([0-9]+).*", "\\1" , as.character(Time_point_f))),
    Time_point_days = paste0(Time_point_f, " days"),
    Time_point_days = fct_reorder(Time_point_days, as.numeric(Time_point))
    )

df_phases_plot <- subset(df_phases, ID %in% ID_tri)|> 
  left_join(Time_points_Nb_rep, by="ID") |> 
  mutate(
    No_rep = paste0("No ", Nb_rep),
    Time_point = as.numeric(gsub("([0-9]+).*", "\\1" , as.character(Time_point_f))),
    Time_point_days = paste0(Time_point_f, " days"),
    Time_point_days = fct_reorder(Time_point_days, as.numeric(Time_point))
    )

```

::::::: panel-tabset
## C1

::: panel-tabset
## Internal concentrations - Normal scale

```{r EPXpredcurvesdataC1, message=F, warning=F}
#| fig-cap: Estimated toxicokinetic of the EPX concentration in earthworms exposed to 1000 ng/g of EPX. Red points represent the experimental data, the blue curve represent the estimated toxicokinetic curve and the transparent blue band correspond to the credibility interval of the model. 
#| fig-label: fig-EPXdatapredfullC1
#| fig-width: 8
#| fig-height: 20

df_mod_CiEPX_ind_t_plot_C1 <- subset(df_mod_CiEPX_ind_t_C1, ID %in% ID_tri) |> 
  mutate(
    No_rep = paste0("No ", Nb_rep),
    Time_point = as.numeric(gsub("([0-9]+).*", "\\1" , as.character(Time_point_f))),
    Time_point_days = paste0(Time_point_f, " days"),
    Time_point_days = fct_reorder(Time_point_days, as.numeric(Time_point))
  )

df_mod_CeEPX_ind_t_plot_C1 <- subset(df_mod_CeEPX_ind_t_C1, ID %in% ID_tri)
df_mod_Weight_ind_t_plot_C1 <- subset(df_mod_Weight_ind_t_C1, ID %in% ID_tri) |> 
  mutate(
    No_rep = paste0("No ", Nb_rep),
    Time_point = as.numeric(gsub("([0-9]+).*", "\\1" , as.character(Time_point_f))),
    Time_point_days = paste0(Time_point_f, " days"),
    Time_point_days = fct_reorder(Time_point_days, as.numeric(Time_point))
  )

alpha_point <- 0.5
col_exposure <- c(Nord_aurora[2], Nord_aurora[3], Nord_aurora[4])

p_CiEPX_traj <- ggplot()+
  
  geom_segment(
    data = df_phases_plot,
    aes(
      x = t_start,
      xend = t_end,
      y = y,
      yend = y,
      group = ID,
      color = factor(Phase)
    ),
    linewidth = 2,
    alpha = 0.7
  ) +

  geom_line(
    data=df_mod_CiEPX_ind_t_plot_C1,
    aes(
      x=Time,
      y= low,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX_ind_t_plot_C1,
    aes(
      x=Time,
      y= up,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX_ind_t_plot_C1,
    aes(
      x=Time,
      y= predict.endpoint,
      group = ID
      ),
    color = col_EPX,
    lwd=1
    )+
  geom_ribbon(
    data=df_mod_CiEPX_ind_t_plot_C1,
    aes(
      x=Time,
      ymax= up,
      ymin= low,
      group = ID
      ),
    fill = col_EPX,
    alpha=0.1
    )+
  geom_point(
    data = dObs_ind_plot,
    aes(
      x = Time,
      y = CiEPX_obs
    ),
    size = 2,
    alpha = 0.7,
    color = col_red
  )+
  # facet_wrap(
  #   ~ID,
  #   ncol=4,
  #   #scales = "free_x"
  #   )+
  facet_grid(
    vars(Time_point_days), vars(No_rep)#,
    )+
  scale_color_manual(
    values = col_exposure,
    label = c("Uptake", "Elimination", "Depuration"),
    name = "Phase"
    )+
  labs(
    x = "Time (days)",
    y = "CiEPX (ng/g)"
  )+
  #lims(y=c(0, 300))+
  theme_minimal()
  

p_CiEPX_traj 

```

```{r, include=F}

Time_point_1 <- as.character(seq(22, 42, 1))

df_phases_plot_1 <- df_phases_plot |> 
  filter(!(Time_point_f %in% Time_point_1))
df_mod_CiEPX_ind_t_plot_C1_1 <- df_mod_CiEPX_ind_t_plot_C1 |> 
  filter(!(Time_point_f %in% Time_point_1))
dObs_ind_plot_1 <- dObs_ind_plot |> 
  filter(!(Time_point_f %in% Time_point_1))

df_phases_plot_2 <- df_phases_plot |> 
  filter(Time_point_f %in% Time_point_1)
df_mod_CiEPX_ind_t_plot_C1_2 <- df_mod_CiEPX_ind_t_plot_C1 |> 
  filter(Time_point_f %in% Time_point_1)
dObs_ind_plot_2 <- dObs_ind_plot |> 
  filter(Time_point_f %in% Time_point_1)

p_CiEPX_traj_1 <- ggplot()+
  
  geom_segment(
    data = df_phases_plot_1,
    aes(
      x = t_start,
      xend = t_end,
      y = y,
      yend = y,
      group = ID,
      color = factor(Phase)
    ),
    linewidth = 2,
    alpha = 0.7
  ) +

  geom_line(
    data=df_mod_CiEPX_ind_t_plot_C1_1,
    aes(
      x=Time,
      y= low,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX_ind_t_plot_C1_1,
    aes(
      x=Time,
      y= up,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX_ind_t_plot_C1_1,
    aes(
      x=Time,
      y= predict.endpoint,
      group = ID
      ),
    color = col_EPX,
    lwd=1
    )+
  geom_ribbon(
    data=df_mod_CiEPX_ind_t_plot_C1_1,
    aes(
      x=Time,
      ymax= up,
      ymin= low,
      group = ID
      ),
    fill = col_EPX,
    alpha=0.1
    )+
  geom_point(
    data = dObs_ind_plot_1,
    aes(
      x = Time,
      y = CiEPX_obs
    ),
    size = 2,
    alpha = 0.7,
    color = col_red
  )+
  facet_grid(
    vars(Time_point_days), vars(No_rep)#,
    )+
  scale_color_manual(
    values = col_exposure,
    label = c("Uptake", "Elimination", "Depuration"),
    name = "Phase"
    )+
  labs(
    x = "Time (days)",
    y = "CiEPX (ng/g)"
  )+
  theme_minimal()

p_CiEPX_traj_2 <- ggplot()+
  
  geom_segment(
    data = df_phases_plot_2,
    aes(
      x = t_start,
      xend = t_end,
      y = y,
      yend = y,
      group = ID,
      color = factor(Phase)
    ),
    linewidth = 2,
    alpha = 0.7
  ) +

  geom_line(
    data=df_mod_CiEPX_ind_t_plot_C1_2,
    aes(
      x=Time,
      y= low,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX_ind_t_plot_C1_2,
    aes(
      x=Time,
      y= up,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX_ind_t_plot_C1_2,
    aes(
      x=Time,
      y= predict.endpoint,
      group = ID
      ),
    color = col_EPX,
    lwd=1
    )+
  geom_ribbon(
    data=df_mod_CiEPX_ind_t_plot_C1_2,
    aes(
      x=Time,
      ymax= up,
      ymin= low,
      group = ID
      ),
    fill = col_EPX,
    alpha=0.1
    )+
  geom_point(
    data = dObs_ind_plot_2,
    aes(
      x = Time,
      y = CiEPX_obs
    ),
    size = 2,
    alpha = 0.7,
    color = col_red
  )+
  facet_grid(
    vars(Time_point_days), vars(No_rep)#,
    )+
  scale_color_manual(
    values = col_exposure,
    label = c("Uptake", "Elimination", "Depuration"),
    name = "Phase"
    )+
  labs(
    x = "Time (days)",
    y = "CiEPX (ng/g)"
  )+
  theme_minimal()
  
```

## Internal concentrations - Log-scale

```{r, message=F, warning=F}
#| fig-cap: Estimated toxicokinetic of the EPX concentration in earthworms exposed to 1000 ng/g of EPX. Red points represent the experimental data, the blue curve represent the estimated toxicokinetic curve and the transparent blue band correspond to the credibility interval of the model. 
#| fig-label: fig-EPXdatapredfulllogC1
#| fig-width: 8
#| fig-height: 20

p_CiEPX_traj_log <- p_CiEPX_traj + scale_y_log10()

p_CiEPX_traj_log

```

## Weights

```{r EPXpredcurvesdataWC1, message=F, warning=F}
#| fig-cap: Weight predictions
#| fig-label: fig-EPXdatapredfullWC1
#| fig-width: 8
#| fig-height: 20

alpha_point <- 0.5

p_W <- ggplot()+
  geom_line(
    data=df_mod_Weight_ind_t_plot_C1,
    aes(
      x=Time,
      y= low,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_Weight_ind_t_plot_C1,
    aes(
      x=Time,
      y= up,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_Weight_ind_t_plot_C1,
    aes(
      x=Time,
      y= predict.endpoint,
      group = ID
      ),
    color = col_EPX,
    lwd=1
    )+
  geom_ribbon(
    data=df_mod_Weight_ind_t_plot_C1, 
    aes(
      x=Time, 
      ymax= up, 
      ymin= low,
      group = ID
      ),
    fill = col_EPX,
    alpha=0.1
    )+
  geom_point(
    data = dObs_ind_plot,
    aes(
      x = Time,
      y = Weight_obs
    ),
    size = 2,
    alpha = 0.7,
    color = col_red
  )+
  # facet_wrap(
  #   ~ID,
  #   ncol = 4,
  #   scales = "free"
  #   )+
  facet_grid(
    vars(Time_point_days), vars(No_rep)#,
    )+
  #lims(y=c(0, 1500))+
  labs(
    x = "Time (days)",
    y = "Weight (g)"
  )+
  theme_minimal()

p_W

```

```{r savetrajC1, include = F}
ggsave(
  filename="TK_EPX_comptrajpred.png", 
  plot=p_CiEPX_traj , 
  width=8, height = 20, 
  path=path_fig_C1
  )
ggsave(
  filename="TK_EPX_comptrajpred.svg", 
  plot=p_CiEPX_traj , 
  width=8, height = 20, 
  path=path_fig_C1
  )
ggsave(
  filename="TK_EPX_comptrajpred_log.png", 
  plot=p_CiEPX_traj_log , 
  width=8, height = 20, 
  path=path_fig_C1
  )
ggsave(
  filename="TK_EPX_comptrajpred_log.svg", 
  plot=p_CiEPX_traj_log , 
  width=8, height = 20, 
  path=path_fig_C1
  )
ggsave(
  filename="TK_EPX_comptrajpredW.png", 
  plot=p_W , 
  width=8, height = 20, 
  path=path_fig_C1
  )
ggsave(
  filename="TK_EPX_comptrajpredW.svg", 
  plot=p_W , 
  width=8, height = 20, 
  path=path_fig_C1
  )

ggsave(
  filename="TK_EPX_comptrajpred_1.png", 
  plot=p_CiEPX_traj_1, 
  width=8, height = 10, 
  path=path_fig_C1
  )

ggsave(
  filename="TK_EPX_comptrajpred_2.png", 
  plot=p_CiEPX_traj_2 , 
  width=8, height = 10, 
  path=path_fig_C1
  )


```
:::

## C1P

::: panel-tabset
## Internal concentrations - Normal scale

```{r EPXpredcurvesdataC1P, message=F, warning=F}
#| fig-cap: Estimated toxicokinetic of the EPX concentration in earthworms exposed to 1000 ng/g of EPX. Red points represent the experimental data, the blue curve represent the estimated toxicokinetic curve and the transparent blue band correspond to the credibility interval of the model. 
#| fig-label: fig-EPXdatapredfullC1P
#| fig-width: 8
#| fig-height: 20

df_mod_CiEPX_ind_t_plot_C1P <- subset(df_mod_CiEPX_ind_t_C1P, ID %in% ID_tri) |> 
  mutate(
    No_rep = paste0("No ", Nb_rep),
    Time_point = as.numeric(gsub("([0-9]+).*", "\\1" , as.character(Time_point_f))),
    Time_point_days = paste0(Time_point_f, " days"),
    Time_point_days = fct_reorder(Time_point_days, as.numeric(Time_point))
  )

df_mod_CeEPX_ind_t_plot_C1P <- subset(df_mod_CeEPX_ind_t_C1P, ID %in% ID_tri)
df_mod_Weight_ind_t_plot_C1P <- subset(df_mod_Weight_ind_t_C1P, ID %in% ID_tri) |> 
  mutate(
    No_rep = paste0("No ", Nb_rep),
    Time_point = as.numeric(gsub("([0-9]+).*", "\\1" , as.character(Time_point_f))),
    Time_point_days = paste0(Time_point_f, " days"),
    Time_point_days = fct_reorder(Time_point_days, as.numeric(Time_point))
  )

alpha_point <- 0.5
col_exposure <- c(Nord_aurora[2], Nord_aurora[3], Nord_aurora[4])

p_CiEPX_traj <- ggplot()+
  
  geom_segment(
    data = df_phases_plot,
    aes(
      x = t_start,
      xend = t_end,
      y = y,
      yend = y,
      group = ID,
      color = factor(Phase)
    ),
    linewidth = 2,
    alpha = 0.7
  ) +

  geom_line(
    data=df_mod_CiEPX_ind_t_plot_C1P,
    aes(
      x=Time,
      y= low,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX_ind_t_plot_C1P,
    aes(
      x=Time,
      y= up,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX_ind_t_plot_C1P,
    aes(
      x=Time,
      y= predict.endpoint,
      group = ID
      ),
    color = col_EPX,
    lwd=1
    )+
  geom_ribbon(
    data=df_mod_CiEPX_ind_t_plot_C1P,
    aes(
      x=Time,
      ymax= up,
      ymin= low,
      group = ID
      ),
    fill = col_EPX,
    alpha=0.1
    )+
  geom_point(
    data = dObs_ind_plot,
    aes(
      x = Time,
      y = CiEPX_obs
    ),
    size = 2,
    alpha = 0.7,
    color = col_red
  )+
  # facet_wrap(
  #   ~ID,
  #   ncol=4,
  #   #scales = "free_x"
  #   )+
  facet_grid(
    vars(Time_point_days), vars(No_rep)#,
    )+
  scale_color_manual(
    values = col_exposure,
    label = c("Uptake", "Elimination", "Depuration"),
    name = "Phase"
    )+
  labs(
    x = "Time (days)",
    y = "CiEPX (ng/g)"
  )+
  #lims(y=c(0, 300))+
  theme_minimal()
  

p_CiEPX_traj 

```

```{r, include=F}

Time_point_1 <- as.character(seq(22, 42, 1))

df_phases_plot_1 <- df_phases_plot |> 
  filter(!(Time_point_f %in% Time_point_1))
df_mod_CiEPX_ind_t_plot_C1P_1 <- df_mod_CiEPX_ind_t_plot_C1P |> 
  filter(!(Time_point_f %in% Time_point_1))
dObs_ind_plot_1 <- dObs_ind_plot |> 
  filter(!(Time_point_f %in% Time_point_1))

df_phases_plot_2 <- df_phases_plot |> 
  filter(Time_point_f %in% Time_point_1)
df_mod_CiEPX_ind_t_plot_C1P_2 <- df_mod_CiEPX_ind_t_plot_C1P |> 
  filter(Time_point_f %in% Time_point_1)
dObs_ind_plot_2 <- dObs_ind_plot |> 
  filter(Time_point_f %in% Time_point_1)

p_CiEPX_traj_1 <- ggplot()+
  
  geom_segment(
    data = df_phases_plot_1,
    aes(
      x = t_start,
      xend = t_end,
      y = y,
      yend = y,
      group = ID,
      color = factor(Phase)
    ),
    linewidth = 2,
    alpha = 0.7
  ) +

  geom_line(
    data=df_mod_CiEPX_ind_t_plot_C1P_1,
    aes(
      x=Time,
      y= low,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX_ind_t_plot_C1P_1,
    aes(
      x=Time,
      y= up,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX_ind_t_plot_C1P_1,
    aes(
      x=Time,
      y= predict.endpoint,
      group = ID
      ),
    color = col_EPX,
    lwd=1
    )+
  geom_ribbon(
    data=df_mod_CiEPX_ind_t_plot_C1P_1,
    aes(
      x=Time,
      ymax= up,
      ymin= low,
      group = ID
      ),
    fill = col_EPX,
    alpha=0.1
    )+
  geom_point(
    data = dObs_ind_plot_1,
    aes(
      x = Time,
      y = CiEPX_obs
    ),
    size = 2,
    alpha = 0.7,
    color = col_red
  )+
  facet_grid(
    vars(Time_point_days), vars(No_rep)#,
    )+
  scale_color_manual(
    values = col_exposure,
    label = c("Uptake", "Elimination", "Depuration"),
    name = "Phase"
    )+
  labs(
    x = "Time (days)",
    y = "CiEPX (ng/g)"
  )+
  theme_minimal()

p_CiEPX_traj_2 <- ggplot()+
  
  geom_segment(
    data = df_phases_plot_2,
    aes(
      x = t_start,
      xend = t_end,
      y = y,
      yend = y,
      group = ID,
      color = factor(Phase)
    ),
    linewidth = 2,
    alpha = 0.7
  ) +

  geom_line(
    data=df_mod_CiEPX_ind_t_plot_C1P_2,
    aes(
      x=Time,
      y= low,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX_ind_t_plot_C1P_2,
    aes(
      x=Time,
      y= up,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX_ind_t_plot_C1P_2,
    aes(
      x=Time,
      y= predict.endpoint,
      group = ID
      ),
    color = col_EPX,
    lwd=1
    )+
  geom_ribbon(
    data=df_mod_CiEPX_ind_t_plot_C1P_2,
    aes(
      x=Time,
      ymax= up,
      ymin= low,
      group = ID
      ),
    fill = col_EPX,
    alpha=0.1
    )+
  geom_point(
    data = dObs_ind_plot_2,
    aes(
      x = Time,
      y = CiEPX_obs
    ),
    size = 2,
    alpha = 0.7,
    color = col_red
  )+
  facet_grid(
    vars(Time_point_days), vars(No_rep)#,
    )+
  scale_color_manual(
    values = col_exposure,
    label = c("Uptake", "Elimination", "Depuration"),
    name = "Phase"
    )+
  labs(
    x = "Time (days)",
    y = "CiEPX (ng/g)"
  )+
  theme_minimal()
  
```

## Internal concentrations - Log-scale

```{r, message=F, warning=F}
#| fig-cap: Estimated toxicokinetic of the EPX concentration in earthworms exposed to 1000 ng/g of EPX. Red points represent the experimental data, the blue curve represent the estimated toxicokinetic curve and the transparent blue band correspond to the credibility interval of the model. 
#| fig-label: fig-EPXdatapredfulllogC1P
#| fig-width: 8
#| fig-height: 20

p_CiEPX_traj_log <- p_CiEPX_traj + scale_y_log10()

p_CiEPX_traj_log

```

## Weights

```{r EPXpredcurvesdataWC1P, message=F, warning=F}
#| fig-cap: Weight predictions
#| fig-label: fig-EPXdatapredfullWC1P
#| fig-width: 8
#| fig-height: 20

alpha_point <- 0.5

p_W <- ggplot()+
  geom_line(
    data=df_mod_Weight_ind_t_plot_C1P,
    aes(
      x=Time,
      y= low,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_Weight_ind_t_plot_C1P,
    aes(
      x=Time,
      y= up,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_Weight_ind_t_plot_C1P,
    aes(
      x=Time,
      y= predict.endpoint,
      group = ID
      ),
    color = col_EPX,
    lwd=1
    )+
  geom_ribbon(
    data=df_mod_Weight_ind_t_plot_C1P, 
    aes(
      x=Time, 
      ymax= up, 
      ymin= low,
      group = ID
      ),
    fill = col_EPX,
    alpha=0.1
    )+
  geom_point(
    data = dObs_ind_plot,
    aes(
      x = Time,
      y = Weight_obs
    ),
    size = 2,
    alpha = 0.7,
    color = col_red
  )+
  # facet_wrap(
  #   ~ID,
  #   ncol = 4,
  #   scales = "free"
  #   )+
  facet_grid(
    vars(Time_point_days), vars(No_rep)#,
    )+
  #lims(y=c(0, 1500))+
  labs(
    x = "Time (days)",
    y = "Weight (g)"
  )+
  theme_minimal()

p_W

```

```{r savetrajC1P, include = F}
ggsave(
  filename="TK_EPX_comptrajpred.png", 
  plot=p_CiEPX_traj , 
  width=8, height = 20, 
  path=path_fig_C1P
  )
ggsave(
  filename="TK_EPX_comptrajpred.svg", 
  plot=p_CiEPX_traj , 
  width=8, height = 20, 
  path=path_fig_C1P
  )
ggsave(
  filename="TK_EPX_comptrajpred_log.png", 
  plot=p_CiEPX_traj_log , 
  width=8, height = 20, 
  path=path_fig_C1P
  )
ggsave(
  filename="TK_EPX_comptrajpred_log.svg", 
  plot=p_CiEPX_traj_log , 
  width=8, height = 20, 
  path=path_fig_C1P
  )
ggsave(
  filename="TK_EPX_comptrajpredW.png", 
  plot=p_W , 
  width=8, height = 20, 
  path=path_fig_C1P
  )
ggsave(
  filename="TK_EPX_comptrajpredW.svg", 
  plot=p_W , 
  width=8, height = 20, 
  path=path_fig_C1P
  )

ggsave(
  filename="TK_EPX_comptrajpred_1.png", 
  plot=p_CiEPX_traj_1, 
  width=8, height = 10, 
  path=path_fig_C1P
  )

ggsave(
  filename="TK_EPX_comptrajpred_2.png", 
  plot=p_CiEPX_traj_2 , 
  width=8, height = 10, 
  path=path_fig_C1P
  )
```
:::

## C2

::: panel-tabset
## Internal concentrations - Normal scale

```{r EPXpredcurvesdataC2, message=F, warning=F}
#| fig-cap: Estimated toxicokinetic of the EPX concentration in earthworms exposed to 1000 ng/g of EPX. Red points represent the experimental data, the blue curve represent the estimated toxicokinetic curve and the transparent blue band correspond to the credibility interval of the model. 
#| fig-label: fig-EPXdatapredfullC2
#| fig-width: 8
#| fig-height: 20

df_mod_CiEPX_ind_t_plot_C2 <- subset(df_mod_CiEPX_ind_t_C2, ID %in% ID_tri) |> 
  mutate(
    No_rep = paste0("No ", Nb_rep),
    Time_point = as.numeric(gsub("([0-9]+).*", "\\1" , as.character(Time_point_f))),
    Time_point_days = paste0(Time_point_f, " days"),
    Time_point_days = fct_reorder(Time_point_days, as.numeric(Time_point))
  )

df_mod_CeEPX_ind_t_plot_C2 <- subset(df_mod_CeEPX_ind_t_C2, ID %in% ID_tri)
df_mod_Weight_ind_t_plot_C2 <- subset(df_mod_Weight_ind_t_C2, ID %in% ID_tri) |> 
  mutate(
    No_rep = paste0("No ", Nb_rep),
    Time_point = as.numeric(gsub("([0-9]+).*", "\\1" , as.character(Time_point_f))),
    Time_point_days = paste0(Time_point_f, " days"),
    Time_point_days = fct_reorder(Time_point_days, as.numeric(Time_point))
  )

alpha_point <- 0.5
col_exposure <- c(Nord_aurora[2], Nord_aurora[3], Nord_aurora[4])

p_CiEPX_traj <- ggplot()+
  
  geom_segment(
    data = df_phases_plot,
    aes(
      x = t_start,
      xend = t_end,
      y = y,
      yend = y,
      group = ID,
      color = factor(Phase)
    ),
    linewidth = 2,
    alpha = 0.7
  ) +

  geom_line(
    data=df_mod_CiEPX_ind_t_plot_C2,
    aes(
      x=Time,
      y= low,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX_ind_t_plot_C2,
    aes(
      x=Time,
      y= up,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX_ind_t_plot_C2,
    aes(
      x=Time,
      y= predict.endpoint,
      group = ID
      ),
    color = col_EPX,
    lwd=1
    )+
  geom_ribbon(
    data=df_mod_CiEPX_ind_t_plot_C2,
    aes(
      x=Time,
      ymax= up,
      ymin= low,
      group = ID
      ),
    fill = col_EPX,
    alpha=0.1
    )+
  geom_point(
    data = dObs_ind_plot,
    aes(
      x = Time,
      y = CiEPX_obs
    ),
    size = 2,
    alpha = 0.7,
    color = col_red
  )+
  # facet_wrap(
  #   ~ID,
  #   ncol=4,
  #   #scales = "free_x"
  #   )+
  facet_grid(
    vars(Time_point_days), vars(No_rep)#,
    )+
  scale_color_manual(
    values = col_exposure,
    label = c("Uptake", "Elimination", "Depuration"),
    name = "Phase"
    )+
  labs(
    x = "Time (days)",
    y = "CiEPX (ng/g)"
  )+
  #lims(y=c(0, 300))+
  theme_minimal()
  

p_CiEPX_traj 

```

```{r, include=F}

Time_point_1 <- as.character(seq(22, 42, 1))

df_phases_plot_1 <- df_phases_plot |> 
  filter(!(Time_point_f %in% Time_point_1))
df_mod_CiEPX_ind_t_plot_C2_1 <- df_mod_CiEPX_ind_t_plot_C2 |> 
  filter(!(Time_point_f %in% Time_point_1))
dObs_ind_plot_1 <- dObs_ind_plot |> 
  filter(!(Time_point_f %in% Time_point_1))

df_phases_plot_2 <- df_phases_plot |> 
  filter(Time_point_f %in% Time_point_1)
df_mod_CiEPX_ind_t_plot_C2_2 <- df_mod_CiEPX_ind_t_plot_C2 |> 
  filter(Time_point_f %in% Time_point_1)
dObs_ind_plot_2 <- dObs_ind_plot |> 
  filter(Time_point_f %in% Time_point_1)

p_CiEPX_traj_1 <- ggplot()+
  
  geom_segment(
    data = df_phases_plot_1,
    aes(
      x = t_start,
      xend = t_end,
      y = y,
      yend = y,
      group = ID,
      color = factor(Phase)
    ),
    linewidth = 2,
    alpha = 0.7
  ) +

  geom_line(
    data=df_mod_CiEPX_ind_t_plot_C2_1,
    aes(
      x=Time,
      y= low,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX_ind_t_plot_C2_1,
    aes(
      x=Time,
      y= up,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX_ind_t_plot_C2_1,
    aes(
      x=Time,
      y= predict.endpoint,
      group = ID
      ),
    color = col_EPX,
    lwd=1
    )+
  geom_ribbon(
    data=df_mod_CiEPX_ind_t_plot_C2_1,
    aes(
      x=Time,
      ymax= up,
      ymin= low,
      group = ID
      ),
    fill = col_EPX,
    alpha=0.1
    )+
  geom_point(
    data = dObs_ind_plot_1,
    aes(
      x = Time,
      y = CiEPX_obs
    ),
    size = 2,
    alpha = 0.7,
    color = col_red
  )+
  facet_grid(
    vars(Time_point_days), vars(No_rep)#,
    )+
  scale_color_manual(
    values = col_exposure,
    label = c("Uptake", "Elimination", "Depuration"),
    name = "Phase"
    )+
  labs(
    x = "Time (days)",
    y = "CiEPX (ng/g)"
  )+
  theme_minimal()

p_CiEPX_traj_2 <- ggplot()+
  
  geom_segment(
    data = df_phases_plot_2,
    aes(
      x = t_start,
      xend = t_end,
      y = y,
      yend = y,
      group = ID,
      color = factor(Phase)
    ),
    linewidth = 2,
    alpha = 0.7
  ) +

  geom_line(
    data=df_mod_CiEPX_ind_t_plot_C2_2,
    aes(
      x=Time,
      y= low,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX_ind_t_plot_C2_2,
    aes(
      x=Time,
      y= up,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX_ind_t_plot_C2_2,
    aes(
      x=Time,
      y= predict.endpoint,
      group = ID
      ),
    color = col_EPX,
    lwd=1
    )+
  geom_ribbon(
    data=df_mod_CiEPX_ind_t_plot_C2_2,
    aes(
      x=Time,
      ymax= up,
      ymin= low,
      group = ID
      ),
    fill = col_EPX,
    alpha=0.1
    )+
  geom_point(
    data = dObs_ind_plot_2,
    aes(
      x = Time,
      y = CiEPX_obs
    ),
    size = 2,
    alpha = 0.7,
    color = col_red
  )+
  facet_grid(
    vars(Time_point_days), vars(No_rep)#,
    )+
  scale_color_manual(
    values = col_exposure,
    label = c("Uptake", "Elimination", "Depuration"),
    name = "Phase"
    )+
  labs(
    x = "Time (days)",
    y = "CiEPX (ng/g)"
  )+
  theme_minimal()
  
```

## Internal concentrations - Log-scale

```{r, message=F, warning=F}
#| fig-cap: Estimated toxicokinetic of the EPX concentration in earthworms exposed to 1000 ng/g of EPX. Red points represent the experimental data, the blue curve represent the estimated toxicokinetic curve and the transparent blue band correspond to the credibility interval of the model. 
#| fig-label: fig-EPXdatapredfulllogC2
#| fig-width: 8
#| fig-height: 20

p_CiEPX_traj_log <- p_CiEPX_traj + scale_y_log10()

p_CiEPX_traj_log

```

## Weights

```{r EPXpredcurvesdataWC2, message=F, warning=F}
#| fig-cap: Weight predictions
#| fig-label: fig-EPXdatapredfullWC2
#| fig-width: 8
#| fig-height: 20

alpha_point <- 0.5

p_W <- ggplot()+
  geom_line(
    data=df_mod_Weight_ind_t_plot_C2,
    aes(
      x=Time,
      y= low,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_Weight_ind_t_plot_C2,
    aes(
      x=Time,
      y= up,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_Weight_ind_t_plot_C2,
    aes(
      x=Time,
      y= predict.endpoint,
      group = ID
      ),
    color = col_EPX,
    lwd=1
    )+
  geom_ribbon(
    data=df_mod_Weight_ind_t_plot_C2, 
    aes(
      x=Time, 
      ymax= up, 
      ymin= low,
      group = ID
      ),
    fill = col_EPX,
    alpha=0.1
    )+
  geom_point(
    data = dObs_ind_plot,
    aes(
      x = Time,
      y = Weight_obs
    ),
    size = 2,
    alpha = 0.7,
    color = col_red
  )+
  # facet_wrap(
  #   ~ID,
  #   ncol = 4,
  #   scales = "free"
  #   )+
  facet_grid(
    vars(Time_point_days), vars(No_rep)#,
    )+
  #lims(y=c(0, 1500))+
  labs(
    x = "Time (days)",
    y = "Weight (g)"
  )+
  theme_minimal()

p_W

```

```{r savetrajC2, include = F}
ggsave(
  filename="TK_EPX_comptrajpred.png", 
  plot=p_CiEPX_traj , 
  width=8, height = 20, 
  path=path_fig_C2
  )
ggsave(
  filename="TK_EPX_comptrajpred.svg", 
  plot=p_CiEPX_traj , 
  width=8, height = 20, 
  path=path_fig_C2
  )
ggsave(
  filename="TK_EPX_comptrajpred_log.png", 
  plot=p_CiEPX_traj_log , 
  width=8, height = 20, 
  path=path_fig_C2
  )
ggsave(
  filename="TK_EPX_comptrajpred_log.svg", 
  plot=p_CiEPX_traj_log , 
  width=8, height = 20, 
  path=path_fig_C2
  )
ggsave(
  filename="TK_EPX_comptrajpredW.png", 
  plot=p_W , 
  width=8, height = 20, 
  path=path_fig_C2
  )
ggsave(
  filename="TK_EPX_comptrajpredW.svg", 
  plot=p_W , 
  width=8, height = 20, 
  path=path_fig_C2
  )

ggsave(
  filename="TK_EPX_comptrajpred_1.png", 
  plot=p_CiEPX_traj_1, 
  width=8, height = 10, 
  path=path_fig_C2
  )

ggsave(
  filename="TK_EPX_comptrajpred_2.png", 
  plot=p_CiEPX_traj_2 , 
  width=8, height = 10, 
  path=path_fig_C2
  )
```
:::

## C2P

::: panel-tabset
## Internal concentrations - Normal scale

```{r EPXpredcurvesdataC2P, message=F, warning=F}
#| fig-cap: Estimated toxicokinetic of the EPX concentration in earthworms exposed to 1000 ng/g of EPX. Red points represent the experimental data, the blue curve represent the estimated toxicokinetic curve and the transparent blue band correspond to the credibility interval of the model. 
#| fig-label: fig-EPXdatapredfullC2P
#| fig-width: 8
#| fig-height: 20

df_mod_CiEPX_ind_t_plot_C2P <- subset(df_mod_CiEPX_ind_t_C2P, ID %in% ID_tri) |> 
  mutate(
    No_rep = paste0("No ", Nb_rep),
    Time_point = as.numeric(gsub("([0-9]+).*", "\\1" , as.character(Time_point_f))),
    Time_point_days = paste0(Time_point_f, " days"),
    Time_point_days = fct_reorder(Time_point_days, as.numeric(Time_point))
  )

df_mod_CeEPX_ind_t_plot_C2P <- subset(df_mod_CeEPX_ind_t_C2P, ID %in% ID_tri)
df_mod_Weight_ind_t_plot_C2P <- subset(df_mod_Weight_ind_t_C2P, ID %in% ID_tri) |> 
  mutate(
    No_rep = paste0("No ", Nb_rep),
    Time_point = as.numeric(gsub("([0-9]+).*", "\\1" , as.character(Time_point_f))),
    Time_point_days = paste0(Time_point_f, " days"),
    Time_point_days = fct_reorder(Time_point_days, as.numeric(Time_point))
  )

alpha_point <- 0.5
col_exposure <- c(Nord_aurora[2], Nord_aurora[3], Nord_aurora[4])

p_CiEPX_traj <- ggplot()+
  
  geom_segment(
    data = df_phases_plot,
    aes(
      x = t_start,
      xend = t_end,
      y = y,
      yend = y,
      group = ID,
      color = factor(Phase)
    ),
    linewidth = 2,
    alpha = 0.7
  ) +

  geom_line(
    data=df_mod_CiEPX_ind_t_plot_C2P,
    aes(
      x=Time,
      y= low,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX_ind_t_plot_C2P,
    aes(
      x=Time,
      y= up,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX_ind_t_plot_C2P,
    aes(
      x=Time,
      y= predict.endpoint,
      group = ID
      ),
    color = col_EPX,
    lwd=1
    )+
  geom_ribbon(
    data=df_mod_CiEPX_ind_t_plot_C2P,
    aes(
      x=Time,
      ymax= up,
      ymin= low,
      group = ID
      ),
    fill = col_EPX,
    alpha=0.1
    )+
  geom_point(
    data = dObs_ind_plot,
    aes(
      x = Time,
      y = CiEPX_obs
    ),
    size = 2,
    alpha = 0.7,
    color = col_red
  )+
  # facet_wrap(
  #   ~ID,
  #   ncol=4,
  #   #scales = "free_x"
  #   )+
  facet_grid(
    vars(Time_point_days), vars(No_rep)#,
    )+
  scale_color_manual(
    values = col_exposure,
    label = c("Uptake", "Elimination", "Depuration"),
    name = "Phase"
    )+
  labs(
    x = "Time (days)",
    y = "CiEPX (ng/g)"
  )+
  #lims(y=c(0, 300))+
  theme_minimal()
  

p_CiEPX_traj 

```

```{r, include=F}

Time_point_1 <- as.character(seq(22, 42, 1))

df_phases_plot_1 <- df_phases_plot |> 
  filter(!(Time_point_f %in% Time_point_1))
df_mod_CiEPX_ind_t_plot_C2P_1 <- df_mod_CiEPX_ind_t_plot_C2P |> 
  filter(!(Time_point_f %in% Time_point_1))
dObs_ind_plot_1 <- dObs_ind_plot |> 
  filter(!(Time_point_f %in% Time_point_1))

df_phases_plot_2 <- df_phases_plot |> 
  filter(Time_point_f %in% Time_point_1)
df_mod_CiEPX_ind_t_plot_C2P_2 <- df_mod_CiEPX_ind_t_plot_C2P |> 
  filter(Time_point_f %in% Time_point_1)
dObs_ind_plot_2 <- dObs_ind_plot |> 
  filter(Time_point_f %in% Time_point_1)

p_CiEPX_traj_1 <- ggplot()+
  
  geom_segment(
    data = df_phases_plot_1,
    aes(
      x = t_start,
      xend = t_end,
      y = y,
      yend = y,
      group = ID,
      color = factor(Phase)
    ),
    linewidth = 2,
    alpha = 0.7
  ) +

  geom_line(
    data=df_mod_CiEPX_ind_t_plot_C2P_1,
    aes(
      x=Time,
      y= low,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX_ind_t_plot_C2P_1,
    aes(
      x=Time,
      y= up,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX_ind_t_plot_C2P_1,
    aes(
      x=Time,
      y= predict.endpoint,
      group = ID
      ),
    color = col_EPX,
    lwd=1
    )+
  geom_ribbon(
    data=df_mod_CiEPX_ind_t_plot_C2P_1,
    aes(
      x=Time,
      ymax= up,
      ymin= low,
      group = ID
      ),
    fill = col_EPX,
    alpha=0.1
    )+
  geom_point(
    data = dObs_ind_plot_1,
    aes(
      x = Time,
      y = CiEPX_obs
    ),
    size = 2,
    alpha = 0.7,
    color = col_red
  )+
  facet_grid(
    vars(Time_point_days), vars(No_rep)#,
    )+
  scale_color_manual(
    values = col_exposure,
    label = c("Uptake", "Elimination", "Depuration"),
    name = "Phase"
    )+
  labs(
    x = "Time (days)",
    y = "CiEPX (ng/g)"
  )+
  theme_minimal()

p_CiEPX_traj_2 <- ggplot()+
  
  geom_segment(
    data = df_phases_plot_2,
    aes(
      x = t_start,
      xend = t_end,
      y = y,
      yend = y,
      group = ID,
      color = factor(Phase)
    ),
    linewidth = 2,
    alpha = 0.7
  ) +

  geom_line(
    data=df_mod_CiEPX_ind_t_plot_C2P_2,
    aes(
      x=Time,
      y= low,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX_ind_t_plot_C2P_2,
    aes(
      x=Time,
      y= up,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX_ind_t_plot_C2P_2,
    aes(
      x=Time,
      y= predict.endpoint,
      group = ID
      ),
    color = col_EPX,
    lwd=1
    )+
  geom_ribbon(
    data=df_mod_CiEPX_ind_t_plot_C2P_2,
    aes(
      x=Time,
      ymax= up,
      ymin= low,
      group = ID
      ),
    fill = col_EPX,
    alpha=0.1
    )+
  geom_point(
    data = dObs_ind_plot_2,
    aes(
      x = Time,
      y = CiEPX_obs
    ),
    size = 2,
    alpha = 0.7,
    color = col_red
  )+
  facet_grid(
    vars(Time_point_days), vars(No_rep)#,
    )+
  scale_color_manual(
    values = col_exposure,
    label = c("Uptake", "Elimination", "Depuration"),
    name = "Phase"
    )+
  labs(
    x = "Time (days)",
    y = "CiEPX (ng/g)"
  )+
  theme_minimal()
  
```

## Internal concentrations - Log-scale

```{r, message=F, warning=F}
#| fig-cap: Estimated toxicokinetic of the EPX concentration in earthworms exposed to 1000 ng/g of EPX. Red points represent the experimental data, the blue curve represent the estimated toxicokinetic curve and the transparent blue band correspond to the credibility interval of the model. 
#| fig-label: fig-EPXdatapredfulllogC2P
#| fig-width: 8
#| fig-height: 20

p_CiEPX_traj_log <- p_CiEPX_traj + scale_y_log10()

p_CiEPX_traj_log

```

## Weights

```{r EPXpredcurvesdataWC2P, message=F, warning=F}
#| fig-cap: Weight predictions
#| fig-label: fig-EPXdatapredfullWC2P
#| fig-width: 8
#| fig-height: 20

alpha_point <- 0.5

p_W <- ggplot()+
  geom_line(
    data=df_mod_Weight_ind_t_plot_C2P,
    aes(
      x=Time,
      y= low,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_Weight_ind_t_plot_C2P,
    aes(
      x=Time,
      y= up,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_Weight_ind_t_plot_C2P,
    aes(
      x=Time,
      y= predict.endpoint,
      group = ID
      ),
    color = col_EPX,
    lwd=1
    )+
  geom_ribbon(
    data=df_mod_Weight_ind_t_plot_C2P, 
    aes(
      x=Time, 
      ymax= up, 
      ymin= low,
      group = ID
      ),
    fill = col_EPX,
    alpha=0.1
    )+
  geom_point(
    data = dObs_ind_plot,
    aes(
      x = Time,
      y = Weight_obs
    ),
    size = 2,
    alpha = 0.7,
    color = col_red
  )+
  # facet_wrap(
  #   ~ID,
  #   ncol = 4,
  #   scales = "free"
  #   )+
  facet_grid(
    vars(Time_point_days), vars(No_rep)#,
    )+
  #lims(y=c(0, 1500))+
  labs(
    x = "Time (days)",
    y = "Weight (g)"
  )+
  theme_minimal()

p_W

```

```{r savetrajC2P, include = F}
ggsave(
  filename="TK_EPX_comptrajpred.png", 
  plot=p_CiEPX_traj , 
  width=8, height = 20, 
  path=path_fig_C2P
  )
ggsave(
  filename="TK_EPX_comptrajpred.svg", 
  plot=p_CiEPX_traj , 
  width=8, height = 20, 
  path=path_fig_C2P
  )
ggsave(
  filename="TK_EPX_comptrajpred_log.png", 
  plot=p_CiEPX_traj_log , 
  width=8, height = 20, 
  path=path_fig_C2P
  )
ggsave(
  filename="TK_EPX_comptrajpred_log.svg", 
  plot=p_CiEPX_traj_log , 
  width=8, height = 20, 
  path=path_fig_C2P
  )
ggsave(
  filename="TK_EPX_comptrajpredW.png", 
  plot=p_W , 
  width=8, height = 20, 
  path=path_fig_C2P
  )
ggsave(
  filename="TK_EPX_comptrajpredW.svg", 
  plot=p_W , 
  width=8, height = 20, 
  path=path_fig_C2P
  )

ggsave(
  filename="TK_EPX_comptrajpred_1.png", 
  plot=p_CiEPX_traj_1, 
  width=8, height = 10, 
  path=path_fig_C2P
  )

ggsave(
  filename="TK_EPX_comptrajpred_2.png", 
  plot=p_CiEPX_traj_2 , 
  width=8, height = 10, 
  path=path_fig_C2P
  )
```
:::
:::::::

### Simulation of the toxicodynamic in earthworms throughout the exposition

The goal here is to recreate the concentration dynamic in the average earthworm during our exposition scheme but without the fasting phase that was required for chemical analysis and during which elimination was happening.

```{r setpointin, message=F, warning=F}

Time_min <- 0
Time_max <- 42
Time_step <- 0.25
Time_pred <- seq(Time_min, Time_max, Time_step)
print_times <- paste(Time_min, Time_max, Time_step, sep=", ")

######## C1 ###################################
l_param_name_tot_C1 <- "kuEPX, keEPX, a_growth, Vr_a_growth, Sigma_W, Sigma_CiEPX"
f_Setpoint(path_mod_EPX_C1, Molecule, print_times, l_param_name_tot_C1)

######## C1P ###################################
l_param_name_tot_C1P <- "kuEPX, keEPX, phi, a_growth, Vr_a_growth, Sigma_W, Sigma_CiEPX"
f_Setpoint(path_mod_EPX_C1P, Molecule, print_times, l_param_name_tot_C1P)

######## C2 ###################################
l_param_name_tot_C2 <- "kuEPX, keEPX, kperiph, a_growth, Vr_a_growth, Sigma_W, Sigma_CiEPX"
f_Setpoint(path_mod_EPX_C2, Molecule, print_times, l_param_name_tot_C2)

######## C2P ###################################
l_param_name_tot_C2P <- "kuEPX, keEPX, kperiph, phi, a_growth, Vr_a_growth, Sigma_W, Sigma_CiEPX"
f_Setpoint(path_mod_EPX_C2P, Molecule, print_times, l_param_name_tot_C2P)

```

```{bash, results=F, eval=F}
pwd
cd ..
cd ..
cd mod/TK_EPX
pwd
./mcsim.m_TK_EPX TK_EPX_Setpoint.in
wait
```

```{r EPXreadSetpoint, message=F, warning=F}

############ C1 ###########################################
Sim.Res_C1 <- as.data.frame(fread(here::here(path_mod_EPX_C1, "Setpoints.out"),sep="\t"))
  
  Nom_Endpoints =c("Weight_1", "CiEPX_1", "C_exposure_1")
  Nsortie = 3
  MPV = IC_min = IC_max = Endpoint = index = NULL

  for (i in 1:length(Nom_Endpoints)){
    
    index =grep(paste("^",Nom_Endpoints[i],"\\.", sep="") , colnames(Sim.Res_C1), fixed=FALSE )
    
    Data_sim = as.matrix( Sim.Res_C1[ , index] )
    
    MPV    = c(  MPV,  as.numeric( Data_sim[nrow(Data_sim), ] ) )
    IC_min = c(IC_min,  apply(Data_sim, 2, quantile,  0.025) )
    IC_max = c(IC_max,  apply(Data_sim, 2, quantile,  0.975) ) 
    
    Endpoint = c(Endpoint, rep(Nom_Endpoints[i], ncol(Data_sim)))

    }

  df_mod_C1 <- data.frame(
    predict.endpoint = MPV,
    Time    = c( rep(Time_pred, Nsortie)),
    low     = IC_min,
    up      = IC_max,
    Endpt   = Endpoint,
    Experiment = c(rep(rep("Experience 1", length(Time_pred)), Nsortie))
    )
  
df_mod_Weight_C1 <- subset(df_mod_C1, Endpt == "Weight_1")
df_mod_CiEPX_C1 <- subset(df_mod_C1, Endpt == "CiEPX_1") 

############ C1P ###########################################
Sim.Res_C1P <- as.data.frame(fread(here::here(path_mod_EPX_C1P, "Setpoints.out"),sep="\t"))
  
  Nom_Endpoints =c("Weight_1", "CiEPX_1", "C_exposure_1")
  Nsortie = 3
  MPV = IC_min = IC_max = Endpoint = index = NULL

  for (i in 1:length(Nom_Endpoints)){
    
    index =grep(paste("^",Nom_Endpoints[i],"\\.", sep="") , colnames(Sim.Res_C1P), fixed=FALSE )
    
    Data_sim = as.matrix( Sim.Res_C1P[ , index] )
    
    MPV    = c(  MPV,  as.numeric( Data_sim[nrow(Data_sim), ] ) )
    IC_min = c(IC_min,  apply(Data_sim, 2, quantile,  0.025) )
    IC_max = c(IC_max,  apply(Data_sim, 2, quantile,  0.975) ) 
    
    Endpoint = c(Endpoint, rep(Nom_Endpoints[i], ncol(Data_sim)))

    }

  df_mod_C1P <- data.frame(
    predict.endpoint = MPV,
    Time    = c( rep(Time_pred, Nsortie)),
    low     = IC_min,
    up      = IC_max,
    Endpt   = Endpoint,
    Experiment = c(rep(rep("Experience 1", length(Time_pred)), Nsortie))
    )
  
df_mod_Weight_C1P <- subset(df_mod_C1P, Endpt == "Weight_1")
df_mod_CiEPX_C1P <- subset(df_mod_C1P, Endpt == "CiEPX_1")

############ C2 ###########################################
Sim.Res_C2 <- as.data.frame(fread(here::here(path_mod_EPX_C2, "Setpoints.out"),sep="\t"))
  
  Nom_Endpoints =c("Weight_1", "CiEPX_1", "C_exposure_1")
  Nsortie = 3
  MPV = IC_min = IC_max = Endpoint = index = NULL

  for (i in 1:length(Nom_Endpoints)){
    
    index =grep(paste("^",Nom_Endpoints[i],"\\.", sep="") , colnames(Sim.Res_C2), fixed=FALSE )
    
    Data_sim = as.matrix( Sim.Res_C2[ , index] )
    
    MPV    = c(  MPV,  as.numeric( Data_sim[nrow(Data_sim), ] ) )
    IC_min = c(IC_min,  apply(Data_sim, 2, quantile,  0.025) )
    IC_max = c(IC_max,  apply(Data_sim, 2, quantile,  0.975) ) 
    
    Endpoint = c(Endpoint, rep(Nom_Endpoints[i], ncol(Data_sim)))

    }

  df_mod_C2 <- data.frame(
    predict.endpoint = MPV,
    Time    = c( rep(Time_pred, Nsortie)),
    low     = IC_min,
    up      = IC_max,
    Endpt   = Endpoint,
    Experiment = c(rep(rep("Experience 1", length(Time_pred)), Nsortie))
    )
  
df_mod_Weight_C2 <- subset(df_mod_C2, Endpt == "Weight_1")
df_mod_CiEPX_C2 <- subset(df_mod_C2, Endpt == "CiEPX_1") 

############ C2P ###########################################
Sim.Res_C2P <- as.data.frame(fread(here::here(path_mod_EPX_C2P, "Setpoints.out"),sep="\t"))
  
  Nom_Endpoints =c("Weight_1", "CiEPX_1", "C_exposure_1")
  Nsortie = 3
  MPV = IC_min = IC_max = Endpoint = index = NULL

  for (i in 1:length(Nom_Endpoints)){
    
    index =grep(paste("^",Nom_Endpoints[i],"\\.", sep="") , colnames(Sim.Res_C2P), fixed=FALSE )
    
    Data_sim = as.matrix( Sim.Res_C2P[ , index] )
    
    MPV    = c(  MPV,  as.numeric( Data_sim[nrow(Data_sim), ] ) )
    IC_min = c(IC_min,  apply(Data_sim, 2, quantile,  0.025) )
    IC_max = c(IC_max,  apply(Data_sim, 2, quantile,  0.975) ) 
    
    Endpoint = c(Endpoint, rep(Nom_Endpoints[i], ncol(Data_sim)))

    }

  df_mod_C2P <- data.frame(
    predict.endpoint = MPV,
    Time    = c( rep(Time_pred, Nsortie)),
    low     = IC_min,
    up      = IC_max,
    Endpt   = Endpoint,
    Experiment = c(rep(rep("Experience 1", length(Time_pred)), Nsortie))
    )
  
df_mod_Weight_C2P <- subset(df_mod_C2P, Endpt == "Weight_1")
df_mod_CiEPX_C2P <- subset(df_mod_C2P, Endpt == "CiEPX_1")
  
```

::: panel-tabset
## C1

```{r EPXpredcurvesC1, message=F, warning=F}
#| fig-cap: Estimated toxicokinetic of the EPX concentration in earthworms exposed to 0.1 mg/kg of EPX. Blue points represent the experimental data, the blue curve represents the estimated toxicokinetic curve and the transparent blue band corresponds to the credibility interval of the model. 
#| fig-label: fig-EPXcurvemodC1
#| fig-width: 8
#| fig-height: 4

alpha_point <- 0.5

p_CiEPX <- ggplot()+
  geom_line(
    data=df_mod_CiEPX_C1,
    aes(
      x=Time,
      y= low
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX_C1,
    aes(
      x=Time,
      y= up
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX_C1,
    aes(
      x=Time,
      y= predict.endpoint
      ),
    color = col_EPX,
    lwd=1
    )+
  geom_ribbon(
    data=df_mod_CiEPX_C1, 
    aes(
      x=Time, 
      ymax= up, 
      ymin= low
      ),
    fill = col_EPX,
    alpha=0.1
    )+
  labs(
    x = "Time (days)",
    y = "Internal EPX concentration (ng/g)"
  )+
  theme_minimal()

p <- p_CiEPX 
p

```

```{r savepredcurvesC1, include = F}
  ggsave(
    filename="TK_EPX_predcurves.png", 
    plot=p, 
    width=8, height = 4, 
    path=path_fig_C1
    )
  ggsave(
    filename="TK_EPX_predcurves.svg", 
    plot=p, 
    width=8, height = 4, 
    path=path_fig_C1
    )
```

## C1P

```{r EPXpredcurvesC1P, message=F, warning=F}
#| fig-cap: Estimated toxicokinetic of the EPX concentration in earthworms exposed to 0.1 mg/kg of EPX. Blue points represent the experimental data, the blue curve represents the estimated toxicokinetic curve and the transparent blue band corresponds to the credibility interval of the model. 
#| fig-label: fig-EPXcurvemodC1P
#| fig-width: 8
#| fig-height: 4

alpha_point <- 0.5

p_CiEPX <- ggplot()+
  geom_line(
    data=df_mod_CiEPX_C1P,
    aes(
      x=Time,
      y= low
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX_C1P,
    aes(
      x=Time,
      y= up
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX_C1P,
    aes(
      x=Time,
      y= predict.endpoint
      ),
    color = col_EPX,
    lwd=1
    )+
  geom_ribbon(
    data=df_mod_CiEPX_C1P, 
    aes(
      x=Time, 
      ymax= up, 
      ymin= low
      ),
    fill = col_EPX,
    alpha=0.1
    )+
  labs(
    x = "Time (days)",
    y = "Internal EPX concentration (ng/g)"
  )+
  theme_minimal()

p <- p_CiEPX 
p

```

```{r savepredcurvesC1P, include = F}
  ggsave(
    filename="TK_EPX_predcurves.png", 
    plot=p, 
    width=8, height = 4, 
    path=path_fig_C1P
    )
  ggsave(
    filename="TK_EPX_predcurves.svg", 
    plot=p, 
    width=8, height = 4, 
    path=path_fig_C1P
    )
```

## C2

```{r EPXpredcurvesC2, message=F, warning=F}
#| fig-cap: Estimated toxicokinetic of the EPX concentration in earthworms exposed to 0.1 mg/kg of EPX. Blue points represent the experimental data, the blue curve represents the estimated toxicokinetic curve and the transparent blue band corresponds to the credibility interval of the model. 
#| fig-label: fig-EPXcurvemodC2
#| fig-width: 8
#| fig-height: 4

alpha_point <- 0.5

p_CiEPX <- ggplot()+
  geom_line(
    data=df_mod_CiEPX_C2,
    aes(
      x=Time,
      y= low
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX_C2,
    aes(
      x=Time,
      y= up
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX_C2,
    aes(
      x=Time,
      y= predict.endpoint
      ),
    color = col_EPX,
    lwd=1
    )+
  geom_ribbon(
    data=df_mod_CiEPX_C2, 
    aes(
      x=Time, 
      ymax= up, 
      ymin= low
      ),
    fill = col_EPX,
    alpha=0.1
    )+
  labs(
    x = "Time (days)",
    y = "Internal EPX concentration (ng/g)"
  )+
  theme_minimal()

p <- p_CiEPX 
p

```

```{r savepredcurvesC2, include = F}
  ggsave(
    filename="TK_EPX_predcurves.png", 
    plot=p, 
    width=8, height = 4, 
    path=path_fig_C2
    )
  ggsave(
    filename="TK_EPX_predcurves.svg", 
    plot=p, 
    width=8, height = 4, 
    path=path_fig_C2
    )
```

## C2P

```{r EPXpredcurvesC2P, message=F, warning=F}
#| fig-cap: Estimated toxicokinetic of the EPX concentration in earthworms exposed to 0.1 mg/kg of EPX. Blue points represent the experimental data, the blue curve represents the estimated toxicokinetic curve and the transparent blue band corresponds to the credibility interval of the model. 
#| fig-label: fig-EPXcurvemodC2P
#| fig-width: 8
#| fig-height: 4

alpha_point <- 0.5

p_CiEPX <- ggplot()+
  geom_line(
    data=df_mod_CiEPX_C2P,
    aes(
      x=Time,
      y= low
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX_C2P,
    aes(
      x=Time,
      y= up
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX_C2P,
    aes(
      x=Time,
      y= predict.endpoint
      ),
    color = col_EPX,
    lwd=1
    )+
  geom_ribbon(
    data=df_mod_CiEPX_C2P, 
    aes(
      x=Time, 
      ymax= up, 
      ymin= low
      ),
    fill = col_EPX,
    alpha=0.1
    )+
  labs(
    x = "Time (days)",
    y = "Internal EPX concentration (ng/g)"
  )+
  theme_minimal()

p <- p_CiEPX 
p

```

```{r savepredcurvesC2P, include = F}
  ggsave(
    filename="TK_EPX_predcurves.png", 
    plot=p, 
    width=8, height = 4, 
    path=path_fig_C2P
    )
  ggsave(
    filename="TK_EPX_predcurves.svg", 
    plot=p, 
    width=8, height = 4, 
    path=path_fig_C2P
    )
```
:::
