```{r lib, include=F}
#| cache: False

library(here)
source(file = here::here("functions/fun.R"))

f_load_libraries_colors()
col_Molecule <- rev(col_Molecule)
path_fig <- here::here("fig/TK_mix")
#pal_Ratio <- c(Nord_frost[4], Nord_aurora[5], Nord_aurora[1:4])
pal_Ratio <- c(col_EPX, Nord_aurora[3], Nord_aurora[1],  Nord_aurora[4], col_IMD, Nord_aurora[4] )
```

# Is there an interaction between IMD & EPX at the TK level ?

We want to answer the following question : Can we predict the concentrations in EPX and IMD in earthworms exposed to different ratios of the mixture ?

## Data importation

```{r data, warning=F, message=F}
df_TK_mix <- f_read_data_TK_mix() |>
  mutate(
    Ratio_plot = case_when(
      Ratio == "E" ~ "1:0 (EPX only)",
      Ratio == "F" ~ "3:1",
      Ratio == "G" ~ "1:1",
      Ratio == "H" ~ "1:3",
      Ratio == "I" ~ "0:1 (IMD only)",
      Ratio == "N" ~ "Ctrl"
    ),
    Ratio_plot = factor(Ratio_plot, levels = Ratio_plot[!duplicated(Ratio)])
  )

Ci0IMD <- mean(subset(df_TK_mix, Ratio == "E")$CiIMD, na.rm = T)
Ci0EPX <- mean(subset(df_TK_mix, Ratio == "I")$CiEPX, na.rm = T)

df_TK_mix_mean_Ce <- subset(df_TK_mix, t = 0) |>
  group_by(Ratio, Line) |>
  mutate(
    CeIMD = mean(CeIMD, na.rm = T),
    CeEPX = mean(CeEPX, na.rm = T)
  ) |> 
  dplyr::select(CeIMD, CeEPX) |> 
  unique()

df_TK_mix_mean <- subset(df_TK_mix, t > 28) |>
  dplyr::select(-c(CeIMD, CeEPX)) |> 
  group_by(Ratio, Line) |>
  mutate(
    Dose_IMD = mean(Dose_IMD, na.rm = T),
    Dose_EPX = mean(Dose_EPX, na.rm = T)
  ) |> 
  ungroup() |> 
  left_join(df_TK_mix_mean_Ce, by = c("Ratio", "Line")) |> 
  group_by(Ratio, Line) |>
  mutate(
    BAFIMD_obs = mean(CiIMD / CeIMD, na.rm = T),
    BAFEPX_obs = mean(CiEPX / CeEPX, na.rm = T)
  ) |> 
  ungroup() 
```

```{r, warning=F, message=F}
#| fig-cap: Results
#| label: fig-DataRes
#| fig-height: 6
#| fig-width: 8

pIMD <- ggplot(
  data = subset(df_TK_mix, t > 0 & Line %in% c(2,5)),
  aes(
    x = Ratio,
    y = CiIMD
  )
) +
  geom_dotplot(
    aes(
      color = Ratio,
      fill = Ratio
    ),
    binaxis = "y",
    stackdir = "center",
    dotsize = 1,
    alpha = 0.7
  ) +
  facet_wrap(~Line, scales = "free")+
  scale_color_manual(values = pal_Ratio) +
  scale_fill_manual(values = pal_Ratio) +
  theme_minimal()

pEPX <- ggplot(
  data = subset(df_TK_mix, t > 0 & Line %in% c(2,5)),
  aes(
    x = Ratio,
    y = CiEPX
  )
) +
  geom_dotplot(
    aes(
      color = Ratio,
      fill = Ratio
    ),
    binaxis = "y",
    stackdir = "center",
    dotsize = 1,
    alpha = 0.7
  ) +
  facet_wrap(~Line, scales = "free")+
  scale_color_manual(values = pal_Ratio) +
  scale_fill_manual(values = pal_Ratio) +
  theme_minimal()

pIMDe <- ggplot(
  data = subset(df_TK_mix_mean, (No_vdt == 1 & Nb_rep == 1 & Line %in% c(2,5))),
  aes(
    x = Ratio,
    y = CeIMD
  )
) +
  geom_col(
    aes(
      color = Ratio,
      fill = Ratio
    ),
    alpha = 0.7
  ) +
  # geom_text(
  #   aes(
  #     label = signif(BAFIMD_obs, 3),
  #     color = Ratio,
  #     y = max(Dose_IMD) * 1.02
  #   ),
  #   vjust = 0,
  #   size = 3
  # ) +
  facet_wrap(~Line, scales = "free")+
  scale_color_manual(values = pal_Ratio) +
  scale_fill_manual(values = pal_Ratio) +
  theme_minimal()

pEPXe <- ggplot(
  data = subset(df_TK_mix_mean, (No_vdt == 1 & Nb_rep == 1 & Line %in% c(2,5))),
  aes(
    x = Ratio,
    y = CeEPX
  )
) +
  geom_col(
    aes(
      color = Ratio,
      fill = Ratio
    ),
    alpha = 0.7
  ) +
  # geom_text(
  #   aes(
  #     label = signif(BAFEPX_obs, 3),
  #     color = Ratio,
  #     y = max(Dose_EPX) * 1.02
  #   ),
  #   vjust = 0,
  #   size = 3
  # ) +
  facet_wrap(~Line, scales = "free")+
  scale_color_manual(values = pal_Ratio) +
  scale_fill_manual(values = pal_Ratio) +
  theme_minimal()

p <- (pIMD + pEPX) / (pIMDe + pEPXe)
p

p_IMD_tot <- pIMD/pIMDe
p_EPX_tot <- pEPX/pEPXe
```

```{r, include = F}
ggsave(
  filename="TK_MIX_IMD_raw.png", 
  plot=p_IMD_tot, 
  width=8, height = 5, 
  path=path_fig
  )
ggsave(
  filename="TK_MIX_EPX_raw.png", 
  plot=p_EPX_tot, 
  width=8, height = 5, 
  path=path_fig
  )
```

```{r}
#| fig-cap: Results
#| label: fig-DataRes2
#| fig-height: 4
#| fig-width: 8

pIMD <- ggplot() +
  geom_point(
    data = df_TK_mix_mean,
    aes(
      x = CeIMD,
      y = CiIMD,
      color = Ratio
    )
  ) +
  labs(
    x = "Concentration d'IMD dans le sol (ng/g)",
    y = "Concentration d'IMD dans le ver (ng/g)"
  ) +
  scale_color_manual(values = pal_Ratio) +
  theme_minimal()

pEPX <- ggplot() +
  geom_point(
    data = df_TK_mix_mean,
    aes(
      x = CeEPX,
      y = CiEPX,
      color = Ratio
    )
  ) +
  labs(
    x = "Concentration d'EPX dans le sol (ng/g)",
    y = "Concentration d'EPX dans le ver (ng/g)"
  ) +
  scale_color_manual(values = pal_Ratio) +
  theme_minimal()


p <- pIMD + pEPX +
  plot_layout(ncol = 2, guides = "collect")
p
```

```{r}
#| fig-cap: Results
#| label: fig-DataRes3
#| fig-height: 4
#| fig-width: 8

pIMD <- ggplot() +
  geom_point(
    data = df_TK_mix_mean,
    aes(
      x = Dose_IMD,
      y = CiIMD / CeIMD,
      color = Ratio
    )
  ) +
  labs(
    x = "Concentration d'IMD dans le sol (ng/g)",
    y = "Ratio des oncentrations d'IMD dans le sol et le ver (ng/g)"
  ) +
  scale_y_log10()+
  scale_color_manual(values = pal_Ratio) +
  theme_minimal()

pEPX <- ggplot() +
  geom_point(
    data = df_TK_mix_mean,
    aes(
      x = Dose_EPX,
      y = CiEPX / CeEPX,
      color = Ratio
    )
  ) +
  labs(
    x = "Concentration d'EPX dans le sol (ng/g)",
    y = "Ratio des concentrations d'EPX dans le sol et le ver (ng/g)"
  ) +
  scale_y_log10()+
  scale_color_manual(values = pal_Ratio) +
  theme_minimal()


p <- pIMD + pEPX +
  plot_layout(ncol = 2, guides = "collect")
p
```

## Quantity in earthworms vs. quantity in the cosm

```{r}
df_TK_mix_Qtity <- df_TK_mix_mean |> 
  mutate(
    Q_EPX_ew = CiEPX * Weight, # ng/g x g
    Q_IMD_ew = CiIMD * Weight,
    Q_EPX_cosm = CeEPX * 200, # ng/g x 200
    Q_IMD_cosm = CeIMD * 200,
    R_Q_EPX_ew_cosm = Q_EPX_ew / Q_EPX_cosm * 100,
    R_Q_IMD_ew_cosm = Q_IMD_ew / Q_IMD_cosm * 100
  )

p <- ggplot(
  data = df_TK_mix_Qtity,
  aes(
    x = paste0(Ratio, Line)
  )
)+
  geom_point(
    mapping = aes(
      y = R_Q_EPX_ew_cosm
    ),
    color = col_EPX,
    alpha = 0.5,
    size = 3
  )+
  geom_point(
    mapping = aes(
      y = R_Q_IMD_ew_cosm
    ),
    color = col_IMD,
    alpha = 0.5,
    size = 3
  )+
  scale_y_log10()+
  labs(
    x = "Condition",
    y = "Quantité de substance dans un ver\nen % de la quantité dans un cosme"
  )+
  theme_minimal(14)
p

```

## Simulations for IMD

```{r increationIMD}
path_mod_mix <- here::here("mod/TK_Mix_IMD")
Nb_experiement <- length(unique(df_TK_mix$ID))
Molecule <- "IMD"
N_draws <- 1000
l_param_name <- "kuIMD, keIMD, kperiph"

f_Simulation_mix_ind(path_mod_mix, Molecule, l_param_name)

```

```{bash, results=F, eval=F}
pwd
cd ..
cd ..
cd mod/TK_Mix_IMD
pwd

for j in $(seq 1 43); do
  ./mcsim.m_TK_IMD "Simulation_ind_IMD_${j}.in" "Simulation_ind_IMD_${j}.out"
done

```

### Predicted vs. Observed

```{r EPXdatapred, message=F, warning=F}

Nb_experiment_IMD <- 43

dObs_ind <- df_TK_mix |>
  mutate(
    ID = as.numeric(ID)
  )

colnames(dObs_ind)[colnames(dObs_ind) == "Weight"] <- "Weight_obs"
colnames(dObs_ind)[colnames(dObs_ind) == "CiIMD"] <- "CiIMD_obs"
colnames(dObs_ind)[colnames(dObs_ind) == "t"] <- "Time"

#col_exposure <- c(Nord_aurora[4], Nord_aurora[1], Nord_frost[2])

IDs <- unique(df_TK_mix$ID)

Sim.Res.ind <- lapply(1:43, function(j) {
  read_tsv(file.path(path_mod_mix, paste0("Simulation_ind_IMD_", j, ".out"))) %>%
    mutate(
      sim = j,
      ID = as.numeric(IDs[j])
    )
}) %>%
  bind_rows()


df_mod_ind_IMD <- NULL

for (i in 1:Nb_experiment_IMD){
  
  ID_i <- unique(dObs_ind$ID)[i]

  Sim.Res.ind_i  <- subset(Sim.Res.ind, sim == i) |> 
    dplyr::select(where(~ !all(is.na(.x))))
  
  dObs_i <- subset(dObs_ind, ID == ID_i)
  
  Time_pred = dObs_i$Time # !!!
  
  Nom_Endpoints = c("Weight", "CiIMD")
  
  Nsortie = 2
  
  MPV = IC_min = IC_max = Endpoint = index = NULL
  
  for (j in 1:length(Nom_Endpoints)){
    
    index =grep(paste0("^",Nom_Endpoints[j],"_") , colnames(Sim.Res.ind_i), fixed=FALSE)

    
    Data_sim = as.matrix( Sim.Res.ind_i[ , index] )
    
    MPV    = c(  MPV,  as.numeric( Data_sim[nrow(Data_sim), ] ) )
    IC_min = c(IC_min,  apply(Data_sim, 2, quantile,  0.025, na.rm=TRUE) )
    IC_max = c(IC_max,  apply(Data_sim, 2, quantile,  0.975, na.rm=TRUE) ) 
    
    Endpoint = c(Endpoint, rep(Nom_Endpoints[j], ncol(Data_sim)))
  }
  
  df_mod_ind_i <- data.frame(
    predict.endpoint = MPV,
    Time    = rep(Time_pred, Nsortie),
    low     = IC_min,
    up      = IC_max,
    Endpt   = Endpoint
    )
  
  df_mod_ind_i <- df_mod_ind_i %>%
    mutate(ID=ID_i)

  df_mod_ind_IMD <- rbind(df_mod_ind_IMD, df_mod_ind_i)
}


df_mod_Weight_ind_IMD <- subset(df_mod_ind_IMD, Endpt == "Weight" & Time !=0) |> 
  mutate(Weight = predict.endpoint)|> 
  dplyr::select(c("Time", "low", "up", "ID", "Weight"))
df_mod_CiEPX_ind_IMD <- subset(df_mod_ind_IMD, Endpt == "CiIMD" & Time !=0) |> 
  mutate(CiIMD = predict.endpoint) |> 
  dplyr::select(c("Time", "low", "up", "ID", "CiIMD"))



df_predobs_CiIMD_ind <- dObs_ind |>
  filter(Ratio != "N" & Line != 1) |> 
  mutate(Line_plot = case_when(
    Line == 2 ~ "Low doses (Isobole 2)",
    Line == 5 ~ "High doses (Isobole 5)"
  )
  ) |> 
  left_join(df_mod_CiEPX_ind_IMD, suffix = c("_obs", "_pred")) |>
  dplyr::select(-c(Weight_obs, CiEPX, CeIMD, CeEPX)) |>
  mutate(across(everything(), ~ replace(.x, .x == -1, NA))) |> 
  filter(Time != 0)

df_predobs_Weight_ind <- dObs_ind |>
  filter(Ratio != "N" & Line != 1) |> 
  left_join(df_mod_Weight_ind_IMD, suffix = c("_obs", "_pred")) |>
  dplyr::select(-c(CiIMD_obs, CiEPX, CeIMD, CeEPX)) |>
  mutate(across(everything(), ~ replace(.x, .x == -1, NA))) |> 
  filter(Time != 0)

# mean(subset(dObs_ind, Line == 5)$CiIMD, na.rm=TRUE)
```

```{r predobsIMD, message=F, warning=F}
#| fig-cap: Results of the model fit on experimental data. Predicted values are represented with points with their respective credibility interval of 95%. Thin black and grey lines represent the 2-folds and 5-fold changes, respectively. The thicker black line represents the identity line.
#| label: fig-IMDpredobs
#| fig-height: 4
#| fig-width: 8

pal_Ratio_bis <- c(col_EPX, Nord_aurora[3], Nord_aurora[1],  Nord_aurora[4], col_IMD, Nord_aurora[4] )

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]

seq_line <- seq(0.1, 1.2, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line * fact_1,
  x_1 = seq_line,
  y_1 = seq_line / fact_1,
  x2  = seq_line,
  y2  = seq_line * fact_2,
  x_2 = seq_line,
  y_2 = seq_line / fact_2
)

p_WIMD <- ggplot(
  data = df_predobs_Weight_ind,
  mapping = aes(
    x = Weight_obs,
    y = Weight
  )
) +
  geom_line(
    data = df_line,
    mapping = aes(x = x1, y = y1),
    color = col_line1
  ) +
  geom_line(
    data = df_line,
    mapping = aes(x = x_1, y = y_1),
    color = col_line1
  ) +
  geom_line(
    data = df_line,
    mapping = aes(x = x2, y = y2),
    color = col_line2
  ) +
  geom_line(
    data = df_line,
    mapping = aes(x = x_2, y = y_2),
    color = col_line2
  ) +
  geom_abline(
    slope = 1,
    intercept = 0,
    color = col_line0,
    linewidth = 1
  ) +
  geom_point(
    alpha = 0.5,
    color = col_IMD
  ) +
  scale_x_log10(
    limits = c(0.2, 1.2)
  ) +
  scale_y_log10(
    limits = c(0.2, 1.2)
  ) +
  labs(
    x = "Observed weight of earthworms (g)",
    y = "Predicted weight of earthworms (g)"
  ) +
  theme_minimal()

fact_1 <- 2
fact_2 <- 5

seq_line <- 10^seq(log10(1), log10(50000), length.out = 1000)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line * fact_1,
  x_1 = seq_line,
  y_1 = seq_line / fact_1,
  x2  = seq_line,
  y2  = seq_line * fact_2,
  x_2 = seq_line,
  y_2 = seq_line / fact_2
)

p_CiIMD_predobs <- ggplot(
  data = df_predobs_CiIMD_ind,
  mapping = aes(
    x = CiIMD_obs,
    y = CiIMD
  )
) +
  geom_path(
    data = df_line,
    mapping = aes(x = x1, y = y1),
    color = col_line1
  ) +
  geom_line(
    data = df_line,
    mapping = aes(x = x_1, y = y_1),
    color = col_line1
  ) +
  geom_line(
    data = df_line,
    mapping = aes(x = x2, y = y2),
    color = col_line2
  ) +
  geom_line(
    data = df_line,
    mapping = aes(x = x_2, y = y_2),
    color = col_line2
  ) +
  geom_abline(
    slope = 1,
    intercept = 0,
    color = col_line0,
    linewidth = 1
  ) +
  geom_pointrange(
    mapping = aes(
      ymin = low, 
      ymax = up,
      color = Ratio_plot,
      shape = Line_plot
    ),
    alpha = 0.5,
    #size = 2
  ) +
  labs(
    x = "Observed concentrations of IMD\nin earthworms (ng/g)",
    y = "Predicted concentrations of IMD\nin earthworms (ng/g)"
  ) +
  scale_color_manual(values = pal_Ratio_bis, name = "Mixture Ratio") +
  scale_shape_manual(values = c(shape_EPX, shape_IMD, shape_IMD, shape_IMD), name = "Isobole Number")+
  scale_x_log10(
    limits=c(0.1, 50000)
  ) +
  scale_y_log10(
    limits=c(0.1, 50000)
  ) +
  theme_minimal()

p_predobs_IMD <- p_WIMD + p_CiIMD_predobs + plot_layout(ncol = 2)
```

### Ratio PredObs vs. Obs

```{r predobsratioIMD, message=F, warning=F}
#| fig-cap: Results of the model fit on experimental data. Predicted values are represented with points with their respective credibility interval of 95%. Thin black and grey lines represent the 2-folds and 5-fold changes, respectively. The thicker black line represents the identity line.
#| label: fig-IMDpredobsratio
#| fig-height: 4
#| fig-width: 8

pal_Ratio_bis <- c(col_EPX, "#9EB7C0", Nord_aurora[5],  "#8A87AD", col_IMD, Nord_aurora[4] )

fact_1 <- 2
fact_2 <- 5

seq_line <- seq(1, 50000, 10)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line * fact_1,
  x_1 = seq_line,
  y_1 = seq_line / fact_1,
  x2  = seq_line,
  y2  = seq_line * fact_2,
  x_2 = seq_line,
  y_2 = seq_line / fact_2
)

p_CiIMD_predobsratio <- ggplot(
  data = df_predobs_CiIMD_ind,
  mapping = aes(
    x = CiIMD_obs,
    y = CiIMD/CiIMD_obs
  )
) +
  geom_pointrange(
    mapping = aes(
      ymin=low,
      ymax=up,
      color = Ratio_plot,
      shape = Line_plot
    ),
    alpha = 0.5
  ) +
  labs(
    x = "Observed concentrations of IMD\nin earthworms (ng/g)",
    y = "Ratio of Predicted to observed concentrations of IMD\nin earthworms (ng/g)"
  ) +
  scale_color_manual(values = pal_Ratio_bis, name = "Mixture Ratio") +
  scale_shape_manual(values = c(shape_EPX, shape_IMD, shape_IMD, shape_IMD), name = "Isobole Number")+
  scale_x_log10(
    limits=c(0.1, 50000)
  ) +
  scale_y_log10(
    limits=c(0.1, 50000)
  ) +
  theme_minimal()

p_CiIMD_predobsratio
```

### Full trajectories

```{r}
Time_min <- 0
Time_max <- 35
Time_step <- 0.25
Time_pred <- seq(Time_min, Time_max, Time_step)
print_times <- paste(Time_min, Time_max, Time_step, sep = ", ")

f_Simulation_mix_ind_full(path_mod_mix, Molecule, print_times)
```

```{bash, eval=F, execute=F}
pwd
cd ..
cd ..
cd mod/TK_Mix_IMD
pwd

for j in $(seq 1 43); do
  ./mcsim.m_TK_IMD "Simulation_ind_full_IMD_${j}.in" "Simulation_ind_full_IMD_${j}.out"
done
```

```{r IMDdatapredfull, message=F, warning=F}
#| cache: false

dObs_ind <- df_TK_mix |>
  mutate(
    ID = as.numeric(ID)
  )

colnames(dObs_ind)[colnames(dObs_ind) == "Weight"] <- "Weight_obs"
colnames(dObs_ind)[colnames(dObs_ind) == "CiIMD"] <- "CiIMD_obs"
colnames(dObs_ind)[colnames(dObs_ind) == "CeIMD"] <- "CeIMD_obs"
colnames(dObs_ind)[colnames(dObs_ind) == "t"] <- "Times"

col_exposure <- c(Nord_aurora[4], Nord_aurora[1], Nord_frost[2])


df_sim_full <- lapply(1:43, function(j) {
  f_MCSim_read_sim(file.path(path_mod_mix, paste0("Simulation_ind_full_IMD_", j, ".out"))) %>%
    mutate(
      sim = j,
      ID = as.numeric(IDs[j])
    )
}) %>%
  bind_rows()


df_mod_Weight_ind <- df_sim_full |>
  left_join(dObs_ind, suffix = c("_obs", "_pred"))

df_mod_CiIMD_ind <- df_sim_full |>
  left_join(dObs_ind, suffix = c("_obs", "_pred"))

df_mod_CeIMD_ind <- df_sim_full |>
  left_join(dObs_ind, suffix = c("_obs", "_pred"))
```

```{r IMDpredcurvesdata, message=F, warning=F}
#| fig-cap: Estimated toxicokinetic of the IMD concentration in earthworms exposed to 100 ng/g of IMD. Red points represent the experimental data, the blue curve represent the estimated toxicokinetic curve and the transparent blue band correspond to the credibility interval of the model.
#| fig-label: fig-IMDdatapredfull
#| fig-width: 8
#| fig-height: 10

col_ratio <- nord(palette = "frost", n = 5)

dObs_ind_plot <- dObs_ind |>
  mutate(across(everything(), ~ replace(.x, .x == -1, NA))) 

alpha_point <- 0.5
col_exposure <- c(Nord_aurora[2], Nord_aurora[3], Nord_aurora[4])

p_CiIMD_traj <- ggplot() +
  geom_line(
    data = df_mod_CiIMD_ind,
    aes(
      x = Time,
      y = CiIMD,
      group = ID
    ),
    color = col_IMD,
    fill = col_IMD,
    lwd = 1
  ) +
  geom_point(
    data = dObs_ind_plot,
    aes(
      x = Times,
      y = CiIMD_obs
    ),
    size = 2,
    alpha = 0.7,
    color = col_red
  ) +
  scale_color_manual(values = col_ratio) +
  scale_fill_manual(values = col_ratio) +
  scale_x_continuous(
    breaks = seq(0, max(df_mod_CiIMD_ind$Time), by = 28), # gros ticks
    minor_breaks = seq(0, max(df_mod_CiIMD_ind$Time), by = 14) # petits ticks
  ) +
  facet_wrap(
    ~ Ratio_plot + ID,
    ncol = 4,
    scales = "free_x"
  ) +
  labs(
    x = "Time (days)",
    y = "Concentration of IMD\nin earthworms (ng/g)"
  ) +
  theme_minimal()
```

## Simulations for EPX

```{r increationEPX}
path_mod_mix <- here::here("mod/TK_Mix_EPX")
Nb_experiement <- length(unique(df_TK_mix$ID))
Molecule <- "EPX"
l_param_name <- "kuEPX, keEPX, kperiph"

f_Simulation_mix_ind(path_mod_mix, Molecule, l_param_name)
```

```{bash, results=F, eval=F}
pwd
cd ..
cd ..
cd mod/TK_Mix_EPX
pwd

for j in $(seq 1 43); do
  ./mcsim.m_TK_EPX "Simulation_ind_EPX_${j}.in" "Simulation_ind_EPX_${j}.out"
done

```

### Predicted vs. Observed

```{r EPXdatapredobs, message=F, warning=F}

Nb_experiment_EPX <- 43

dObs_ind <- df_TK_mix |>
  mutate(
    ID = as.numeric(ID)
  )

colnames(dObs_ind)[colnames(dObs_ind) == "Weight"] <- "Weight_obs"
colnames(dObs_ind)[colnames(dObs_ind) == "CiEPX"] <- "CiEPX_obs"
colnames(dObs_ind)[colnames(dObs_ind) == "t"] <- "Time"

col_exposure <- c(Nord_aurora[4], Nord_aurora[1], Nord_frost[2])

IDs <- unique(df_TK_mix$ID)

Sim.Res.ind <- lapply(1:43, function(j) {
  read_tsv(file.path(path_mod_mix, paste0("Simulation_ind_EPX_", j, ".out"))) %>%
    mutate(
      sim = j,
      ID = as.numeric(IDs[j])
    )
}) %>%
  bind_rows()


df_mod_ind_EPX <- NULL

for (i in 1:Nb_experiment_EPX){
  
  ID_i <- unique(dObs_ind$ID)[i]

  Sim.Res.ind_i  <- subset(Sim.Res.ind, sim == i) |> 
    dplyr::select(where(~ !all(is.na(.x))))
  
  dObs_i <- subset(dObs_ind, ID == ID_i)
  
  Time_pred = dObs_i$Time # !!!
  
  Nom_Endpoints = c("Weight", "CiEPX")
  
  Nsortie = 2
  
  MPV = IC_min = IC_max = Endpoint = index = NULL
  
  for (j in 1:length(Nom_Endpoints)){
    
    index =grep(paste0("^",Nom_Endpoints[j],"_") , colnames(Sim.Res.ind_i), fixed=FALSE)

    
    Data_sim = as.matrix( Sim.Res.ind_i[ , index] )
    
    MPV    = c(  MPV,  as.numeric( Data_sim[nrow(Data_sim), ] ) )
    IC_min = c(IC_min,  apply(Data_sim, 2, quantile,  0.025, na.rm=TRUE) )
    IC_max = c(IC_max,  apply(Data_sim, 2, quantile,  0.975, na.rm=TRUE) ) 
    
    Endpoint = c(Endpoint, rep(Nom_Endpoints[j], ncol(Data_sim)))
  }
  
  df_mod_ind_i <- data.frame(
    predict.endpoint = MPV,
    Time    = rep(Time_pred, Nsortie),
    low     = IC_min,
    up      = IC_max,
    Endpt   = Endpoint
    )
  
  df_mod_ind_i <- df_mod_ind_i %>%
    mutate(ID=ID_i)

  df_mod_ind_EPX <- rbind(df_mod_ind_EPX, df_mod_ind_i)
}


df_mod_Weight_ind_EPX <- subset(df_mod_ind_EPX, Endpt == "Weight" & Time !=0) |> 
  mutate(Weight = predict.endpoint)|> 
  dplyr::select(c("Time", "low", "up", "ID", "Weight"))
df_mod_CiEPX_ind_EPX <- subset(df_mod_ind_EPX, Endpt == "CiEPX" & Time !=0) |> 
  mutate(CiEPX = predict.endpoint) |> 
  dplyr::select(c("Time", "low", "up", "ID", "CiEPX"))



df_predobs_CiEPX_ind <- dObs_ind |>
  filter(Ratio != "N" & Line != 1) |> 
  mutate(Line_plot = case_when(
    Line == 2 ~ "Low doses (Isobole 2)",
    Line == 5 ~ "High doses (Isobole 5)"
  )
  ) |> 
  left_join(df_mod_CiEPX_ind_EPX, suffix = c("_obs", "_pred")) |>
  dplyr::select(-c(CiIMD, CeIMD, CeEPX)) |>
  mutate(across(everything(), ~ replace(.x, .x == -1, NA))) |> 
  filter(Time != 0)

df_predobs_Weight_ind <- dObs_ind |>
  filter(Ratio != "N" & Line != 1) |> 
  left_join(df_mod_Weight_ind_EPX, suffix = c("_obs", "_pred")) |>
  dplyr::select(-c(CiIMD, CeIMD, CeEPX)) |>
  mutate(across(everything(), ~ replace(.x, .x == -1, NA))) |> 
  filter(Time != 0)

# mean(subset(df_predobs_CiEPX_ind_ratio, Line == 5)$Ratio_predobs, na.rm=TRUE)
```

```{r predobsEPX, message=F, warning=F}
#| fig-cap: Results of the model fit on experimental data. Predicted values are represented with points with their respective credibility interval of 95%. Thin black and grey lines represent the 2-folds and 5-fold changes, respectively. The thicker black line represents the identity line.
#| label: fig-EPXpredobs
#| fig-height: 4
#| fig-width: 8

pal_Ratio_bis <- c(col_EPX, Nord_aurora[3], Nord_aurora[1],  Nord_aurora[4], col_IMD, Nord_aurora[4] )

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]

seq_line <- seq(0.1, 1.2, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line * fact_1,
  x_1 = seq_line,
  y_1 = seq_line / fact_1,
  x2  = seq_line,
  y2  = seq_line * fact_2,
  x_2 = seq_line,
  y_2 = seq_line / fact_2
)

p_WEPX <- ggplot(
  data = df_predobs_Weight_ind,
  mapping = aes(
    x = Weight_obs,
    y = Weight
  )
) +
  geom_line(
    data = df_line,
    mapping = aes(x = x1, y = y1),
    color = col_line1
  ) +
  geom_line(
    data = df_line,
    mapping = aes(x = x_1, y = y_1),
    color = col_line1
  ) +
  geom_line(
    data = df_line,
    mapping = aes(x = x2, y = y2),
    color = col_line2
  ) +
  geom_line(
    data = df_line,
    mapping = aes(x = x_2, y = y_2),
    color = col_line2
  ) +
  geom_abline(
    slope = 1,
    intercept = 0,
    color = col_line0,
    linewidth = 1
  ) +
  geom_point(
    alpha = 0.5,
    color = col_EPX
  ) +
  scale_x_log10(
    limits = c(0.2, 1.2)
  ) +
  scale_y_log10(
    limits = c(0.2, 1.2)
  ) +
  labs(
    x = "Observed weight of earthworms (g)",
    y = "Predicted weight of earthworms (g)"
  ) +
  theme_minimal()

fact_1 <- 2
fact_2 <- 5

seq_line <- 10^seq(log10(0.005), log10(100000), length.out = 1000)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line * fact_1,
  x_1 = seq_line,
  y_1 = seq_line / fact_1,
  x2  = seq_line,
  y2  = seq_line * fact_2,
  x_2 = seq_line,
  y_2 = seq_line / fact_2
)


p_CiEPX_predobs <- ggplot(
  data = df_predobs_CiEPX_ind,
  mapping = aes(
    x = CiEPX_obs,
    y = CiEPX
  )
) +
  geom_path(
    data = df_line,
    mapping = aes(x = x1, y = y1),
    color = col_line1
  ) +
  geom_line(
    data = df_line,
    mapping = aes(x = x_1, y = y_1),
    color = col_line1
  ) +
  geom_line(
    data = df_line,
    mapping = aes(x = x2, y = y2),
    color = col_line2
  ) +
  geom_line(
    data = df_line,
    mapping = aes(x = x_2, y = y_2),
    color = col_line2
  ) +
  geom_abline(
    slope = 1,
    intercept = 0,
    color = col_line0,
    linewidth = 1
  ) +
  geom_pointrange(
    mapping = aes(
      ymin = low, 
      ymax = up,
      color = Ratio_plot,
      shape = Line_plot
    ),
    alpha = 0.5,
    #size = 2
  ) +
  labs(
    x = "Observed concentrations of EPX\nin earthworms (ng/g)",
    y = "Predicted concentrations of EPX\nin earthworms (ng/g)"
  ) +
  scale_color_manual(values = pal_Ratio_bis, name = "Mixture Ratio") +
  scale_shape_manual(values = c(shape_EPX, shape_IMD, shape_IMD, shape_IMD), name = "Isobole Number")+
  scale_x_log10(
    limits=c(0.005, 100000)
  ) +
  scale_y_log10(
    limits=c(0.005, 100000)
  ) +
  theme_minimal()

p_predobs_EPX <- p_WEPX + p_CiEPX_predobs + plot_layout(ncol = 2)
```

### Full trajectories

```{r}
Time_min <- 0
Time_max <- 35
Time_step <- 0.25
Time_pred <- seq(Time_min, Time_max, Time_step)
print_times <- paste(Time_min, Time_max, Time_step, sep = ", ")

f_Simulation_mix_ind_full(path_mod_mix, Molecule, print_times)
```

```{bash, eval=F, execute=F}
pwd
cd ..
cd ..
cd mod/TK_Mix_EPX
pwd

for j in $(seq 1 43); do
  ./mcsim.m_TK_EPX "Simulation_ind_full_EPX_${j}.in" "Simulation_ind_full_EPX_${j}.out"
done
```

```{r EPXdatapredfull, message=F, warning=F}
#| cache: false

dObs_ind <- df_TK_mix |>
  mutate(
    ID = as.numeric(ID)
  )

colnames(dObs_ind)[colnames(dObs_ind) == "Weight"] <- "Weight_obs"
colnames(dObs_ind)[colnames(dObs_ind) == "CiEPX"] <- "CiEPX_obs"
colnames(dObs_ind)[colnames(dObs_ind) == "CeEPX"] <- "CeEPX_obs"
colnames(dObs_ind)[colnames(dObs_ind) == "t"] <- "Times"

col_exposure <- c(Nord_aurora[4], Nord_aurora[1], Nord_frost[2])


df_sim_full <- lapply(1:43, function(j) {
  f_MCSim_read_sim(file.path(path_mod_mix, paste0("Simulation_ind_full_EPX_", j, ".out"))) %>%
    mutate(
      sim = j,
      ID = as.numeric(IDs[j])
    )
}) %>%
  bind_rows()


df_mod_Weight_ind <- df_sim_full |>
  left_join(dObs_ind, suffix = c("_obs", "_pred"))

df_mod_CiEPX_ind <- df_sim_full |>
  left_join(dObs_ind, suffix = c("_obs", "_pred"))

df_mod_CeEPX_ind <- df_sim_full |>
  left_join(dObs_ind, suffix = c("_obs", "_pred"))
```

```{r EPXpredcurvesdata, message=F, warning=F}
#| fig-cap: Estimated toxicokinetic of the EPX concentration in earthworms exposed to 1000 ng/g of EPX. Red points represent the experimental data, the blue curve represent the estimated toxicokinetic curve and the transparent blue band correspond to the credibility interval of the model.
#| fig-label: fig-EPXdatapredfull
#| fig-width: 8
#| fig-height: 10

col_ratio <- nord(palette = "frost", n = 5)

dObs_ind_plot <- dObs_ind |>
  mutate(across(everything(), ~ replace(.x, .x == -1, NA))) 

alpha_point <- 0.5
col_exposure <- c(Nord_aurora[2], Nord_aurora[3], Nord_aurora[4])

p_CiEPX_traj <- ggplot() +
  geom_line(
    data = df_mod_CiEPX_ind,
    aes(
      x = Time,
      y = CiEPX,
      group = ID
    ),
    color = col_EPX,
    fill = col_EPX,
    lwd = 1
  ) +
  geom_point(
    data = dObs_ind_plot,
    aes(
      x = Times,
      y = CiEPX_obs
    ),
    size = 2,
    alpha = 0.7,
    color = col_red
  ) +
  scale_color_manual(values = col_ratio) +
  scale_fill_manual(values = col_ratio) +
  scale_x_continuous(
    breaks = seq(0, max(df_mod_CiEPX_ind$Time), by = 28), # gros ticks
    minor_breaks = seq(0, max(df_mod_CiEPX_ind$Time), by = 14) # petits ticks
  ) +
  facet_wrap(
    ~ Ratio_plot + ID,
    ncol = 4,
    scales = "free_x"
  ) +
  labs(
    x = "Time (days)",
    y = "Concentration of EPX\nin earthworms (ng/g)"
  ) +
  theme_minimal()
```

## Summary

```{r, message=F, warning=F}
#| fig-cap: Results of the model fits on experimental data. Predicted values are represented with points with their respective credibility interval of 95%. Thin black and grey lines represent the 2-folds and 5-fold changes, respectively. The thicker black line represents the identity line.
#| label: fig-MIXpredobs
#| fig-height: 8
#| fig-width: 8

p_predobs_full <- p_WEPX + p_CiEPX_predobs + p_WIMD + p_CiIMD_predobs + plot_layout(ncol = 2)
p_predobs_full
```

```{r, include = F}
ggsave(
  filename = "TK_MIX_predobs.png",
  plot = p_predobs_full,
  width = 8, height = 8,
  path = path_fig
)
ggsave(
  filename = "TK_MIX_preobs.svg",
  plot = p_predobs_full,
  width = 8, height = 8,
  path = path_fig
)
```

```{r, include = FALSE}
p_predobs_Ci <- (
  (p_CiIMD_predobs + theme(legend.position = "none")) +
    p_CiEPX_predobs +
    plot_layout(ncol = 2, guides = "collect")
) +
  plot_annotation(tag_levels = "A") &
  theme(
    plot.tag = element_text(face = "bold"),
    plot.tag.position = c(0, 1)
  )
```

```{r, include = F}
ggsave(
  filename = "Article_predobs_mix.png",
  plot = p_predobs_Ci,
  width = 8, height = 4,
  path = here::here("fig")
)
```

```{r, message=F, warning=F}
#| fig-cap: Estimated toxicokinetic of the EPX & IMD concentrations in earthworms. Red points represent the experimental data, the blue curve represent the estimated toxicokinetic curve and the transparent blue band correspond to the credibility interval of the model.
#| fig-label: fig-MIXdatapredfull
#| fig-width: 8
#| fig-height: 30

p_traj_full <- p_CiEPX_traj + p_CiIMD_traj + plot_layout(ncol = 1)
p_traj_full
```

```{r, include = F}
ggsave(
  filename = "TK_MIX_traj_EPX.png",
  plot = p_CiEPX_traj,
  width = 12, height = 8,
  path = path_fig
)
ggsave(
  filename = "TK_MIX_traj_EPX.svg",
  plot = p_CiEPX_traj,
  width = 12, height = 8,
  path = path_fig
)

ggsave(
  filename = "TK_MIX_traj_IMD.png",
  plot = p_CiIMD_traj,
  width = 12, height = 8,
  path = path_fig
)
ggsave(
  filename = "TK_MIX_traj_IMD.svg",
  plot = p_CiIMD_traj,
  width = 12, height = 8,
  path = path_fig
)
```

Single substances were also tested at two concentrations within the mixture experiment and served to validate the single-substance toxicokinetic models (@fig-MIXdatapredfull). For both compounds, internal concentrations measured in earthworms exposed to low doses were well predicted by the respective single-substance models.

However, deviations emerged at higher doses. For imidacloprid, internal concentrations appeared to reach a plateau in earthworm tissues, with a mean internal concentration of 1676 ng/g, suggesting a potential saturation process. In contrast, epoxiconazole internal concentrations were systematically underestimated by the model at high doses, with a mean predicted-to-observed ratio of 0.34. No consistent trend related to mixture ratios was observed.

Additionally, the residual concentration of epoxiconazole measured in earthworms exposed only to imidacloprid is not captured by our model, which predicts a decline toward zero due to the absence of epoxiconazole in the soil and ongoing elimination during the experiment. This discrepancy may be explained by the presence of a small background burden of epoxiconazole retained in earthworm tissues, potentially accumulated over time during laboratory culture.
