# Preliminary information about this study

People that have contributed to this study :

-   Valentine Lebars (M1 internship) : Toxicokinetics tests & EC50 tests & Earthworms breeding (May - July 2024)
-   Maia Collombel (L3 internship) : Toxicokinetics tests & EC50 tests & Earthworms breeding (May - June 2024)
-   Laura Frattaroli (research technician) : Earthworms breeding & Mixture tests (October 2024 - August 2025)
-   Julien Rouyer (Gap year intership of engineering school) : Earthworms breeding & Mixture tests (October - December 2024)
-   Cheikh Ahmed Tidane Sarr (M2 intership) : Mixture tests (March - August 2025)

## Abstract

## GANTT {#sec-GANTT}

```{r,, include=F}
# Load necessary libraries
library(ggplot2)
library(dplyr)
library(lubridate)
library(forcats)
library(nord)

Nord_frost <- nord(palette = "frost")
Nord_aurora <- nord(palette = "aurora")
Nord_polar <- nord(palette = "polarnight")
```

```{r, echo=F, warning=F}
#| fig-cap: GANTT
#| label: fig-GANTT
#| fig-width: 10
#| fig-height: 4

# Sample data
data_gantt <- data.frame(
  task = c(
    "1. Preliminary tests",                      # 1
    "2. Toxicokinetic tests",                    # 2
    "3.1. EC50 tests for IMD",                   # 3
    "3.2. EC50 tests for EPX",                   # 4
    "4.1. Mixture tests - Autumn 2024",          # 5
    "4.2. Mixture tests - Small test with IMD",  # 6
    "4.3. Mixture tests - Spring 2025",          # 7
    "4.3. Mixture tests - Hatchling monitoring"  # 8
  ),
  start_date = as.Date(
    c(
      "2024-03-05",                              # 1
      "2024-05-27",                              # 2
      "2024-04-01",                              # 3
      "2024-05-03",                              # 4
      "2024-10-14",                              # 5
      "2025-01-07",                              # 6
      "2025-03-25",                              # 7
      "2025-04-30"                               # 8
    )
  ),
  end_date = as.Date(
    c
    ("2024-04-19",                               # 1
      "2024-07-04",                              # 2
      "2024-07-08",                              # 3
      "2024-07-08",                              # 4
      "2024-12-18",                              # 5
      "2025-02-05",                              # 6
      "2025-04-30",                              # 7
      "2025-07-31"                               # 8
    )
  ),
  status = c(
    "Completed",                                 # 1
    "Completed",                                 # 2
    "Completed",                                 # 3
    "Completed",                                 # 4
    "Completed",                                 # 5
    "Completed",                                 # 6
    "Completed",                                 # 7
    "In Progress"                                # 8
  )
)

# Custom color palette for the statuses

status_colors <- c("In Progress" = Nord_frost[1], "Completed" = Nord_frost[4])

# Creating the Gantt chart
ggplot(
  data_gantt, 
  aes(
    x = start_date, 
    # y = reorder(task, -as.numeric(start_date))
    y = fct_rev(task)
  )
) +  # Reorder tasks
  
  geom_segment(
    aes(
      xend = end_date, 
      yend = task, 
      color = status
    ), 
    size = 6, 
    lineend = "round",
    alpha = 0.7
  ) +  # Rounded bars
  
  geom_text(
    aes(
      x = ymd(start_date) + (ymd(end_date)-ymd(start_date))/2, 
      label = task,
    ),
    hjust = 0.5,
    vjust = -1.2,
    size = 4, 
    color = "black",
    fontface = "bold"
  )+
  
  scale_color_manual(values = status_colors) +  # Apply custom colors
  
  labs(
    title = "Project Timeline",
    x = NULL,  # Remove axis title for x
    y = NULL,  # Remove axis title for y
    color = "Status"
  ) +
  
  theme_minimal(base_family = "Arial") +                                          # Use a clean, sans-serif font
  theme(
    plot.title = element_text(size = 18, face = "bold", hjust = 0.5),             # Title style
    legend.position = "right",
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    # axis.text.y = element_text(size = 12, hjust = 0, face = "bold"),                                        # Make task labels bold
    axis.text.y = element_blank(),
    axis.text.x = element_text(size = 10, color = "grey40"),                      # Date labels in grey
    panel.grid.minor = element_blank(),                                           # Remove minor grid lines
    panel.grid.major.y = element_blank(),                                         # Remove horizontal grid lines
    panel.grid.major.x = element_line(color = "grey85", linetype = "dashed")      # Subtle dashed vertical grid
  ) +
  scale_x_date(date_labels = "%b %Y", date_breaks = "2 month", expand = c(0, 0))  # Custom date formatting


```
