---
title: "Modèle TK EPX"
subtitle: "v1.1"
author:
  - name: Lisa Gollot
    email: lisa.gollot@agroparistech.fr
lang: fr
format: 
  pdf:
    echo: false
    documentclass: scrreprt
    toc: true
    toc-depth: 3
    lof: true
    lot: true
    tbl-colwidths: auto
    df-print: tibble
    number-sections: true
    fontsize: large
    linestretch: 1.2
    layout: 
      - header=1cm
    geometry: 
      - top=2cm
      - bottom=2cm
      - left=2cm
      - right=2cm
    include-in-header: 
      text: 
        \usepackage{pdfpages}
        \usepackage{lscape}
        \newcommand{\blandscape}{\begin{landscape}}
        \newcommand{\elandscape}{\end{landscape}}
editor: 
    markdown:
      canonical: true
execute:
  cache: true
---

```{r, include=F}
library(here)
source(file = here::here("functions/fun.R"))
f_load_libraries_colors()
col_Molecule <- rev(col_Molecule)
```

# Toxicokinetics of Epoxiconazole

## Results of the experiment

### Data importation

Notations :

-   `Date_start` : Start of the experiement (t0)
-   `Molecule` : Substance to which the earthworm is exposed
-   `Dose` : Exposure dose (mg/kg)
-   `ID_recipient` : Recipient in which the soil was prepared
-   `ID_camp` : ID of the earthworm campagne and generation (see XXX for more information)
-   `ID` : ID of the earthworm
-   `Nb_rep` : Identification number of the replicate
-   `Time_point` : Time point to which the earthworm is dedicated
-   `Phase` : Uptake or Elimination phase
-   `Time_introduction_D0` : Time of the day when the earthworm was introduced into his contaminated cosm
-   `w0` : Body weight at t0
-   `w_Tp` : Body weight at the given time point
-   `w_frozen` : Body weight before congelation
-   `C_worm` : Measured concentration of the substance in the earthworm
-   `C_soil` : Measured concentration of the substance in the soil at the given time point

```{r data, warning=F, message=F}


df_TK_EPX <- f_read_data_TK("EPX") %>%
  mutate(across(where(is.numeric), ~ na_if(.x, -1)))


df_TK_EPX <- df_TK_EPX |> 
  mutate(
    Time = t,
    CiIMD = C_worm_IMD,
    CiEPX = C_worm_EPX,
    Weight = Weight_nog,
    Time_point_f = as.factor(Time_point)
  ) |> 
  dplyr::select(Time, CiEPX, CiIMD, Weight, w, Molecule, ID, expo, Time_point_f) |> 
  mutate(
    CiEPX = na_if(CiEPX, -1),
    CiIMD = na_if(CiIMD, -1)
    )

df_TK_EPX_mean <- df_TK_EPX |> 
  dplyr::select(-ID) |> 
  group_by(Time) |> 
  summarise(
    CiEPX = exp(mean(log(CiEPX[CiEPX > 0]), na.rm = TRUE)),
    CiIMD = exp(mean(log(CiIMD[CiIMD > 0]), na.rm = TRUE)),
    Weight = mean(Weight, na.rm = TRUE),
    w = mean(w, na.rm = TRUE),
    expo = mean(expo),
    .groups = "drop"
  ) |> 
  mutate(Molecule = "EPX")
```

### Initial state

```{r, warning=F, message=F}
#| fig-cap: Initial weights (with gut content) of earthworms. 
#| label: fig-init
#| fig-width: 6
#| fig-height: 4

# Weights at t=0
plot_D0 <- ggplot(
  data=subset(df_TK_EPX, Time==0), 
  aes(
    x=Time_point_f, 
    y=w, 
    color=Molecule, 
    fill=Molecule
    )
  )+

  geom_boxplot(alpha=0.2)+
  geom_dotplot(
    binaxis='y', 
    stackdir='center', 
    dotsize=0.7, 
    alpha=0.7
    )+
  facet_wrap(~Molecule, ncol=1, scales="free")+
  
  scale_color_manual(values=col_Molecule)+
  scale_fill_manual(values=col_Molecule)+

  labs(x="Dose (mg/kg)", y="Weight (mg)")+
  

  theme_classic(14)+
  theme(
    legend.position = "none", 
    legend.title=element_text(size=sizetitle-2,face="bold"),
    legend.text = element_text(size=sizetitle-2,face="plain"),
    
    title=element_text(size=sizetitle, face="bold"), 
    
    axis.title.x = element_blank(),
    axis.title.y = element_text(size=sizetitle,face="plain"),
    
    axis.text.x = element_blank(),
    axis.line.x=element_blank(),
    axis.ticks.x=element_blank(),
    
    
    strip.background = element_rect(
      color="black", 
      fill=Nord_snow[3], 
      size=0, 
      linetype="solid"
      ),
    strip.text = element_text(face = "bold")
    )
plot_D0
```

```{r, include=F}
ggsave(
  filename="TK_EPX_initial_weights.png", 
  plot=plot_D0, 
  width=6, 
  height = 4, 
  path=here::here("fig/TK")
  )
```

### Growth curves

```{r, warning=F, message=F}
#| fig-cap: Evolution of earthworms body weight (with gut content) throughout the experiment. 
#| label: fig-growthcurves
#| fig-width: 8
#| fig-height: 4

p <- ggplot() +
  geom_vline(
    xintercept = 21, 
    color = Nord_snow[1],
    linetype = "dashed"
    )+

  geom_point(
    data = subset(df_TK_EPX, !expo==2),
    aes(
      x = Time,
      y = w,
      group = ID,
      color = Molecule
      ),
    alpha=0.5
    ) +
  
  annotate(
    geom = "text",
    x = 10,
    y = 1.200,
    label = "Uptake\n phase",
    color = Nord_aurora[1],
    fontface = "bold",
    size = 3.5
  )+
  annotate(
    geom = "text",
    x = 35,
    y = 1.200,
    label = "Elimination\n phase",
    color = Nord_aurora[4],
    fontface = "bold",
    size = 3.5
  )+
  facet_wrap(~Molecule)+
  scale_color_manual(values=col_Molecule)+
  scale_fill_manual(values=col_Molecule)+
  labs(
   # title = "Growth Curves",
    x = "Time (days)",
    y = "Weight",
    color = ""
  ) +
  theme_minimal(base_size = 15) +  # Thème minimaliste
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    legend.position = "none",
    strip.background = element_rect(
      color="black", 
      fill=Nord_snow[3], 
      size=0, 
      linetype="solid"
      ),
    strip.text = element_text(face = "bold")
  )
p
```

```{r, include=F}
ggsave(
  filename="TK_EPX_growth_curves.png", 
  plot=p, 
  width=8, 
  height = 4, 
  path=here::here("fig/TK")
  )
ggsave(
  filename="TK_EPX_growth_curves.svg", 
  plot=p, 
  width=8, 
  height = 4, 
  path=here::here("fig/TK")
  )
```

```{r, warning=F, message=F}
#| fig-cap: Evolution of earthworms body weight before and after fasting 
#| label: fig-fasting
#| fig-width: 8
#| fig-height: 10

p_EPX <- ggplot() +
  geom_vline(
    xintercept = 21, 
    color = Nord_snow[1],
    linetype = "dashed"
    )+
  geom_point(
    data = df_TK_EPX,
    aes(
      x = Time,
      y = w,
      group = ID
      ),
    alpha=0.5,
    color = col_EPX
    ) +

  facet_wrap(~ID)+
  labs(
    title = "Growth Curves",
    x = "Time (days)",
    y = "Weight",
    color = ""
  ) +
  theme_minimal(base_size = 12) +  # Thème minimaliste
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    legend.position = "none",
    strip.background = element_rect(
      color="black", 
      fill=Nord_snow[3], 
      size=0, 
      linetype="solid"
      ),
    strip.text = element_text(face = "bold")
  )

p_EPX
```

```{r, warning=F, message=F}

# t1 = dernière masse avant expo == 2
t1_df <- df_TK_EPX %>%
  filter(expo != 2) %>%
  group_by(ID) %>%
  filter(Time == max(Time)) %>%
  dplyr::select(ID, w1 = w, Molecule)

# t2 = première masse pendant expo == 2
t2_df <- df_TK_EPX %>%
  filter(expo == 2) %>%
  group_by(ID) %>%
  dplyr::select(ID, w2 = w, Molecule)

# Joindre les deux et calculer le pourcentage de perte
df_TK_fasting <- t1_df %>%
  inner_join(t2_df, by = c("ID", "Molecule")) %>%
  mutate(
    Per_loss = 100 * (w1 - w2) / w1,
    #Loss = (w1 - w2)
    Loss = w2
    )

summary(df_TK_fasting)

```

```{r}
#intercept <- 1.0
#fit <- lm(I(x - intercept) ~ 0 + y, lin)> summary(fit)
lm.fasting <- lm(Loss ~ w1+0, data = df_TK_fasting)
summary(lm.fasting)
#plot(lm.fasting)

ggplot(
  data = df_TK_fasting
)+
  geom_point(
    aes(
      x=w1,
      y=Loss,
      color = Molecule
      ),
    alpha = 0.3
  )+
  geom_abline(
    intercept = 0,
    slope = lm.fasting$coefficients[1],
    color = col_red
  )+
  scale_color_manual(values = col_Molecule)+
  theme_minimal()


```

!!!!!!!! Growth rates !!!!!

### Measured internal concentrations

```{r, message=F, warning=F}
#| fig-cap: Measurements of EPX concentration in earthworms exposed to 10 mg/kg of EPX and related weight measurement of earthworms. Points represent the experimental data, the blue curve and the transparent blue band are produced with geom_smooth. 
#| fig-label: fig-curvesmooth
#| fig-width: 8
#| fig-height: 4

p <- ggplot(
  data = df_TK_EPX,
  aes(
    x = Time
  )
  )+
  geom_point(
    mapping = aes(
      y = CiEPX
    ),
    color = col_EPX,
    fill = col_EPX
  )+
  geom_point(
    mapping = aes(
      y = CiIMD
    ),
    color = col_IMD,
    fill = col_IMD
  )+
  facet_wrap(~Molecule, ncol = 2, scales = "free")+
  labs(
    x = "Time (days)",
    y = "Concentration in earthworm (ng/g)"
  )+
  theme_minimal()
p
```

## Modeling of the toxicokinetics

```{r increation, message=F, warning=F, eval=F}
source(file = here::here("functions/fun.R"))
Molecule <- "EPX"

Nb_Iter <- 20000
seeds <- c(C1 = 3333, C2 = 6666, C3 = 1213)

text_priors <- "Distrib(kuEPX,     LogUniform,   0.00001, 100000); # min, max 
Distrib(keEPX,    LogUniform,   0.00001, 100000); # min, max

Distrib(kcomp_in,     LogUniform,   0.00001, 100000); # min, max 
Distrib(kcomp_out,    LogUniform,   0.00001, 100000); # min, max

Distrib(a_growth,  TruncNormal,   0.005,   0.005,    -0.5,    1); # mean, sd, min, max
Distrib (Vr_a_growth,  TruncNormal, 0.0015, 0.0015, 0, 1);

Distrib(Sigma_W,     TruncNormal,  0.03, 0.01, 0.0001, 1);
Distrib(Sigma_CiEPX, TruncNormal,  3.0, 3.0,    1, 1000);"

text_likelihood <- "Likelihood(CiEPX,  LogNormal, Prediction(CiEPX),  Sigma_CiEPX);  # Calcul des vraisemblances (geometric mean, geometric standard deviation)
Likelihood(Weight, Normal,    Prediction(Weight), Sigma_W);      # Calcul des vraisemblances"

text_param_ind <- "Distrib(a_growth,  TruncNormal, a_growth,  Vr_a_growth, -1.0, 1);"

f_In_tot(Molecule, text_priors, text_likelihood, text_param_ind, Nb_Iter, seeds)
```

```{bash, eval=F, execute=F}
pwd
cd ..
cd ..
cd mod/TK_EPX
pwd

makemcsim m_TK_EPX.model &
wait
./mcsim.m_TK_EPX TK_EPX_C1.in &
./mcsim.m_TK_EPX TK_EPX_C2.in &
./mcsim.m_TK_EPX TK_EPX_C3.in &
wait

<!-- or -->

<!-- makemcsim m_TK_EPX.model & -->
<!-- for j in $(seq 1 62); do -->
<!-- ./mcsim.m_TK_EPX TK_EPX_C${j}.in -->
<!-- done -->
```

```{r, message=F, warning=F}
Molecule <- "EPX"
path_mod_EPX <- here::here("mod/TK_EPX")
```

The first step is to retrieve the information of the MCMC simulation experiments.

The inputs :

-   Input files must a name like "xxxxx.1.in"
-   Output files must a name like "xxxxx.1.out"

```{r EPXreadMCMC, message=F, warning=F, results='hidden'}
MCMC_out_EPX <- f_MCSim_ind(path_mod_EPX)

NC <- MCMC_out_EPX$NC
Nb_param <- MCMC_out_EPX$Nb_param
Nb_experiement <- MCMC_out_EPX$Nb_experiement
Nb_iter_kept <- MCMC_out_EPX$Nb_iter_kept
N_iter_setpoint <- MCMC_out_EPX$N_iter_setpoint

L_parameters <- unique(MCMC_out_EPX$Priors$Nom)

```

We can retrieve different information from the model :

-   The number of chains used : `r NC`
-   The number of parameters : `r Nb_param`
-   The number of experiments : `r Nb_experiement`
-   The number of last iterations used to describe the posterior distribution : `r Nb_iter_kept`
-   The number of last iterations used to create the `tab_setpoint.out` file : `r N_iter_setpoint`

Warning : Run the command `./mcsim.m_TK_EPX TK_EPX_Setpoint.in` in the terminal while being in the folder `mod/TK_EPX` to create the `Setpoints.out` now. Do the same with `./mcsim.m_TK_EPX TK_EPX_Setpoint_ind.in` to create the `Setpoints_ind.out` and with `./mcsim.m_TK_EPX TK_EPX_Setpoint_ind_full.in` to create the `Setpoints_ind_full.out`.

### Priors used for the model

```{r EPXreadpriors, message = F, warning = F}
#| tbl-cap: Priors used for the model
#| tbl-label: tbl-EPXPriors

#colnames(MCMC_out_EPX$Priors) <- c("Nom", "Distribution", "Mean", "Sd", "Min", "Max")

# MCMC_out_EPX$Priors |> datatable(
#   options = list(
#     dom = 't',
#     autoWidth = TRUE,
#     columnDefs = list(
#       list(className = 'dt-left', targets = "_all")
#       )
#     ), 
#   class="hover"
#   ) 

MCMC_out_EPX$Priors
```

```{r EPXpriors, message=F, warning=F}
#| fig-cap: Distributions of the priors.
#| label: fig-EPXprior
#| fig-height: 6
#| fig-width: 8

n_samples <- 1e6 # Simulation of the distribution

df_priors_dist <- MCMC_out_EPX$Priors |> 
  dplyr::select(Nom, Distribution, P1, P2, P3, P4) |> 
  rowwise() |> 
  mutate(samples = case_when(
    Distribution == "Uniform" ~ list(runif(n_samples, min = P1, max = P2)),
    Distribution == "Normal" ~ list(rnorm(n_samples, mean = P1, sd = P2)),
    Distribution == "LogUniform" ~ list(exp(runif(n_samples, min = log(P1), max = log(P2)))),
    Distribution == "TruncNormal" ~ list(rtruncnorm(n_samples, a = P3, b = P4, mean = P1, sd = P2))
  )) |> 
  unnest(samples) |> 
  filter(!(Nom %in% c("kuEPX", "keEPX","kcomp_in", "kcomp_out") & samples > 0.01))

col_prior <- Nord_polar[4]
alpha_prior <- 0.5

p_priors <- ggplot() +
  facet_wrap(~Nom, scales = "free")+
  
  stat_halfeye(
    data = df_priors_dist, 
    aes(
       x = samples
       ),
    alpha = alpha_prior,
    fill = col_prior,
    color = col_prior,
    normalize = "xy" 
    ) +
  
  labs(
    title = "Priors distributions", 
    x = "Parameter value", 
    y = "Density"
    ) +
  theme_minimal()

p_priors 

```

```{r, include = F}
ggsave(
  filename="TK_EPX_priors.png", 
  plot=p_priors, 
  width=8, height = 6, 
  path=here::here("fig/TK/")
  )
ggsave(
  filename="TK_EPX_priors.svg", 
  plot=p_priors, 
  width=8, height = 6, 
  path=here::here("fig/TK/")
  )
```

### Chains

```{r EPXChains, message=F, warning=F}
#| fig-cap: Parameters chains. Only the first iteration and the last `r Nb_iter_kept` are represented.
#| label: fig-EPXchains
#| fig-height: 5
#| fig-width: 8

p_chains <-  
  ggplot(
    data = MCMC_out_EPX$Chains, 
    aes(
      x = Iteration, 
      y = value, 
      color = as.factor(Chain), 
      group = as.factor(Chain)
      )
  )+
  geom_line(alpha=0.7)+
  scale_y_log10()+
  facet_wrap(~Parameter, scales = "free", ncol = 2)+
  
  scale_color_manual(name = "Chains", values = nord(palette = "frost"))+
  
  theme_bw()+
  theme(
    legend.position = "right", 
    title=element_text(size=12, face="plain"), 
    axis.title.x = element_text(face="plain"),
    strip.background = element_rect(fill="white")
    )

p_chains
  
```

```{r, include = F}
ggsave(
  filename="TK_EPX_chains.png", 
  plot=p_chains, 
  width=8, height = 5, 
  path=here::here("fig/TK/")
  )
ggsave(
  filename="TK_EPX_chains.svg", 
  plot=p_chains, 
  width=8, height = 5, 
  path=here::here("fig/TK/")
  )
```

We can also take a look at the likelihood and the deviance ratio.

```{r EPXlike, message=F, warning=F}
#| fig-cap: Evolution of likelihood and deviance ratio through the iterations.
#| label: fig-EPXlike
#| fig-height: 5
#| fig-width: 8

p1 <- ggplot(
  MCMC_out_EPX$df_LnPost_start, 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = c("1", "2", "3"), values = Nord_frost) +
  labs(
    x = "First half iterations", 
    y = "LnPosterior"
    ) +
  theme_minimal()

p2 <- ggplot(
  MCMC_out_EPX$df_LnPost, 
  aes(
    x = iteration, 
    y = LnPosterior, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = c("1", "2", "3"), values = Nord_frost) +
  labs(
    x = paste(MCMC_out_EPX$Nb_iter_kept, "last iterations"), 
    y = "LnPosterior"
    ) +
  theme_minimal()

p3 <- ggplot(
  MCMC_out_EPX$df_Devc, 
  aes(
    x = iteration, 
    y = RatioDeviance, 
    color = Chain
    )
  ) +
  geom_line() +
  scale_color_manual(name = "Chains", label = c("1", "2", "3"), values = Nord_frost) +
  labs(
    x = paste(MCMC_out_EPX$Nb_iter_kept, "last iterations"), 
    y = "Ratio Deviance"
    ) +
  theme_minimal()

p_LL <- p1 + p2 + p3 +
  plot_layout(ncol=3, guides = "collect")
p_LL

```

```{r, include = F}
ggsave(
  filename="TK_EPX_likedevratio.png", 
  plot=p_LL, 
  width=8, height = 5, 
  path=here::here("fig/TK/")
  )
ggsave(
  filename="TK_EPX_likedevratio.svg", 
  plot=p_LL, 
  width=8, height = 5, 
  path=here::here("fig/TK/")
  )
```

Correlations :

```{r mcmclist, message=F, warning=F}
# Large format per chain
mcmc_list <- lapply(split(MCMC_out_EPX$Chains, MCMC_out_EPX$Chains$Chain), function(d) {
  wide <- d %>%
    dplyr::select(Iteration, Parameter, value) %>%
    pivot_wider(names_from = Parameter, values_from = value) %>%
    arrange(Iteration)
  
  mcmc(as.matrix(wide[,-1]))
})

mcmc_list <- as.mcmc.list(mcmc_list)

```

```{r corr, message=F, warning=F}
#| fig-cap: Parameter correlations.
#| label: fig-corr
#| fig-height: 5
#| fig-width: 6

colramp_aurora <- colorRampPalette(rev(Nord_aurora[1:4]))
ipairs(as.matrix(mcmc_list), colramp = colramp_aurora, pixs=0.25, cex.diag = 0.5)
```

### Parameter estimation results

```{r EPXpost, message=F, warning=F}
#| fig-cap: Distributions of the priors and the posteriors.
#| label: fig-EPXpost
#| fig-height: 6
#| fig-width: 8

alpha_prior <- 0.5
alpha_post <- 0.5
col_prior <- Nord_snow[1]
col_post <- col_EPX


MCMC_out_EPX$Chains_plot <- MCMC_out_EPX$Chains |> 
  mutate(Nom = str_remove(Parameter, "\\.\\d+\\.$")) |> 
  filter(!((Nom %in% c("kcomp_in","kcomp_out") & value > 0.02)))|> 
  filter(!((Nom %in% c("kuEPX") & value > 5)))

p_post <- ggplot() +
  
  # Priors
  stat_halfeye(
    data = df_priors_dist,
    aes(
       x = samples,
       #y = ..scaled..
       ),
    alpha = alpha_prior,
    fill = col_prior,
    color = col_prior,
    normalize = "xy"
    ) +
  
  # Posterior
  stat_halfeye(
    data = subset(MCMC_out_EPX$Chains_plot, Nom %in% L_parameters),
    mapping = aes(
      x=value
    ),
    fill = col_post,
    color = col_post,
    alpha = alpha_post,
    normalize = "xy"
  ) +
  
  facet_wrap(~Nom, scales = "free")+
  labs(
    title = "<span style = 'color:#88C0D0;'>Posterior</span>
       and <span style = 'color:#D8DEE9;'>prior</span> distributions", 
    x = "Parameter value", 
    y = "Density"
    ) +
  theme_minimal()+
  theme(
    title=element_markdown(face="bold")
  )

p_post
```

```{r, include = F}
ggsave(
  filename="TK_EPX_post.png", 
  plot=p_post, 
  width=8, height = 6, 
  path=here::here("fig/TK/")
  )
ggsave(
  filename="TK_EPX_post.svg", 
  plot=p_post, 
  width=8, height = 6, 
  path=here::here("fig/TK/")
  )
```

```{r calcBCFEPX, message=F, warning=F}

f_get_mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}

MCMC_out_EPX$Chains <- MCMC_out_EPX$Chains |> 
  mutate(Nom = str_remove(Parameter, "\\.\\d+\\.$"))

ku_samples <- MCMC_out_EPX$Chains |> filter(Nom == "kuEPX")
ke_samples <- MCMC_out_EPX$Chains |> filter(Nom == "keEPX")

BCF_samples <- ku_samples$value / ke_samples$value

BCF_mode <- f_get_mode(BCF_samples)
BCF_CI <- quantile(BCF_samples, probs = c(0.025, 0.975))
BCF_CI_low <- as.numeric(BCF_CI[1])
BCF_CI_up <- as.numeric(BCF_CI[2])
BCF_min <- min(BCF_samples)
BCF_max <- max(BCF_samples)
BCF_mean <- mean(BCF_samples)
BCF_sd <- sd(BCF_samples)

BCF <- c(
  BCF_mode, 
  BCF_CI_low, BCF_CI_up, 
  BCF_min, BCF_max, 
  BCF_mean, BCF_sd
  )

```

```{r EPXSummaryRes, message=F, warning=F}
#| tbl-cap: Results summary
#| tbl-label: tbl-EPXressum

Summary_res_EPX_tmp <- cbind(as.data.frame(MCMC_out_EPX$Summary_res)[1:length(L_parameters)], BCF)

Summary_res_EPX_f <- Summary_res_EPX_tmp |> 
  mutate(across(where(is.numeric), signif, 2))

# Summary_res_EPX_f |> datatable(
#   options = list(
#     dom = 't',
#     autoWidth = TRUE,
#     columnDefs = list(
#       list(className = 'dt-left', targets = "_all")
#       )
#     ), 
#   class="hover"
#   ) 

Summary_res_EPX_f

```

### Comparison of observed vs. predicted data

```{r setpointindin, message=F, warning=F, eval=F}
l_param_name <- "kuEPX, keEPX, kcomp_in, kcomp_out, a_growth"
f_Setpoint_ind(Molecule, l_param_name)
```

```{bash, eval=F, execute=F}
pwd
cd ..
cd ..
cd mod/TK_EPX
pwd

for j in $(seq 1 62); do
./mcsim.m_TK_EPX TK_EPX_Setpoint_ind_${j}.in
done
```

```{r EPXdataObs, message=F, warning=F}

dObs_ind <- df_TK_EPX |> 
  mutate(
    ID = as.numeric(ID),
    Group = case_when(
      ID < 65 ~ "Uptake",
      ID > 64 ~ "Elimination"
    )
    )

colnames(dObs_ind)[colnames(dObs_ind) == "Weight"] <- "Weight_obs"
colnames(dObs_ind)[colnames(dObs_ind) == "CiEPX"] <- "CiEPX_obs"
colnames(dObs_ind)[colnames(dObs_ind) == "t"] <- "Times"

col_exposure <- c(Nord_aurora[4], Nord_aurora[1], Nord_frost[2])

```

```{r EPXdatapred, message=F, warning=F}

Sim.Res.ind <- lapply(1:62, function(j) {
  read_tsv(file.path(path_mod_EPX, paste0("Setpoints_ind_", j, ".out"))) %>%
    mutate(sim = j)
}) %>%
  bind_rows()

df_mod_ind <- NULL

for (i in 1:Nb_experiement){
  
  ID_i <- unique(dObs_ind$ID)[i]

  Sim.Res.ind_i  <- subset(Sim.Res.ind, sim == i) |> 
    dplyr::select(where(~ !all(is.na(.x))))
  
  dObs_i <- subset(dObs_ind, ID == ID_i)
  
  Time_pred = dObs_i$Time # !!!
  
  Nom_Endpoints = c("Weight", "CiEPX")
  
  Nsortie = 2
  
  MPV = IC_min = IC_max = Endpoint = index = NULL
  
  for (j in 1:length(Nom_Endpoints)){
    
    index =grep(paste0("^",Nom_Endpoints[j],"_") , colnames(Sim.Res.ind_i), fixed=FALSE)

    
    Data_sim = as.matrix( Sim.Res.ind_i[ , index] )
    
    MPV    = c(  MPV,  as.numeric( Data_sim[nrow(Data_sim), ] ) )
    IC_min = c(IC_min,  apply(Data_sim, 2, quantile,  0.025, na.rm=TRUE) )
    IC_max = c(IC_max,  apply(Data_sim, 2, quantile,  0.975, na.rm=TRUE) ) 
    
    Endpoint = c(Endpoint, rep(Nom_Endpoints[j], ncol(Data_sim)))
  }
  
  df_mod_ind_i <- data.frame(
    predict.endpoint = MPV,
    Time    = rep(Time_pred, Nsortie),
    low     = IC_min,
    up      = IC_max,
    Endpt   = Endpoint
    )
  
  df_mod_ind_i <- df_mod_ind_i %>%
    mutate(ID=ID_i)

  df_mod_ind <- rbind(df_mod_ind, df_mod_ind_i)
}

df_mod_Weight_ind <- subset(df_mod_ind, Endpt == "Weight")
df_mod_CiEPX_ind <- subset(df_mod_ind, Endpt == "CiEPX")

df_predobs_CiEPX_ind <- dObs_ind |> 
  left_join(df_mod_CiEPX_ind, suffix = c("_obs", "_pred")) |> 
  dplyr::select(-c(Weight_obs, CiIMD)) |> 
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

df_predobs_Weight_ind <- dObs_ind |> 
  filter(!(expo == 2)) |> 
  left_join(df_mod_Weight_ind, suffix = c("_obs", "_pred"))|>
  dplyr::select(-c(CiEPX_obs, CiIMD)) |> 
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na()

```

```{r predobsEPX, message=F, warning=F}
#| fig-cap: Results of the model fit on experimental data. Predicted values are represented with points with their respective credibility interval of 95%. Thin black and grey lines represent the 2-folds and 5-fold changes, respectively. The thicker black line represents the identity line. 
#| label: fig-EPXpredobs
#| fig-height: 4
#| fig-width: 6

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]

seq_line <- seq(0.5, 1.5, 0.001)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_W <- ggplot(
  data = df_predobs_Weight_ind,
  mapping = aes(
      x = Weight_obs,
      y = predict.endpoint
    )
  )+
  geom_line(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up
    ),
    alpha = 0.5,
    color = col_EPX
  )+
  xlim(
    xmin = 0.5,
    xmax = max(df_predobs_Weight_ind$Weight_obs)
  )+
  ylim(
    ymin = 0.5,
    ymax = max(df_predobs_Weight_ind$predict.endpoint)
  )+
  scale_x_log10(limits=c(0.5, 1.2))+
  scale_y_log10(limits=c(0.5, 1.2))+
  labs(
    x = "Observed weight of earthworms (g)",
    y = "Predicted weight of earthworms (g)"
  )+
  theme_minimal()

fact_1 <- 2
fact_2 <- 5

seq_line <- seq(0.5, 1500, 0.01)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )


p_CiEPX_predobs <- ggplot(
  data = df_predobs_CiEPX_ind,
  mapping = aes(
      x = CiEPX_obs,
      y = predict.endpoint
    )
  )+
  geom_path(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  geom_pointrange(
    mapping = aes(
      ymin = low,
      ymax = up,
      color = Group
    ),
    alpha = 0.5#,
    #color = col_EPX
  )+
  
  xlim(
    xmin = 0.5,
    xmax = max(df_predobs_CiEPX_ind$CiEPX_obs)
  )+
  ylim(
    ymin = 0.5,
    ymax = max(df_predobs_CiEPX_ind$predict.endpoint)
  )+
  labs(
    x = "Observed concentrations of EPX\nin earthworms (ng/g)",
    y = "Predicted concentrations of EPX\nin earthworms (ng/g)"
  )+
  scale_color_manual(
    values = col_exposure
    )+
  scale_x_log10(
    #limits=c(1, 500)
    )+
  scale_y_log10(
    #limits=c(1, 500)
    )+
  theme_minimal()

p_predobs <- p_W + p_CiEPX_predobs
p_predobs

```

```{r, include = F}
ggsave(
  filename = "TK_EPX_predobs.png",
  plot = p_predobs,
  width = 10, height = 6,
  path = here::here("fig/TK/")
)
ggsave(
  filename = "TK_EPX_predobs.svg",
  plot = p_predobs,
  width = 10, height = 6,
  path = here::here("fig/TK/")
)
```

```{r countfoldEPX, warning=F}
df_predobs_Weight_ind <- df_predobs_Weight_ind |>
  mutate(
    Ratio_predobs = predict.endpoint / Weight_obs,
    Residuals = predict.endpoint - Weight_obs
  )

Weight_count_fold2 <- length(subset(df_predobs_Weight_ind, Ratio_predobs >= 0.5 & Ratio_predobs <= 2)$Weight_obs) / length(df_predobs_Weight_ind$Weight_obs) * 100

Weight_count_fold5 <- length(subset(df_predobs_Weight_ind, Ratio_predobs >= 0.2 & Ratio_predobs <= 5)$Weight_obs) / length(df_predobs_Weight_ind$Weight_obs) * 100

df_predobs_CiEPX_ind <- df_predobs_CiEPX_ind |>
  mutate(
    Ratio_predobs = predict.endpoint / CiEPX_obs,
    Residuals = predict.endpoint - CiEPX_obs
  )

CiEPX_count_fold2 <- length(subset(df_predobs_CiEPX_ind, Ratio_predobs >= 0.5 & Ratio_predobs <= 2)$CiEPX_obs) / length(df_predobs_CiEPX_ind$CiEPX_obs) * 100

CiEPX_count_fold5 <- length(subset(df_predobs_CiEPX_ind, Ratio_predobs >= 0.2 & Ratio_predobs <= 5)$CiEPX_obs) / length(df_predobs_CiEPX_ind$CiEPX_obs) * 100

cat(
  "For weights : \n\n",
  "Percentage of prediction in fold 2 = ", round(Weight_count_fold2, 1), "%\n",
  "Percentage of prediction in fold 5 = ", round(Weight_count_fold5, 1), "%"
)
cat(
  "\n\nFor internal concentrations : \n\n",
  "Percentage of prediction in fold 2 = ", round(CiEPX_count_fold2, 1), "%\n",
  "Percentage of prediction in fold 5 = ", round(CiEPX_count_fold5, 1), "%"
)
```

```{r, message=F, warning=FALSE}
#| fig-cap: Residuals
#| label: fig-EPXresiduals
#| fig-height: 4
#| fig-width: 6

df_residuals_CiEPX <- df_predobs_CiEPX_ind |> 
  mutate(
    Residual = predict.endpoint - CiEPX_obs,
    Ratio_Residual = predict.endpoint/CiEPX_obs
    ) |> 
  mutate(
    Time_point = as.numeric(as.character(Time_point_f)),
    Group = factor(Group, c("Uptake", "Elimination")),
    Time_relative = case_when(
      Group == "Uptake" ~ Time_point,
      Group == "Elimination" ~ Time_point - 21
    )
    )

p_residus <- ggplot(df_residuals_CiEPX)+
  geom_point(
    aes(
      x = Time_relative,
      y = Ratio_Residual,
      color = Group
    ),
    alpha=0.7
  )+
  labs(
    x = "Temps d'accumulation / d'élimination (sans compter la dépuration)",
    y = "Résidus CiEPX"
  )+
  scale_color_manual(
    values = col_exposure
    )+
  facet_wrap(~Group)+
  scale_x_continuous(
    breaks = unique(df_residuals_CiEPX$Time_relative)
  )+
  scale_y_log10()+
  theme_minimal()

p_residus
```

### Full individual trajectories

```{r setpointindfullin, message=F, warning=F}
Time_min <- 0

Time_max <- 44
Time_step <- 0.25
Time_pred <- seq(Time_min, Time_max, Time_step)
print_times <- paste(Time_min, Time_max, Time_step, sep=", ")
Molecule <- "EPX"
l_param_name <- "kuEPX, keEPX, kcomp_in, kcomp_out, a_growth"
f_Setpoint_ind_full(Molecule, print_times, l_param_name)
```

```{bash, results=F, eval=F}
pwd
cd ..
cd ..
cd mod/TK_EPX
pwd

for j in $(seq 1 62); do
./mcsim.m_TK_EPX TK_EPX_Setpoint_ind_full_${j}.in
done

```

```{r EPXdatapredfull, message=F, warning=F}
#| cache: false

dObs_ind <- df_TK_EPX |> 
  mutate(ID = as.numeric(ID))
colnames(dObs_ind)[colnames(dObs_ind) == "Weight"] <- "Weight_obs"
colnames(dObs_ind)[colnames(dObs_ind) == "CiEPX"] <- "CiEPX_obs"
colnames(dObs_ind)[colnames(dObs_ind) == "t"] <- "Times"

nb_rows_ind <- NC*N_iter_setpoint+1


Sim.Res.ind.full <- lapply(1:62, function(j) {
  read_tsv(file.path(path_mod_EPX, paste0("Setpoints_ind_full_", j, ".out"))) %>%
    mutate(sim = j)
}) %>%
  bind_rows()


df_mod_ind <- NULL

for (i in 1:Nb_experiement){
  
  ID_i <- unique(dObs_ind$ID)[i]

  Sim.Res.ind.full_i  <- subset(Sim.Res.ind.full, sim == i) |> 
    dplyr::select(where(~ !all(is.na(.x))))
  
  dObs_i <- subset(dObs_ind, ID == ID_i)
  
  Nom_Endpoints = c("Weight", "CiEPX", "C_exposure")
  
  Nsortie = length(Nom_Endpoints)
  
  MPV = IC_min = IC_max = Endpoint = index = NULL
  
  for (j in 1:length(Nom_Endpoints)){
    
    index =grep(paste0("^",Nom_Endpoints[j],"_") , colnames(Sim.Res.ind.full_i), fixed=FALSE)

    
    Data_sim = as.matrix( Sim.Res.ind.full_i[ , index] )
    
    MPV    = c(  MPV,  as.numeric( Data_sim[nrow(Data_sim), ] ) )
    IC_min = c(IC_min,  apply(Data_sim, 2, quantile,  0.025, na.rm=TRUE) )
    IC_max = c(IC_max,  apply(Data_sim, 2, quantile,  0.975, na.rm=TRUE) ) 
    
    Endpoint = c(Endpoint, rep(Nom_Endpoints[j], ncol(Data_sim)))
  }
  
  df_mod_ind_i <- data.frame(
    predict.endpoint = MPV,
    Time    = rep(Time_pred, Nsortie),
    low     = IC_min,
    up      = IC_max,
    Endpt   = Endpoint
    )
  
  df_mod_ind_i <- df_mod_ind_i %>%
    mutate(ID=ID_i)

  df_mod_ind <- rbind(df_mod_ind, df_mod_ind_i)
}

df_mod_Weight_ind <- subset(df_mod_ind, Endpt == "Weight")
df_mod_CiEPX_ind <- subset(df_mod_ind, Endpt == "CiEPX")
df_mod_CeEPX_ind <- subset(df_mod_ind, Endpt == "C_exposure")

time_limits <- dObs_ind %>%
  group_by(ID) %>%
  summarise(time_cutoff = max(Time, na.rm = TRUE) + 5)

df_mod_CiEPX_ind_t <- df_mod_CiEPX_ind %>%
  left_join(time_limits, by = "ID") %>%
  filter(Time <= time_cutoff) %>%
  dplyr::select(-time_cutoff) 

df_mod_Weight_ind_t <- df_mod_Weight_ind %>%
  left_join(time_limits, by = "ID") %>%
  filter(Time <= time_cutoff) %>%
  dplyr::select(-time_cutoff) 

df_mod_CeEPX_ind_t <- df_mod_CeEPX_ind %>%
  left_join(time_limits, by = "ID") %>%
  filter(Time <= time_cutoff) %>%
  dplyr::select(-time_cutoff) 

```

```{r}
y_segment <- 1000

df_phases <- dObs_ind |>
  arrange(ID, Time) |>
  group_by(ID) |>
  mutate(
    row = row_number(),
    t_start = Time,
    t_end = lead(Time),  
    segment = row,
    y = y_segment
  ) |>
  filter(!is.na(t_end)) |>  
  dplyr::select(ID, segment, t_start, t_end, y) |>
  ungroup() |> 
  mutate(
    Phase = case_when(
      (segment == 1 & ID < 65) ~ 1,
      (segment == 2 & ID < 65) ~ 3,
      (segment == 1 & ID > 64) ~ 1,
      (segment == 2 & ID > 64) ~ 2,
      (segment == 3 & ID > 64) ~ 3
    )
  )
```

```{r EPXpredcurvesdata, message=F, warning=F}
#| fig-cap: Estimated toxicokinetic of the EPX concentration in earthworms exposed to 1000 ng/g of EPX. Red points represent the experimental data, the blue curve represent the estimated toxicokinetic curve and the transparent blue band correspond to the credibility interval of the model. 
#| fig-label: fig-EPXdatapredfull
#| fig-width: 8
#| fig-height: 10

library(ggforce)

ID_tri <- c(1, 9, 17, 25, 33, 41, 49, 57, 65, 73, 81, 89, 97, 107, 115, 123)

#ID_tri <- unique(df_mod_CiEPX_ind_t$ID)

dObs_ind_plot <- dObs_ind |> 
  mutate(across(everything(), ~replace(.x, .x == -1, NA))) |> 
  drop_na() |> 
  filter(ID %in% ID_tri)

df_mod_CiEPX_ind_t_plot <- subset(df_mod_CiEPX_ind_t, ID %in% ID_tri)
df_mod_CeEPX_ind_t_plot <- subset(df_mod_CeEPX_ind_t, ID %in% ID_tri)
df_mod_Weight_ind_t_plot <- subset(df_mod_Weight_ind_t, ID %in% ID_tri)

df_phases_plot <- subset(df_phases, ID %in% ID_tri)

alpha_point <- 0.5
col_exposure <- c(Nord_aurora[2], Nord_aurora[3], Nord_aurora[4])

p_CiEPX_traj <- ggplot()+
  
  geom_segment(
    data = df_phases_plot,
    aes(
      x = t_start,
      xend = t_end,
      y = y,
      yend = y,
      group = ID,
      color = factor(Phase)
    ),
    linewidth = 2,
    alpha = 0.7
  ) +
  
  # geom_line(
  #   data=df_mod_CeEPX_ind_t_plot,
  #   aes(
  #     x=Time,
  #     y= predict.endpoint,
  #     group = ID
  #     ),
  #   color = Nord_polar[4],
  #   lwd=1
  #   )+

  geom_line(
    data=df_mod_CiEPX_ind_t_plot,
    aes(
      x=Time,
      y= low,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX_ind_t_plot,
    aes(
      x=Time,
      y= up,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX_ind_t_plot,
    aes(
      x=Time,
      y= predict.endpoint,
      group = ID
      ),
    color = col_EPX,
    lwd=1
    )+
  geom_ribbon(
    data=df_mod_CiEPX_ind_t_plot,
    aes(
      x=Time,
      ymax= up,
      ymin= low,
      group = ID
      ),
    fill = col_EPX,
    alpha=0.1
    )+
  geom_point(
    data = dObs_ind_plot,
    aes(
      x = Time,
      y = CiEPX_obs
    ),
    size = 2,
    alpha = 0.7,
    color = col_red
  )+
  
  #scale_y_log10()+
  # facet_wrap(
  #   ~ID,
  #   ncol=8,
  #   scales = "free_x",
  #   )+
  facet_wrap_paginate(
    ~ID,
    #ncol = 4,
    ncol=4,
    nrow = 4,
    scales = "free_x",
    page = 1
    )+
  scale_color_manual(
    values = col_exposure,
    label = c("Uptake", "Elimination", "Depuration"),
    name = "Phase"
    )+
  labs(
    x = "Time (days)",
    y = "CiEPX (ng/g)"
  )+
  #lims(y=c(0, 300))+
  theme_minimal()

p_CiEPX_traj 

p_CiEPX_traj_log <- p_CiEPX_traj + scale_y_log10()

p_CiEPX_traj_log

```

```{r, include = F}
ggsave(
  filename="TK_EPX_comptrajpred.png", 
  plot=p_CiEPX_traj , 
  width=10, height = 20, 
  path=here::here("fig/TK/")
  )
ggsave(
  filename="TK_EPX_comptrajpred.svg", 
  plot=p_CiEPX_traj , 
  width=10, height = 20, 
  path=here::here("fig/TK/")
  )
```

```{r EPXpredcurvesdataW, message=F, warning=F}
#| fig-cap: Weight predictions
#| fig-label: fig-EPXdatapredfullW
#| fig-width: 8
#| fig-height: 10

alpha_point <- 0.5

p_W <- ggplot()+
  geom_line(
    data=df_mod_Weight_ind_t_plot,
    aes(
      x=Time,
      y= low,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_Weight_ind_t_plot,
    aes(
      x=Time,
      y= up,
      group = ID
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_Weight_ind_t_plot,
    aes(
      x=Time,
      y= predict.endpoint,
      group = ID
      ),
    color = col_EPX,
    lwd=1
    )+
  geom_ribbon(
    data=df_mod_Weight_ind_t_plot, 
    aes(
      x=Time, 
      ymax= up, 
      ymin= low,
      group = ID
      ),
    fill = col_EPX,
    alpha=0.1
    )+
  geom_point(
    data = dObs_ind_plot,
    aes(
      x = Time,
      y = Weight_obs
    ),
    size = 2,
    alpha = 0.7,
    color = col_red
  )+
  facet_wrap(
    ~ID,
    ncol = 4,
    scales = "free"
    )+
  #lims(y=c(0, 1500))+
  labs(
    x = "Time (days)",
    y = "Weight (g)"
  )+
  theme_minimal()

p_W

```

```{r, include = F}
ggsave(
  filename="TK_EPX_comptrajpredW.png", 
  plot=p_W , 
  width=10, height = 20, 
  path=here::here("fig/TK/")
  )
ggsave(
  filename="TK_EPX_comptrajpredW.svg", 
  plot=p_W , 
  width=10, height = 20, 
  path=here::here("fig/TK/")
  )
```

### Simulation of the toxicodynamic in earthworms throughout the exposition

The goal here is to recreate the concentration dynamic in the average earthworm during our exposition scheme but without the fasting phase that was required for chemical analysis and during which elimination was happening.

```{r setpointin, message=F, warning=F}

Time_min <- 0
Time_max <- 42
Time_step <- 0.25
Time_pred <- seq(Time_min, Time_max, Time_step)
print_times <- paste(Time_min, Time_max, Time_step, sep=", ")

l_param_name_tot <- "kuEPX, keEPX, kcomp_in, kcomp_out, a_growth, Vr_a_growth, Sigma_W, Sigma_CiEPX"

f_Setpoint(Molecule, print_times, l_param_name_tot)
```

```{bash, results=F, eval=F}
pwd
cd ..
cd ..
cd mod/TK_EPX
pwd
./mcsim.m_TK_EPX TK_EPX_Setpoint.in
wait
```

```{r EPXreadSetpoint, message=F, warning=F}

Sim.Res <- as.data.frame(fread(here::here(path_mod_EPX, "Setpoints.out"),sep="\t"))

  
  Nom_Endpoints =c("Weight_1", "CiEPX_1", "C_exposure_1")
  Nsortie = 3
  MPV = IC_min = IC_max = Endpoint = index = NULL

  for (i in 1:length(Nom_Endpoints)){
    
    index =grep(paste("^",Nom_Endpoints[i],"\\.", sep="") , colnames(Sim.Res), fixed=FALSE )
    
    Data_sim = as.matrix( Sim.Res[ , index] )
    
    MPV    = c(  MPV,  as.numeric( Data_sim[nrow(Data_sim), ] ) )
    IC_min = c(IC_min,  apply(Data_sim, 2, quantile,  0.025) )
    IC_max = c(IC_max,  apply(Data_sim, 2, quantile,  0.975) ) 
    
    Endpoint = c(Endpoint, rep(Nom_Endpoints[i], ncol(Data_sim)))

    }

  df_mod <- data.frame(
    predict.endpoint = MPV,
    Time    = c( rep(Time_pred, Nsortie)),
    low     = IC_min,
    up      = IC_max,
    Endpt   = Endpoint,
    Experiment = c(rep(rep("Experience 1", length(Time_pred)), Nsortie))
    )
  
df_mod_Weight <- subset(df_mod, Endpt == "Weight_1")
df_mod_CiEPX <- subset(df_mod, Endpt == "CiEPX_1") 
  
  # length(MPV)
  # length(df_Cin$Time)
  # length(Endpoint)
  # length(df_Cin$Experiment)
   
```

```{r EPXpredcurves, message=F, warning=F}
#| fig-cap: Estimated toxicokinetic of the EPX concentration in earthworms exposed to 0.1 mg/kg of EPX. Blue points represent the experimental data, the blue curve represents the estimated toxicokinetic curve and the transparent blue band corresponds to the credibility interval of the model. 
#| fig-label: fig-EPXcurvemod
#| fig-width: 8
#| fig-height: 4

alpha_point <- 0.5

p_CiEPX <- ggplot()+
  geom_line(
    data=df_mod_CiEPX,
    aes(
      x=Time,
      y= low
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX,
    aes(
      x=Time,
      y= up
      ),
    linetype="dotted",
    color = col_EPX
    )+
  geom_line(
    data=df_mod_CiEPX,
    aes(
      x=Time,
      y= predict.endpoint
      ),
    color = col_EPX,
    lwd=1
    )+
  geom_ribbon(
    data=df_mod_CiEPX, 
    aes(
      x=Time, 
      ymax= up, 
      ymin= low
      ),
    fill = col_EPX,
    alpha=0.1
    )+
  labs(
    x = "Time (days)",
    y = "Internal EPX concentration (ng/g)"
  )+
  theme_minimal()

p <- p_CiEPX 
p

```

```{r, include = F}
  ggsave(
    filename="TK_EPX_predcurves.png", 
    plot=p, 
    width=3, height = 2.5, 
    path=here::here("fig/TK/")
    )
  ggsave(
    filename="TK_EPX_predcurves.svg", 
    plot=p, 
    width=6, height = 4, 
    path=here::here("fig/TK/")
    )
```
